### 2013-10-24 PositionPaper/incremental.tex
first version

Given a requirement expressing a query and quality of service preferences : cost, provenance, reputation, time the system processes it according to the following steps:

\begin{enumerate}
\item Computation of a global SLA given the existing possible data providers that can be called for answering the query.

\item See whether a similar SLA has been computed before
  \begin{description}
  \item[$\longrightarrow$ yes:] use it
  \item[$\longrightarrow$ else:] compute the total or partial SLA and store it in the history
  \end{description}
  \begin{enumerate}
  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query
  \item Rewrite the query into n subqueries that can compute a partial answer
  \end{enumerate}

\item see wether a similar Q has been already rewritten
  \begin{description}
  \item[$\longrightarrow$ yes:] use the rewriten queries
  \item[$\longrightarrow$ else:] compute it and store the result
  \end{description}
  \begin{enumerate}
  \item Generate a service coordination that can compute each subquery and can integrate the global result. 
Each subquery is optimized with respect to user profile
  \item Dispatch the execution of subqueries, integrate them into a result
  \end{enumerate}

\item[$\longrightarrow$] at execution: monitor the consumption of resources, the execution, time, behaviour of the services and make decisions
\end{enumerate}

### 2013-10-24 PositionPaper/introduction.tex
first version

The emergence of new architectures like the cloud opens new challenges to data processing. 
The possibility of having unlimited Access to cloud resources and the ``pay as U go'' model make it possible to change the hypothesis under which current technology and solutions address the processing of huge volumes of data. 
Instead of designing processes and algorithms taking into consideration the limits on resources availability, the cloud sets the focus on the economic cost implied of using resources and producing results by parallelizing the use of computing resources while delivering data under subscription oriented cost models.

Current data management approaches on the cloud tend to use NoSQL stores for managing huge heterogeneous data collections (graph, key-value, tables, relational): polyglot approaches. 
Yet, having such heterogeneous schema-less data stores, calls for efficient methods for integrating (correlating, associating, filtering) heterogeneous data collections taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality of service, e.g., trust, freshness, provenance, partial or total consistency. 
Existing data integration techniques based on mappings, views management, ontologies have to be revisited in order to integrate data that are weakly curated and described through metadata or schemas.

{\color{green} 
Furthermore, security aspects are crucial in integrating big data. Indeed, the integration task must guarantee the integrity and privacy of data, the willingness of the clouds to well contribute to the security process through acceptable runtime environment conditions, and the adequacy of the proposed security levels to the services behind the integration operation.
}

Our work intends to address data integration on a hybrid cloud guided by the SLA exported by different cloud providers and by several QoS measures associated to data collections properties: trust, privacy, economic cost. 
We aim to address big data integration d in a multi-cloud hybrid context. 
This implies several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed along different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).

The objectives of our work are to propose an SLA guided continuous data provision and integration system that will be exported as a DaaS by a cloud provider. 
Therefore we propose strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting and bi data sets integration according to user preferences. 
Given the computational cost of a query evaluation, our approach uses automatic learning techniques for generating knowledge out of every task and reducing its economic cost.

This paper proposes data integration (lookup, aggregation, correlation) strategies adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies security requirement rather that a more powerful cloud but with less security guarantees in the SLA.

### 2013-10-24 PositionPaper/relwork.tex
first version

\begin{itemize}
\item security concerns - SLA 
\item data integration (cf. travaux Gonzalez) 
\end{itemize}

### 2013-10-24 PositionPaper/slaDataInteg.tex
first version

{\color{green}
Overview of our approach that will include:
- An SLA Model: including security issues

- A multi cloud environment representation

- On demand incremental data integration strategies
}

\begin{figure}
\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
\end{figure}

Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s. 
These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.

\subsection{SLA model}
\label{sec:slaModel}

\begin{itemize}
\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
  \begin{itemize}
  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
  \item Templates pour exprimer le SLA
  \item Intégration: modèle pivot de SLA
\end{itemize}

\item SLA violation contrôlée avec des mechanisms de monitoring.
\item Que ce que devient l’intégration de données par rapport au SLA
\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
\end{itemize}

\subsection{Query Rewriting}
\label{sec:queryRew}

{\color{red}
Here Martin will explain the rewriting problem.
}

\subsection{Data and query models}
\label{sec:dqm}

TBD.

### 2013-10-24 PositionPaper/useCase.tex
first version

Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
Producers are characterized according to their location, the amount of energy in kWatts-hour that they can sell, the cost, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance. 
Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy. 
A energy exchange market is established in order to continuously monitor energy provision/consumption ensuring that all consumers will have the energy they require at every moment.

\begin{figure}
\includegraphics[width=0.6\textwidth]{figs/arch.png}
\caption{\label{fig:energyXChange} Energy exchange.}
\end{figure}

In our approach energy producers are modelled as services with associated ``agreed'' SLAs for a given time window. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific QoS preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.

\begin{itemize}
\item Processing big data implied in the energy consumption observation 
\item Computing energy consumption behavior models
\item Analyse and optimize energy consumption versus respecting the comfort requirement of inhabitants
\end{itemize}

Need of efficient data processing solutions

### 2013-11-08 PositionPaper/relwork.tex
modifs Nadia

@@
 \begin{itemize}
-\item security concerns - SLA 
+\item Cloud computing represents a novel on-demand computing approach where resources are provided in compliance to a set of predefined non-functional properties specified and negotiated by means of Service Level Agreements (SLAs).
+SLA currently exploited in the cloud allows service providers and cloud client to fix the resource level that should be used either by a service for the service provider or by the client in the case of service invokation.
+SLA could concern all types of the services on the cloud (IAAS, PAAS or SAAS).
+One of the weakness of SLA for the client is that they express low level clauses like storage amount use or virtualization level.
+In fact when a client launches a task on the cloud, she has unlikely Q \& S requirement rather than low level features.
+Recently we notice the existing of a lot of works with the objective to fill the gap.
+Emeakaroha and al propose in \cite{5547150}  a cloud component that acts autonomously based on low level  monitored features after analysing them towards high level clauses expressed by the user.
+Moreover, another difficulty to enforce an SLA is to measure and identify, starting from a high level SLA clause, how could it be declined at different layers in the cloud.
+Therefore in \cite{Dastjerdi:2012:DOA:2275356.2275360} the authors describe a semanticSLA which can be understood by all parties including providers,
+requestors, and monitoring services.
+One of the major objectives in the cloud is to anticipate SLA violation and to assess SLA failure cascading on violation detection.
+\cite{Dastjerdi:2012:DOA:2275356.2275360} proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
+\cite{5547150} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
+in \cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+On the other hand SLA contracts do not cover all client requirement. There is still a lack in some domain.....(to be completed)
+
   \item data integration (cf. travaux Gonzalez) 

### 2013-11-08 PositionPaper/slaDataInteg.tex
modifs Nadia

@@
 
+In order to propose an SLA guided continuous data provision and integration, we need to think about possible steps from the request to the delivery of the result sets.
+Indeed, let consider a request R launched by a user who specifies a number of constraints on the environment execution.
+Executing this query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
+One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
+This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e.
+macroscopic constraints: execution time, pay / no pay, data reliability, data source).
+The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).
+To meet this objective, it is necessary to compare the SLA services to combine, in order to check if their joint use is compatible with the individual SLA.
+This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive Template.
+The negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
+This negotiation can be expensive and may not scale well.
+It is therefore crucial to provide proactive mechanisms for optimizing the production of such SLA.
+We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results.
+Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not touching the data).
+For two different queries, they will be negotiated in the same way.
+These previously negotiated SLAs are reusable.
+In a second time, we think optimizing this process on the data storage mechanisms to cache intermediate results, individually or in partial or complete combination depending on the terms of SLA services (data access, intermediate storage capacity , cost of storage , etc ...
+).
+Given this proposal, we identify several issues:
+- Level modeling would require a model that allows the representation of SLA integration.
+- There should also be a template for representing the requirements expressed by the user
+- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
+This implies mapping between property and expressed clauses being.
+
 \subsection{Query Rewriting}

### 2013-11-12 PositionPaper/introduction.tex
no message

@@
 
-Current data management approaches on the cloud tend to use NoSQL stores for managing huge heterogeneous data collections (graph, key-value, tables, relational): polyglot approaches. 
+Current data management approaches on the cloud tend to use NoSQL stores for managing huge heterogeneous data collections (graph, key-value, tables, relational). 
 Yet, having such heterogeneous schema-less data stores, calls for efficient methods for integrating (correlating, associating, filtering) heterogeneous data collections taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality of service, e.g., trust, freshness, provenance, partial or total consistency.
@@
 
-{\color{green} 
-Furthermore, security aspects are crucial in integrating big data.
-Indeed, the integration task must guarantee the integrity and privacy of data, the willingness of the clouds to well contribute to the security process through acceptable runtime environment conditions, and the adequacy of the proposed security levels to the services behind the integration operation.
-}
+%{\color{green} 
+%Furthermore, security aspects are crucial in integrating big data.
+Indeed, the integration task must guarantee the integrity and privacy of data, the willingness of the clouds to  contribute to the security process through acceptable runtime environment conditions, and the adequacy of the proposed security levels to the services behind the integration operation.
+%}
 
@@
 
-The objectives of our work are to propose an SLA guided continuous data provision and integration system that will be exported as a DaaS by a cloud provider. 
-Therefore we propose strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting and bi data sets integration according to user preferences.
-Given the computational cost of a query evaluation, our approach uses automatic learning techniques for generating knowledge out of every task and reducing its economic cost.
+The objectives of our work are to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider. 
+Therefore we propose strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting for integrating data sets  according to user profiles.
+%Given the computational cost of a query evaluation and a user profile, our approach uses automatic learning techniques for generating knowledge out of every task and reducing query evaluation economic cost.
 
 This paper proposes data integration (lookup, aggregation, correlation) strategies adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies security requirement rather that a more powerful cloud but with less security guarantees in the SLA.
+
+Accordingly, the remainder of this paper is organized as follows.
+Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes.
+Section \ref{sec:slaDataInteg} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by concilating SLA's provided by services and user's profiles expressing QoS preferences about the data they want to consume and the conditions in which they must be processed and delivered.
+Section \ref{sec:incremental} introduces on demand and incremental data integration strategies.
+Section \ref{sec:useCase}presents a use case for illustrating the interest and use of our approach.
+Finally \ref{sec:conclusions} concludes the papers and discusses future work.

### 2013-11-18 PositionPaper/incremental.tex
Current state

@@
 \begin{enumerate}
-\item Computation of a global SLA given the existing possible data providers that can be called for answering the query.
 
@@
   \end{description}
+
+\item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query.
+Data providers are filtered in this way, since only those agreed SLA that can be combined into a global SLA that can fulfill the user preferences are considered for retrieving data.
+
   \begin{enumerate}
@@
   \begin{enumerate}
-  \item Generate a service coordination that can compute each subquery and can integrate the global result. 
+  \item Generate a service coordination search space that can compute each subquery and can integrate the global result. 
 Each subquery is optimized with respect to user profile

### 2013-11-19 PositionPaper/slaDataInteg.tex
Current state
some rewriting...

@@
 
-\begin{figure}
+\begin{figure*}
 \caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-\end{figure}
+\end{figure*}
 
@@
 
-{\color{red}
-Here Martin will explain the rewriting problem.
-}
+%{\color{red}
+%Here Martin will explain the rewriting problem.
+%}
+
+Query rewriting is a well-known problem for the database community.
+The problem consists on transforming an abstract query into a set (or list) of lower-level queries to the available databases.
+Traditionally, the abstract query is a query over a set of views and the lower-level queries are performed on the available databases whose information compose the view. 
+The rewriting is guided by the schema of both abstract and concrete databases.
+The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
+
+The query rewriting problem may be generalized to the case of services.
+This is a natural consequence of the use of information-providing\footnote{Services that do not perform changes in the data they use.} services as interfaces over relational databases.
+Both database queries and service invocations may be represented using a similar syntax.
+Indeed, the interfaces to relational databases and information-providing services are exactly the same.
+In the case of general services, the abstract query is seen as an abstract service composition, which is rewritten into a \textit{concrete} service composition.
+The rewriting process is guided by the interfaces (types) of the abstract and concrete services.
+
+Abstract services and database interfaces have some conspicuous differences.
+Services may change information: Two different invocations may not return the same answer, even when given the same input data.
+Also service compositions may need to meet some requirements such as QoS or other quality constraints that need to be verified.
+
+Query rewriting techniques have been adapted to the context of service composition~\cite{queryRewriting}. 
+In~\cite{UmbertoICWE2013} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
+The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting,  known in the database domain.
+The proposed approach consists in generating several translations of an abstract service specification into compositions
+over concrete  services. 
+The solutions proposed are ranked and may be coded into concrete orchestrations.
 

### 2013-11-21 PositionPaper/incremental.tex
no message

@@
-Given a requirement expressing a query and quality of service preferences : cost, provenance, reputation, time the system processes it according to the following steps:
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according to the following steps:
 

### 2013-11-21 PositionPaper/incremental.tex
Reorganisation du papier. Une seule section avec l'approche ensuite Use case

@@
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according to the following steps:
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according to the three  main steps: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
+The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
+The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
+
+ Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt?}.
+Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query.
+Thus, the whole query evaluation process is done through the following steps:
 
@@
 
-\item See whether a similar SLA has been computed before
-  \begin{description}
-  \item[$\longrightarrow$ yes:] use it
-  \item[$\longrightarrow$ else:] compute the total or partial SLA and store it in the history
-  \end{description}
+\item  {\bf Global SLA computation: vertical integration}. 
+Given the user preferences, see whether a similar SLA has been computed with this input before or compute the total or partial SLA, and store it in the history
 
+ \begin{enumerate}
 \item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query.
@@
 
-  \begin{enumerate}
   \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query
-  \item Rewrite the query into n subqueries that can compute a partial answer
   \end{enumerate}
 
-\item see wether a similar Q has been already rewritten
-  \begin{description}
-  \item[$\longrightarrow$ yes:] use the rewriten queries
-  \item[$\longrightarrow$ else:] compute it and store the result
-  \end{description}
-  \begin{enumerate}
-  \item Generate a service coordination search space that can compute each subquery and can integrate the global result. 
-Each subquery is optimized with respect to user profile
-  \item Dispatch the execution of subqueries, integrate them into a result
+  \item {\bf Rewrite the query.} See wether a similar Q has been already rewritten or rewrite it into n subqueries that can compute a partial answer.
+The subsueries represent the possible combination of services that can answer the initial query with given SLA.
+
+  \item {\bf Optimize and execute subqueries.} Generate a service coordination search space that can compute each subquery and can integrate the global result. 
+Each subquery is optimized with respect to user profile.
+
+  \item Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour of the services and make decisions
 \end{enumerate}
 
-\item[$\longrightarrow$] at execution: monitor the consumption of resources, the execution, time, behaviour of the services and make decisions
-\end{enumerate}
+\subsection{SLA model}
+\label{sec:slaModel}
+
+\begin{itemize}
+\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
+  \begin{itemize}
+  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
+  \item Templates pour exprimer le SLA
+  \item Intégration: modèle pivot de SLA
+\end{itemize}
+
+\item SLA violation contrôlée avec des mechanisms de monitoring.
+\item Que ce que devient l’intégration de données par rapport au SLA
+\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
+\end{itemize}
+
+In order to propose an SLA guided continuous data provision and integration, we need to think about possible steps from the request to the delivery of the result sets.
+Indeed, let consider a request R launched by a user who specifies a number of constraints on the environment execution.
+Executing this query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
+One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
+This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e.
+macroscopic constraints: execution time, pay / no pay, data reliability, data source).
+The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).
+To meet this objective, it is necessary to compare the SLA services to combine, in order to check if their joint use is compatible with the individual SLA.
+This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive Template.
+The negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
+This negotiation can be expensive and may not scale well.
+It is therefore crucial to provide proactive mechanisms for optimizing the production of such SLA.
+We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results.
+Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not touching the data).
+For two different queries, they will be negotiated in the same way.
+These previously negotiated SLAs are reusable.
+
+In a second time, we think optimizing this process on the data storage mechanisms to cache intermediate results, individually or in partial or complete combination depending on the terms of SLA services (data access, intermediate storage capacity , cost of storage , etc ...
+).
+Given this proposal, we identify several issues:
+- Level modeling would require a model that allows the representation of SLA integration.
+- There should also be a template for representing the requirements expressed by the user
+- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
+This implies mapping between property and expressed clauses being.
+
+\subsection{Query Rewriting}
+\label{sec:queryRew}
+
+%{\color{red}
+%Here Martin will explain the rewriting problem.
+%}
+
+Query rewriting is a well-known problem for the database community.
+The problem consists on transforming an abstract query into a set (or list) of lower-level queries to the available databases.
+Traditionally, the abstract query is a query over a set of views and the lower-level queries are performed on the available databases whose information compose the view. 
+The rewriting is guided by the schema of both abstract and concrete databases.
+The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
+
+The query rewriting problem may be generalized to the case of services.
+This is a natural consequence of the use of information-providing\footnote{Services that do not perform changes in the data they use.} services as interfaces over relational databases.
+Both database queries and service invocations may be represented using a similar syntax.
+Indeed, the interfaces to relational databases and information-providing services are exactly the same.
+In the case of general services, the abstract query is seen as an abstract service composition, which is rewritten into a \textit{concrete} service composition.
+The rewriting process is guided by the interfaces (types) of the abstract and concrete services.
+
+Abstract services and database interfaces have some conspicuous differences.
+Services may change information: Two different invocations may not return the same answer, even when given the same input data.
+Also service compositions may need to meet some requirements such as QoS or other quality constraints that need to be verified.
+
+Query rewriting techniques have been adapted to the context of service composition~\cite{queryRewriting}. 
+In~\cite{UmbertoICWE2013} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
+The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting,  known in the database domain.
+The proposed approach consists in generating several translations of an abstract service specification into compositions
+over concrete  services. 
+The solutions proposed are ranked and may be coded into concrete orchestrations.

### 2013-11-21 PositionPaper/introduction.tex
Reorganisation du papier. Une seule section avec l'approche ensuite Use case

@@
 Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes.
-Section \ref{sec:slaDataInteg} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by concilating SLA's provided by services and user's profiles expressing QoS preferences about the data they want to consume and the conditions in which they must be processed and delivered.
-Section \ref{sec:incremental} introduces on demand and incremental data integration strategies.
-Section \ref{sec:useCase}presents a use case for illustrating the interest and use of our approach.
-Finally \ref{sec:conclusions} concludes the papers and discusses future work.
+Section \ref{sec:incremental} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by concilating SLA's provided by services and user's profiles expressing QoS preferences about the data they want to consume and the conditions in which they must be processed and delivered.
+%Section \ref{sec:incremental} introduces on demand and incremental data integration strategies. 
+Section \ref{sec:useCase}presents a use case for illustrating the interest and use of our approach. Finally \ref{sec:conclusions} concludes the papers and discusses future work.

### 2013-11-21 PositionPaper/useCase.tex
Reorganisation du papier. Une seule section avec l'approche ensuite Use case

@@
+\begin{figure*}
+\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
+\end{figure*}
+
+Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
+These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
+The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.
+
 Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 

### 2013-11-22 PositionPaper/incremental.tex
no message

@@
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according to the three  main steps: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
+We propose an SLA guided continuous data provision and integration approach that proposes three steps  starting from the processing of the request  to the delivery of the result sets.
+
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
 The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
@@
 
-\item  {\bf Global SLA computation: vertical integration}. 
-Given the user preferences, see whether a similar SLA has been computed with this input before or compute the total or partial SLA, and store it in the history
+\item  {\bf Global SLA computation}. 
+This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e.
+macroscopic constraints: execution time, pay / no pay, data reliability, data source).
+The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).
+
+One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user. 
+To meet this objective, it is necessary to compare the SLA services to combine, in order to check if their joint use is compatible with the individual SLA.
+This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
 
@@
 
-  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query
+  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.
+
+  \item Negociation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
+This negotiation can be expensive and may not scale well.
   \end{enumerate}
 
-  \item {\bf Rewrite the query.} See wether a similar Q has been already rewritten or rewrite it into n subqueries that can compute a partial answer.
+  \item {\bf Rewrite the query.} See wether a similar Q has been already rewritten or rewrite it.
+Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
 The subsueries represent the possible combination of services that can answer the initial query with given SLA.
@@
 
-  \item Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour of the services and make decisions
+  \item Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions
 \end{enumerate}
 
+%-----------------------------------------------------------------
 \subsection{SLA model}
 \label{sec:slaModel}
+%-----------------------------------------------------------------
 
-\begin{itemize}
-\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
-  \begin{itemize}
-  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
-  \item Templates pour exprimer le SLA
-  \item Intégration: modèle pivot de SLA
-\end{itemize}
+%\begin{itemize}
+%\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
+%  \begin{itemize}
+%  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
+%  \item Templates pour exprimer le SLA
+%  \item Intégration: modèle pivot de SLA
+%\end{itemize}
+%
+%\item SLA violation contrôlée avec des mechanisms de monitoring.
+%\item Que ce que devient l’intégration de données par rapport au SLA
+%\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
+%\end{itemize}
 
-\item SLA violation contrôlée avec des mechanisms de monitoring.
-\item Que ce que devient l’intégration de données par rapport au SLA
-\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
-\end{itemize}
-
-In order to propose an SLA guided continuous data provision and integration, we need to think about possible steps from the request to the delivery of the result sets.
-Indeed, let consider a request R launched by a user who specifies a number of constraints on the environment execution.
-Executing this query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
-One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
-This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e.
-macroscopic constraints: execution time, pay / no pay, data reliability, data source).
-The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).
-To meet this objective, it is necessary to compare the SLA services to combine, in order to check if their joint use is compatible with the individual SLA.
-This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive Template.
-The negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
-This negotiation can be expensive and may not scale well.
-It is therefore crucial to provide proactive mechanisms for optimizing the production of such SLA.
-We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results.
-Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not touching the data).
-For two different queries, they will be negotiated in the same way.
-These previously negotiated SLAs are reusable.
-
-In a second time, we think optimizing this process on the data storage mechanisms to cache intermediate results, individually or in partial or complete combination depending on the terms of SLA services (data access, intermediate storage capacity , cost of storage , etc ...
-).
-Given this proposal, we identify several issues:
-- Level modeling would require a model that allows the representation of SLA integration.
-- There should also be a template for representing the requirements expressed by the user
-- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
-This implies mapping between property and expressed clauses being.
-
+%-----------------------------------------------------------------
 \subsection{Query Rewriting}
 \label{sec:queryRew}
-
+%-----------------------------------------------------------------
 %{\color{red}
@@
 The solutions proposed are ranked and may be coded into concrete orchestrations.
+
+%-----------------------------------------------------------------
+\subsection{Executing optimized queries}
+\label{sec:queryOpt}
+%-----------------------------------------------------------------
+
+%-----------------------------------------------------------------
+\subsection{Reducing the overhead of the evaluation process}
+\label{sec:queryProcessOpt}
+%-----------------------------------------------------------------
+% Indeed, let consider a request R launched by a user who specifies a %number of constraints on the environment execution.
+
+ It is  crucial to provide proactive mechanisms for optimizing the production of such SLA.
+We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results.
+Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not touching the data).
+For two different queries, they will be negotiated in the same way.
+These previously negotiated SLAs are reusable.
+
+In a second time, we think optimizing this process on the data storage mechanisms to cache intermediate results, individually or in partial or complete combination depending on the terms of SLA services (data access, intermediate storage capacity , cost of storage , etc ...
+).
+Given this proposal, we identify several issues:
+- Level modeling would require a model that allows the representation of SLA integration.
+- There should also be a template for representing the requirements expressed by the user
+- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
+This implies mapping between property and expressed clauses being.

### 2013-11-22 PositionPaper/incremental.tex
no message

@@
 The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
+The following sections describe how this query is computed according to our approach.
 
- Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt?}.
-Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query.
-Thus, the whole query evaluation process is done through the following steps:
+%-----------------------------------------------------------------
+\subsection{Computing query SLA}
+\label{sec:slaModel}
+%-----------------------------------------------------------------
 
-\begin{enumerate}
+%\begin{itemize}
+%\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
+%  \begin{itemize}
+%  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
+%  \item Templates pour exprimer le SLA
+%  \item Intégration: modèle pivot de SLA
+%\end{itemize}
+%
+%\item SLA violation contrôlée avec des mechanisms de monitoring.
+%\item Que ce que devient l’intégration de données par rapport au SLA
+%\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
+%\end{itemize}
 
-\item  {\bf Global SLA computation}. 
 This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e.
@@
 
-  \item {\bf Rewrite the query.} See wether a similar Q has been already rewritten or rewrite it.
-Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
-The subsueries represent the possible combination of services that can answer the initial query with given SLA.
-
-  \item {\bf Optimize and execute subqueries.} Generate a service coordination search space that can compute each subquery and can integrate the global result. 
-Each subquery is optimized with respect to user profile.
-
-  \item Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions
-\end{enumerate}
-
-%-----------------------------------------------------------------
-\subsection{SLA model}
-\label{sec:slaModel}
-%-----------------------------------------------------------------
-
-%\begin{itemize}
-%\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
-%  \begin{itemize}
-%  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
-%  \item Templates pour exprimer le SLA
-%  \item Intégration: modèle pivot de SLA
-%\end{itemize}
-%
-%\item SLA violation contrôlée avec des mechanisms de monitoring.
-%\item Que ce que devient l’intégration de données par rapport au SLA
-%\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
-%\end{itemize}
-
 %-----------------------------------------------------------------
@@
 %}
+
+See wether a similar Q has been already rewritten or rewrite it.
+Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
+The subsueries represent the possible combination of services that can answer the initial query with given SLA.
 
@@
 %-----------------------------------------------------------------
+Generate a service coordination search space that can compute each subquery and can integrate the global result. 
+Each subquery is optimized with respect to user profile.
+
+ Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions
 

### 2013-11-22 PositionPaper/useCase.tex
no message

@@
 
-\begin{figure}
+\begin{figure*}
 \includegraphics[width=0.6\textwidth]{figs/arch.png}
 \caption{\label{fig:energyXChange} Energy exchange.}
-\end{figure}
+\end{figure*}
 
@@
 Need of efficient data processing solutions
+
+ Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt?}.
+Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query.

### 2013-11-22 PositionPaper/relwork.tex
Related works

--- 2013-10-24 PositionPaper/relwork.tex
@@
-\begin{itemize}
-\item security concerns - SLA 
-\item data integration (cf. travaux Gonzalez) 
-\end{itemize}
+%\begin{itemize}
+%\item Cloud computing represents a novel on-demand computing approach where resources are provided in compliance to a set of predefined non-functional properties specified and negotiated by means of Service Level Agreements (SLAs).
+SLA currently exploited in the cloud allows service providers and cloud client to fix the resource level that should be used either by a service for the service provider or by the client in the case of service invokation.
+SLA could concern all types of the services on the cloud (IAAS, PAAS or SAAS).
+One of the weakness of SLA for the client is that they express low level clauses like storage amount use or virtualization level.
+In fact when a client launches a task on the cloud, she has unlikely Q \& S requirement rather than low level features.
+Recently we notice the existing of a lot of works with the objective to fill the gap.
+Emeakaroha and al propose in \cite{5547150}  a cloud component that acts autonomously based on low level  monitored features after analysing them towards high level clauses expressed by the user.
+Moreover, another difficulty to enforce an SLA is to measure and identify, starting from a high level SLA clause, how could it be declined at different layers in the cloud.
+Therefore in \cite{Dastjerdi:2012:DOA:2275356.2275360} the authors describe a semanticSLA which can be understood by all parties including providers,
+%requestors, and monitoring services.
+One of the major objectives in the cloud is to anticipate SLA violation and to assess SLA failure cascading on violation detection.
+\cite{Dastjerdi:2012:DOA:2275356.2275360} proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
+\cite{5547150} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
+in \cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+%On the other hand SLA contracts do not cover all client requirement. There is still a lack in some domain.....(to be completed)
+
+%\item some
+
+Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
+and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
+working group. The extension allows security constraints to be expressed over the service description
+terms (SDTs) and the service level objectives (SLOs) of the SLA.
+Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP.
+Luna and al
+work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool.
+The designed template is then used both to express user security requirements and CSP security provisions.
+
+Another issue in the SLA management domain is how to let CSP offer fit the best user requirements.
+In fact, current SLA are only resource oriented and lacks in expressing client requirement in service quality and characteristics.
+Plenty of works tends to fill the gap.
+First by proposing predefined templates;.
+In \cite{Ortiz:2013:VPS:2486767.2486772}, the authors
+  a set of templates to the user of cloud data services, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
+
+  In \cite{LunaGarcia:2012:BCS:2381913.2381932,}, the authors propose to do a mapping of both user SecSLA requirements and CSP SecSLA provisions on a set of Quantitative Policy Tree(QPT), where atomic capabilities are mapped on leaves and intermediate represents coarse provisions with some logical operators (AND, OR).
+The mapping allows to give a quantitative benchmarking to each CSP offer with respect to user requirements that lets the user be able to make a choice.
+For more experienced users, \cite{6313668} proposes an extensible specification grammar that allows to express user and application-specific requirements in using a cloud data service.
+This allows to customize the SLA management at the cloud side.
+Emeakaroha and al propose in \cite{5547150}  a cloud component that acts autonomously based on low level monitored features after analysing them towards high level clauses expressed by the user.
+Moreover, another difficulty to enforce an SLA is to measure and identify, starting from a high level SLA clause, how could it be declined at different layers in the cloud.
+Therefore in  \cite{Dastjerdi:2012:DOA:2275356.2275360}  the authors describe a semantic- SLA which can be understood by all parties including providers,requestors, and monitoring services.
+
+Finally, some works tend to deal with SLA violation anticipation and SLA failure cascading on violation detection.
+\cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
+\cite{5614035} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
+in
+\cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+
+ % \item data integration (cf. travaux Gonzalez) 
+%\end{itemize}

### 2013-11-22 PositionPaper/incremental.tex

@@
 %-----------------------------------------------------------------
-%{\color{red}
-%Here Martin will explain the rewriting problem.
-%}
-
+{\color{red}
 See wether a similar Q has been already rewritten or rewrite it.
 Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
-The subsueries represent the possible combination of services that can answer the initial query with given SLA.
+The subqueries represent the possible combination of services that can answer the initial query with given SLA.
+}
 

### 2013-11-22 PositionPaper/incremental.tex

@@
 The query rewriting problem may be generalized to the case of services.
-This is a natural consequence of the use of information-providing\footnote{Services that do not perform changes in the data they use.} services as interfaces over relational databases.
 Both database queries and service invocations may be represented using a similar syntax.
-Indeed, the interfaces to relational databases and information-providing services are exactly the same.
-In the case of general services, the abstract query is seen as an abstract service composition, which is rewritten into a \textit{concrete} service composition.
-The rewriting process is guided by the interfaces (types) of the abstract and concrete services.
+Indeed, the interfaces to relational databases and information-providing\footnote{Services that do not perform changes in the data they use.} services are exactly the same.
+In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services (which take the place of the available database queries).
 
-Abstract services and database interfaces have some conspicuous differences.
-Services may change information: Two different invocations may not return the same answer, even when given the same input data.
-Also service compositions may need to meet some requirements such as QoS or other quality constraints that need to be verified.
+The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-providing case.
+Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
+In this context, the \textit{Global as a View} (\textit{GAV}) methods of query rewriting~\cite{queryRewriting} are suitable.
+In the GAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available databases.
+In the case of general services, we can use the specification of the composition to be produced as well as the specification of each available service.
+These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
 
@@
 The solutions proposed are ranked and may be coded into concrete orchestrations.
+
+The next example shows the main features of the approach proposed in~\cite{UmbertoICWE2013}.
+
+\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
+Let us consider the case of generating sales reports for a global bookstore.
+This hypothetical bookstore sells books both at about 300 shops around the globe as well as via Internet.
+The bookstore has four international warehouses, located in four different continents.
+The bookstore uses the services of three different cloud providers.
+Each cloud provider exports their own interfaces.
+
+Local shops use the nearest cloud provider.
+Internet transactions are processed by the Asian and South American cloud providers.
+
+When a potential Internet client requires a list of books, a composed web service is generated, in order to fetch each book (from the nearest warehouse where the book is available) and to put in motion the payment and packing procedures.
+Depending on the location of the client, different conditions may apply on the selling and payment procedures.
+So, for each country or region, a limited number of options may be available for payment, packaging and delivery.
+Additionally, non-functional requirements, defined by SLA may apply.
+
+In this context, the user supplies the list of books, his location and payment information and a composite web service should be generated to satisfy the order.
+The generated service composition should pick each book at the nearest warehouse, in order to minimize the costs of delivery and processing.
+Additional requirements, such as delivery time, may apply.
+
+In order to produce a personalised service composition for each user, the algorithm in~\cite{UmbertoICWE2013} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
+The specification of each available service is also considered (this specification is given by each cloud provider).
+~\hfill\openbox
+\end{example}
+
+The next example illustrates one of the limits of the automatic composition algorithm.
+
+\begin{example}[Incremental queries]\label{Ex:rew2}
+Let us return to the global bookstore of Example~\ref{Ex:rew1}.
+Let us suppose that the sales data is needed to produce daily and weekly ``\textit{Top 500}'' best-selling lists.
+In this case, each warehouse database will be queried and the list will be produced by adding data obtained from them.
+Let us supose that, in order to minimize the the communications between servers around the Globe, the \textit{Top 500} lists need to be produced incrementally.
+In this case, the composition produced by the service refinement may need to include an iteration.
+(The data produced by the warehouse servers will be processed in batches and the process will end once the list reaches the size of 500 titles.)
+
+As far as our knowledge, the incremental production of a solution is outside of the scope of the current solutions for rewriting service compositions and represents a challenge to the area.
+~\hfill\openbox
+\end{example}
 

### 2013-11-22 PositionPaper/incremental.tex
refs and minor changes

@@
 Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
-In this context, the \textit{Global as a View} (\textit{GAV}) methods of query rewriting~\cite{queryRewriting} are suitable.
-In the GAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available databases.
+In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
+In the LAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available databases.
 In the case of general services, we can use the specification of the composition to be produced as well as the specification of each available service.
@@
 
-Query rewriting techniques have been adapted to the context of service composition~\cite{queryRewriting}. 
-In~\cite{UmbertoICWE2013} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
+Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
+In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
 The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting,  known in the database domain.
@@
 
-The next example shows the main features of the approach proposed in~\cite{UmbertoICWE2013}.
+The next example shows the main features of the approach proposed in~\cite{CostaAMR13}.
 
@@
 
-In order to produce a personalised service composition for each user, the algorithm in~\cite{UmbertoICWE2013} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
+In order to produce a personalised service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
 The specification of each available service is also considered (this specification is given by each cloud provider).

### 2013-11-23 PositionPaper/incremental.tex
Incremental (SLA) + figure in Use Case

@@
 
-This first stage can be defined as a vertical mapping SLAs given the high level SLA described by the user (i.e.
-macroscopic constraints: execution time, pay / no pay, data reliability, data source).
-The system should be able to find relevant service compositions that respond to the query and, when combined, meet the constraints imposed by the user (High level SLA).
+This first stage of our data integration and provision process is  defined as a vertical mapping of SLAs that are expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source.
+The system should be able to find relevant service compositions that respond to the query  such that when combined, meet the constraints imposed by the user (High level SLA).
+One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
 
-One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user. 
-To meet this objective, it is necessary to compare the SLA services to combine, in order to check if their joint use is compatible with the individual SLA.
+To meet this objective, we assume that services export SLA's (agreed SLA's) that are sometimes of finer granularity than those defined by the user.
+So the challenge  is  to determine whether their joint use is compatible with the individual SLA.
 This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
@@
 %-----------------------------------------------------------------
-Generate a service coordination search space that can compute each subquery and can integrate the global result. 
-Each subquery is optimized with respect to user profile.
+Given the query rewritten as a service composition, the idea is then to optimize them and execute them.
+In our approach these queries are implemented as query worflows.
+A query workflow implements a service composition defining activities and a control flow.
+An activity is a program that implements the interaction with a data service (through a method call) and the processing of the data it provides; it can also implement an data processing operation such as filter, aggregation, correlation.
+The control flow defines the order in which activities must be executed (sequencially or in parallel).
+Service compositions defining subqueries are transformed into query workflows.
 
- Dispatch the execution of subqueries, integrate them into a result. Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions
+A query worflow can be optimized with respect to the preferences expressed in a user profile: the economic cost, the execution time, the energy necessary to execute it.
+Therefore, given a service coordination expressing a (sub)query we compute a search space of all possibile query workflows that can implement a query (all activities sequentially, as much activities in parallel as possible, conmuting activities).
+Each quey workflow has an estimated multi-dimensional cost, computing according to some measures of the computed SLA.
+The "optimum" query workflow is the one whose cost is the closest to the expected requirements of the user.
+Since the cost is multidimensional, several query workflows can be close to the user preferences.
+For this reason, we use a top-k algorithm for choosing an ordered set of "best" query workflows.
+One of these queries is executed by a workflow engine.
 
@@
 This implies mapping between property and expressed clauses being.
+
+Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions

### 2013-11-24 PositionPaper/incremental.tex
Stabilizing section 3 ... a less abstract idea on how to deal with agreed and global SLA

@@
 
-This first stage of our data integration and provision process is  defined as a vertical mapping of SLAs that are expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source.
-The system should be able to find relevant service compositions that respond to the query  such that when combined, meet the constraints imposed by the user (High level SLA).
+This first stage of our data integration and provision process is  defined as a vertical mapping of SLAs that are expressed as macroscopic constraints (i.e., high level SLA): execution time, pay / no pay, data reliability, data source.
+The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user.
 One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
 
-To meet this objective, we assume that services export SLA's (agreed SLA's) that are sometimes of finer granularity than those defined by the user.
-So the challenge  is  to determine whether their joint use is compatible with the individual SLA.
+To meet this objective, we assume that services export SLA's (i.e., agreed SLA's) that are sometimes of finer granularity than those defined by the user.
+The service SLA measures are are: response time, availability, price/call, reliability, data production rate.
+Other measures are associated to the conditions in which the service is called.
+For example the cost, which includes the price of calling the service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
+With this measures the service has an associated agreed SLA expressed through a XML document using the specification WSLA (Web service level agreement \footnote{http://www.research.ibm.com/people/a/akeller/Data/WSLASpecV1-20030128.pdf}).
+Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
+
+The challenge  is  to determine whether their joint use is compatible with the individual SLA.
 This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
 
- \begin{enumerate}
-\item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query.
+% \begin{enumerate}
+%\item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query.
 Data providers are filtered in this way, since only those agreed SLA that can be combined into a global SLA that can fulfill the user preferences are considered for retrieving data.
 
-  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.
+%  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.
 
-  \item Negociation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
+ % \item 
+ Negociation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
 This negotiation can be expensive and may not scale well.
-  \end{enumerate}
+ % \end{enumerate}
 
@@
 %-----------------------------------------------------------------
-{\color{red}
-See wether a similar Q has been already rewritten or rewrite it.
+%{\color{red}
+%See wether a similar Q has been already rewritten or rewrite it.
 Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
 The subqueries represent the possible combination of services that can answer the initial query with given SLA.
-}
+%}
 

### 2013-11-24 PositionPaper/incremental.tex
no message

@@
 
-This first stage of our data integration and provision process is  defined as a vertical mapping of SLAs that are expressed as macroscopic constraints (i.e., high level SLA): execution time, pay / no pay, data reliability, data source.
+The first stage of our proposed data integration and provision process is  defined as a vertical mapping of high level and agreed SLAs.
+Hig level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source.
 The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user.
@@
 For example the cost, which includes the price of calling the service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
-With this measures the service has an associated agreed SLA expressed through a XML document using the specification WSLA (Web service level agreement \footnote{http://www.research.ibm.com/people/a/akeller/Data/WSLASpecV1-20030128.pdf}).
+With this measures the service has an associated agreed SLA expressed through a XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/Data/WSLASpecV1-20030128.pdf}).
 Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
@@
 The challenge  is  to determine whether their joint use is compatible with the individual SLA.
+We propose a classification of SLA measures represents the relationship between fine grained measures used by agree SLAs and coarse grained measures used in globel SLAs.
+It specifies also how to compute coarse grained measures with fine grained ones.
+Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
+
 This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
-
+%
+%
 % \begin{enumerate}
@@
 Data providers are filtered in this way, since only those agreed SLA that can be combined into a global SLA that can fulfill the user preferences are considered for retrieving data.
-
+%
+ % 
 %  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.
-
+  %
  % \item 
@@
 Query rewriting is a well-known problem for the database community.
-The problem consists on transforming an abstract query into a set (or list) of lower-level queries to the available databases.
+The problem consists in transforming an abstract query into a set (or list) of lower-level queries to the available databases.
 Traditionally, the abstract query is a query over a set of views and the lower-level queries are performed on the available databases whose information compose the view. 
@@
 Both database queries and service invocations may be represented using a similar syntax.
-Indeed, the interfaces to relational databases and information-providing\footnote{Services that do not perform changes in the data they use.} services are exactly the same.
-In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services (which take the place of the available database queries).
+Indeed, the interfaces to relational databases and information-provision
+%\footnote{Services that do not perform changes in the data they use.} 
+services are exactly the same.
+In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
+%(which take the place of the available database queries).
 
-The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-providing case.
+The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
 Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
@@
 In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting,  known in the database domain.
+The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
+%known in the database domain.
 The proposed approach consists in generating several translations of an abstract service specification into compositions
 over concrete  services. 
-The solutions proposed are ranked and may be coded into concrete orchestrations.
-
-The next example shows the main features of the approach proposed in~\cite{CostaAMR13}.
+The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.
+The next example shows the main features of the approach proposed in~\cite{CostaAMR13} and that is extended in the case of SLA guided services based data integration.
 
@@
 In this case, the composition produced by the service refinement may need to include an iteration.
-(The data produced by the warehouse servers will be processed in batches and the process will end once the list reaches the size of 500 titles.)
+The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the size of 500 titles.
 

### 2013-11-24 PositionPaper/conclusions.tex
With conclusions

This paper introduces the challenge of integrating data from distributed data services deployed on different cloud providers guided by service level agreement. The data integratio problem is stated as a continuos data provision problem that has ans associated economic cost and that uses automatic learning techniques for ensuring different qualities of delivered data (fresh, precise, partial).

Current big data settings impose today to consider SLA and different data delivery models. We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-knowns solutions and adapted to this contexts. We are currently developing the strategies and algorithms sketched here applied to energy consumption applications as the one described in the paper and also to elections and political campaign data integration in order to guide decision making on campaign strategies.

### 2013-11-24 PositionPaper/incremental.tex
no message

@@
 %-----------------------------------------------------------------
-\subsection{Reducing the overhead of the evaluation process}
+\subsection{Monitoring the resources consumed by the evaluation process}
 \label{sec:queryProcessOpt}
@@
 
- It is  crucial to provide proactive mechanisms for optimizing the production of such SLA.
+ %It is  crucial to provide proactive mechanisms for optimizing the production of such SLA.
+
  We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results.
@@
 ).
-Given this proposal, we identify several issues:
-- Level modeling would require a model that allows the representation of SLA integration.
-- There should also be a template for representing the requirements expressed by the user
-- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
+%Given this proposal, we identify several issues:
+%- Level modeling would require a model that allows the representation of SLA integration.
+%- There should also be a template for representing the requirements expressed by the user
+%- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
 This implies mapping between property and expressed clauses being.
 
-Monitor the consumption of resources, the execution, time, behaviour ofi the services and make decisions
+Monitor the consumption of resources, the execution, time, behaviour of the services and make decisions

### 2013-11-25 PositionPaper/incremental.tex
small changes

@@
-We propose an SLA guided continuous data provision and integration approach that proposes three steps  starting from the processing of the request  to the delivery of the result sets.
+We propose an SLA guided, continuous data provision and integration approach that proposes three steps  starting from the processing of the request  to the delivery of the result sets.
 
@@
 The first stage of our proposed data integration and provision process is  defined as a vertical mapping of high level and agreed SLAs.
-Hig level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source.
+Higher level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source.
 The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user.
@@
 
-When a potential Internet client requires a list of books, a composed web service is generated, in order to fetch each book (from the nearest warehouse where the book is available) and to put in motion the payment and packing procedures.
+When an on-line client requires a list of books, a composed web service is generated, in order to fetch each book (from the nearest warehouse where the book is available) and to put in motion the payment and packing procedures.
 Depending on the location of the client, different conditions may apply on the selling and payment procedures.
@@
 
-In this context, the user supplies the list of books, his location and payment information and a composite web service should be generated to satisfy the order.
+In this context, the user supplies the list of books, his location and payment information and a composite web service should be generated to fulfill the order.
 The generated service composition should pick each book at the nearest warehouse, in order to minimize the costs of delivery and processing.
@@
 In order to produce a personalised service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
-The specification of each available service is also considered (this specification is given by each cloud provider).
+The specification of each available service is also considered (this specification should be given by the service provider).
 ~\hfill\openbox
@@
 
-As far as our knowledge, the incremental production of a solution is outside of the scope of the current solutions for rewriting service compositions and represents a challenge to the area.
+As far as our knowledge, the incremental production of a solution is outside of the scope of the current methods for rewriting service compositions and represents a challenge to the area.
 ~\hfill\openbox

### 2013-11-25 PositionPaper/relwork.tex
small changes

@@
 
+The advent of cloud computing imposed a new model for resource managing.
+The new model is not concerned with the \textit{limits} of resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources.
+Service Level Agreements (SLA)~\cite{SLA} can be used in thee context of cloud computing in order to establish those conditions.
+SLAs are bounding contracts between each service provider and their clients.
+The deployment of SLAs lies on two features: (i) the negotiation of conditions, agreed by both parts and (ii) the monitoring of these conditions during the use of each service.
+
+=====================
 Recent research works on SLA are devoted to the SLA extension to security concerns. Hale

### 2013-11-25 PositionPaper/incremental.tex
Incremental.tex more stable as time goes by ...

@@
 %-----------------------------------------------------------------
-\subsection{Computing query SLA}
+\subsection{Deriving a query SLA}
 \label{sec:slaModel}
@@
 
-The first stage of our proposed data integration and provision process is  defined as a vertical mapping of high level and agreed SLAs.
-Higher level SLA is expressed as macroscopic constraints: execution time, pay / no pay, data reliability, data source.
-The system  finds relevant service compositions that respond to the query  such that when combined, they meet the constraints imposed by the user.
-One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
+The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs that leads to a {\em derived SLA} that guides the evaluation of a query.
+A query has associated preferences  expressed as macroscopic constraints: execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode.
+These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assined storage space, number of requests, transfered Mega Octets, etc.).
+Given a query and its preferences statement, the system  finds relevant service compositions that produces results  such that when combined, they meet the required constraints.
 
-To meet this objective, we assume that services export SLA's (i.e., agreed SLA's) that are sometimes of finer granularity than those defined by the user.
-The service SLA measures are are: response time, availability, price/call, reliability, data production rate.
-Other measures are associated to the conditions in which the service is called.
-For example the cost, which includes the price of calling the service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
-With this measures the service has an associated agreed SLA expressed through a XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/Data/WSLASpecV1-20030128.pdf}).
+%One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
+
+We assume that services export SLA's (i.e., agreed SLA's) that define measures  of finer granularity than those defined by the user.
+The service SLA measures  are: response time, availability, price/call, reliability, data production rate.
+Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
+These measures are in general computed by monitoring the execution and conversations associted to services.
+For example the cost of retrieving the list of energy providers within a region with their KWatt cost provided that calls cost between 0,25 - 0,50 euros depending on the data service.
+This request  includes the price of calling a service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
 Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
+ Measures can be also hybrid, in the sense that they can be statically stated partially but they require to be precised at execution time.
+A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
 
-The challenge  is  to determine whether their joint use is compatible with the individual SLA.
-We propose a classification of SLA measures represents the relationship between fine grained measures used by agree SLAs and coarse grained measures used in globel SLAs.
+Given agreed SLA's and a user preferences statement the challenge is to compute a  {\em derived SLA} that  maps SLA measures and preferences attributes.
+The derived SLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures.
+The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.
+
+ We propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements.
 It specifies also how to compute coarse grained measures with fine grained ones.
+For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
+The derived SLA is can be seen as a set of equations that has to be solved during the execution of a service composition.
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
+We will discuss this issue in the next sections.
 
@@
 %-----------------------------------------------------------------
-\subsection{Monitoring the resources consumed by the evaluation process}
+\subsection{Dealing with the resources consumed by the evaluation process}
 \label{sec:queryProcessOpt}
@@
 
- We believe that the optimization of this process can occur at two levels, firstly at the level of SLA previously traded, and secondly at the level of partial or total results.
-Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not touching the data).
-For two different queries, they will be negotiated in the same way.
-These previously negotiated SLAs are reusable.
+ Our data provision and integration approach relys on data services deployed on one or different providers and it is delivered as a DaaS.
+This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
+It is thus important to optimize the use of these resources.
 
-In a second time, we think optimizing this process on the data storage mechanisms to cache intermediate results, individually or in partial or complete combination depending on the terms of SLA services (data access, intermediate storage capacity , cost of storage , etc ...
+ We believe that the optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
+Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service).
+Instead of recomputing the derived SLA every time, we propose to store it and reuse it for other queries.
+
+Second, precalculated queries and partial results can be also stored in cache or in a persistent supprt.
+Rewritting and optimization results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
+Being able of storing such SLAs will depend on the cloud subscription (data access, intermediate storage capacity , cost of storage , etc ...
 ).
@@
 
-Monitor the consumption of resources, the execution, time, behaviour of the services and make decisions
+As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
+In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transfered when services deliver results.
+These computations are used dynamically for instanciating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query.
+Since this is monitered dynamicalle, the evaluation of the query can be adapted if the SLA is not being respected anymore.

### 2013-11-25 PositionPaper/relwork.tex

@@
 SLAs are bounding contracts between each service provider and their clients.
-The deployment of SLAs lies on two features: (i) the negotiation of conditions, agreed by both parts and (ii) the monitoring of these conditions during the use of each service.
+The deployment of SLAs relies on two principles: (i) The negotiation of conditions, which are statically agreed between the parts and (ii) The monitoring of these conditions during the use of each service.
+
+The agreed conditions should be explicit and quantifiable.
+They should be part of the contract between the client and the service provider.
+Their quantifiable nature makes it possible for the conditions to appear as non-functional requirement to be imposed to each individual service.
+
+Monitoring SLAs is normally part of the infrastructure provided by the cloud.
+The user may verify that the service complies with the agreed SLA.
 
 =====================
+
 Recent research works on SLA are devoted to the SLA extension to security concerns. Hale

### 2013-11-25 PositionPaper/relwork.tex
relworks

@@
 Their quantifiable nature makes it possible for the conditions to appear as non-functional requirement to be imposed to each individual service.
+SLA could concern all types of services on the cloud (IaaS, PaaS or SaaS).
 
+SLA compliance may be ensured by construction or may be monitored during the execution of the service.
 Monitoring SLAs is normally part of the infrastructure provided by the cloud.
-The user may verify that the service complies with the agreed SLA.
+Service monitoring may incur in extra processing costs.
 
-=====================
+SLA currently exploited in the cloud allows service providers and cloud clients to limit the amount of resources that should be used.
+This limit may apply both for the service provider and the client (in the case of service invocation).
 
-Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
-and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
-working group. The extension allows security constraints to be expressed over the service description
+Negotiating a SLA may be a difficult task.
+On the server side, SLA are normally expressed in terms of \textit{low level} concepts, like size of the used storage or degree of virtualization. 
+On the client side, the interest is normally on \textit{higher level} concepts such as QoS requirements.
+Some recent proposals address the problem of filling this gap.  
+For instance,~\cite{5547150} propose a bottom-up approach, where a cloud component that acts autonomously based on low level monitored features after analysing them towards high level clauses expressed by the user.
+On the other side of the spectrum of solutions, \cite{Dastjerdi:2012:DOA:2275356.2275360} describe a \textit{Semantic SLA} which can be understood by all parties including providers, requestors, and monitoring services.
+Their goal is, starting from a high level SLA, to measure and identify how the SLA be declined at different layers in the cloud.
+
+{\color{red}
+One of the major objectives in the cloud is to anticipate SLA violation and to assess SLA failure cascading on violation detection. 
+\cite{Dastjerdi:2012:DOA:2275356.2275360} proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.  
+\cite{5547150} proposes to anticipate failure by analysing the monitored feature and to act by anticipation. 
+In \cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs. 
+}
+
+Recent research works on SLA are devoted to the SLA extension to security concerns. 
+\cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
+working group. 
+The extension allows security constraints to be expressed over the service description
 terms (SDTs) and the service level objectives (SLOs) of the SLA. 
-Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP.
-Luna and al
-work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool.
-The designed template is then used both to express user security requirements and CSP security provisions.
+Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different cloud service provider. 
+\cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
+The designed template is then used both to express user security requirements and cloud service provider security provisions.
 
-Another issue in the SLA management domain is how to let CSP offer fit the best user requirements.
+=====================================
+
+Another issue in the SLA management domain is how to let cloud service provider offer fit the best user requirements.
 In fact, current SLA are only resource oriented and lacks in expressing client requirement in service quality and characteristics.

### 2013-11-26 PositionPaper/incremental.tex
Incrementar et use case

@@
 
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA global computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA derivation computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
 The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
@@
 
-The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs that leads to a {\em derived SLA} that guides the evaluation of a query.
-A query has associated preferences  expressed as macroscopic constraints: execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode.
-These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assined storage space, number of requests, transfered Mega Octets, etc.).
-Given a query and its preferences statement, the system  finds relevant service compositions that produces results  such that when combined, they meet the required constraints.
+The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs.
+This  leads to a {\em derived SLA} that guides the evaluation of a query.
+A query has associated preferences  expressed as macroscopic constraints (i.e.
+user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode.
+These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
+Given a query and its preferences statement, the system  finds  service compositions that produce results   meeting the required constraints.
 
@@
 
-We assume that services export SLA's (i.e., agreed SLA's) that define measures  of finer granularity than those defined by the user.
+We assume that services export SLAs (i.e., agreed SLAs) that define measures  of finer granularity than those defined by the user.
 The service SLA measures  are: response time, availability, price/call, reliability, data production rate.
 Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-These measures are in general computed by monitoring the execution and conversations associted to services.
+These measures are, in general, computed by monitoring the execution and conversations associted to services.
 For example the cost of retrieving the list of energy providers within a region with their KWatt cost provided that calls cost between 0,25 - 0,50 euros depending on the data service.
@@
 For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The derived SLA is can be seen as a set of equations that has to be solved during the execution of a service composition.
+The derived SLA  can be seen as a set of inequations that have to be solved during the execution of a service composition.
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.

### 2013-11-26 PositionPaper/useCase.tex
examples
Incremental (SLA) + figure in Use Case
Stabilizing section 3 ... a less abstract idea on how to deal with agreed and global SLA
Incrementar et use case

@@
 \begin{figure*}
+\includegraphics[width=0.8\textwidth]{figs/arch.png}
 \caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
@@
 Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
-A energy exchange market is established in order to continuously monitor energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
+A energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
 
 \begin{figure*}
-\includegraphics[width=0.6\textwidth]{figs/arch.png}
+\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
 \caption{\label{fig:energyXChange} Energy exchange.}
@@
 
-In our approach energy producers are modelled as services with associated ``agreed'' SLAs for a given time window. 
-In general, we assume that several producers will be able to supply energy for a given period of time given specific QoS preferences expressed by a consumer. 
+In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
+In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
 An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
+In our example assume that there are several energy provision services (e$_1$, ...
+e$_n$) that can be independent or hubs:
+\begin{description}
+\item energyProvider.requestAvailability() $\rangle$ $<$ KWatt/h, cost, rate, location $>$ $\langle$
 
-\begin{itemize}
-\item Processing big data implied in the energy consumption observation 
-\item Computing energy consumption behavior models
-\item Analyse and optimize energy consumption versus respecting the comfort requirement of inhabitants
-\end{itemize}
-
-Need of efficient data processing solutions
+\item energyHub.requestAvailability() $\rangle$ $<$ {ID, KWatt/h, cost, rate, location $>$}$\langle$
+\end{description}
 

### 2013-11-26 PositionPaper/useCase.tex
Use Case

@@
-\begin{figure*}
-\includegraphics[width=0.8\textwidth]{figs/arch.png}
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/arch.png}
 \caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-\end{figure*}
+\end{figure}
 
@@
 An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
-In our example assume that there are several energy provision services (e$_1$, ...
-e$_n$) that can be independent or hubs:
+In our example assume that there are several energy provision services ({\sf e$_1$, ...
+e$_n$}) that can be independent or hubs integrating several energy providers:
 \begin{description}
-\item energyProvider.requestAvailability() $\rangle$ $<$ KWatt/h, cost, rate, location $>$ $\langle$
+\sf\footnotesize
+\item energyProvider.requestAvailability() $\rightarrow$ $\langle$KWatt/h, Ecost, rate, location$\rangle$
 
-\item energyHub.requestAvailability() $\rangle$ $<$ {ID, KWatt/h, cost, rate, location $>$}$\langle$
+\item energyHub.requestAvailability() $\rightarrow$  \{$\langle$ID, KWatt/h, cost, rate, location$\rangle$\}
+
 \end{description}
+
+Each service is deployed in different cloud provider and each exports an agreed SLA that specifies {\sf agreedSLA:$\langle$cost/call, maxCalls, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+Cloud providers define also their SLA contracts defining {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}.
 
@@
 Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query.
+
+ \paragraph{Derived SLA}
+
+  \paragraph{Computing service compositions}
+
+   \paragraph{Optimizing service compositions execution}

### 2013-11-26 PositionPaper/incremental.tex
Use case and incremental: more and more stability

@@
 Since this is monitered dynamicalle, the evaluation of the query can be adapted if the SLA is not being respected anymore.
+
+%-----------------------------------------------------------------
+\subsection{SLA based data integration system}
+\label{sec:architecture}
+%-----------------------------------------------------------------
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/arch.png}
+\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
+\end{figure}
+
+Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
+These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
+The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.

### 2013-11-26 PositionPaper/useCase.tex
Use case and incremental: more and more stability

@@
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/arch.png}
-\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-\end{figure}
-
-Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
-These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.
-
 Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
@@
 
-Each service is deployed in different cloud provider and each exports an agreed SLA that specifies {\sf agreedSLA:$\langle$cost/call, maxCalls, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
-Cloud providers define also their SLA contracts defining {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}.
+Each service is deployed in different cloud provider and each exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the disponibility of the service, the average response time when a method is called, the reliability, the privace of the produced data (whether they can be stored or not), the precision,freshness and provenance of the produced data.
+As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider.
+In contrast, the other measures are constantly computed by monitoring the conversations between the service and the applications that contact it.
+Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transfering data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+For exmaple some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
+zone 1 is Europe).
+If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.
+
+\begin{description}
+\sf\footnotesize
+ \item {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+
+ \item  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
+ \end{description}
 

### 2013-11-26 PositionPaper/useCase.tex
Use case: every time more complete

@@
 
- Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt?}.
-Assuming also that energy providers are represented by services exporting their SLA agreements and that can potentially be combined for answering the query.
+ Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}.
+
+ Assume that there are four civilian energy providers are represented by services  {\sf e$_1$, ...
+e$_4$} and two {\sf hub}s which are also services integrating energy providers communities {\sf h$_1$ and h$_2$}; there are two free location services exporting  the following interface {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$} meaning that given an IP address it returns the geographic position expresses as {\sf X} and {\sf Y}.
+t can potentially be combined for answering the query.
 

### 2013-11-26 PositionPaper/useCase.tex
More use case ...

@@
  Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}.
+The user preferences statement, includes her cloud provider contract and her quality preferences.
+ \begin{description}
+\sf\footnotesize
+
+ \item  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}.
+
+ \item {\sf preferencesStatement:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+
+ \end{description}
+ We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure with {\sf 0,05 cents per call,  8 Gigabytes of I/O volume/month, free data transfert cost within the same region,  Gigabyte of storage}.
+The user is ready to pay maximum {\sf 5 euros as total query cost}, she wants only {\sf green} energy providers (provenance), at least {\sf 85$\%$} of precision of provided data, even if they are not fresh, she wants at least {\sf 90$\%$} available services, with a response time of {\sf 0,01 seconds}.
 
@@
 e$_4$} and two {\sf hub}s which are also services integrating energy providers communities {\sf h$_1$ and h$_2$}; there are two free location services exporting  the following interface {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$} meaning that given an IP address it returns the geographic position expresses as {\sf X} and {\sf Y}.
-t can potentially be combined for answering the query.
+This services can potentially be combined for answering the query.
 
- \paragraph{Derived SLA}
+ \paragraph{Derived SLA} Som of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
+These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
 

### 2013-11-26 PositionPaper/useCase.tex
More and more use case

@@
 A energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
-
-\begin{figure*}
-\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
-\caption{\label{fig:energyXChange} Energy exchange.}
-\end{figure*}
 
@@
 e$_n$}) that can be independent or hubs integrating several energy providers:
-\begin{description}
+\begin{itemize}
 \sf\footnotesize
@@
 
-\end{description}
+\end{itemize}
 
@@
 
-\begin{description}
+\begin{itemize}
 \sf\footnotesize
@@
  \item  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
- \end{description}
+ \end{itemize}
 
@@
 The user preferences statement, includes her cloud provider contract and her quality preferences.
- \begin{description}
+ \begin{itemize}
 \sf\footnotesize
@@
 
- \item {\sf preferencesStatement:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+ \item {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}.
 
- \end{description}
+ \end{itemize}
  We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure with {\sf 0,05 cents per call,  8 Gigabytes of I/O volume/month, free data transfert cost within the same region,  Gigabyte of storage}.
@@
 
- \paragraph{Derived SLA} Som of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
+ %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
+ \paragraph{Derived SLA} 
+ %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
+ Some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
 These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
+ \begin{itemize}
+\sf\footnotesize
+ \item  query total cost: $\Sigma_{i = 1 ... n}$ s$_i$ + data transfer cost $\leq$ 5 euros
+ \item  total responseTime: $\Sigma_{j = 1 ... i}$ response time of services composed for ex(s$_j$) + data transfer cost $\leq$ 5 euros
+ \item availability: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}, 
+ \item freshness: non 
+ \item precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
+ \item provenance:  all services involved must be $green$
+ \item storage: {\em partial results size} $\leq 1 Giga$ 
+ \end{itemize}
 
+  %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
   \paragraph{Computing service compositions} 
+%.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .   
+  Some of the inequations of the derived SLA are included in the service compositions that can potentially answer the query given a set of services that can possibly be composedL In the case of our query example the following composition can be used for answering it.
+  \begin{description}
+\sf\footnotesize
+\item Q$_1$ $\rightarrow$  \\$\langle$X$_1$,Y$_1$ $\rangle$ = loc$_1$(IP) $\parallel$  \\$\langle$ X$_2$,Y$_2$ $\rangle$ = loc$_1$(Eprovider), \\D= eucledianDistance(X$_1$,Y$_1$,X$_2$,Y$_2$), \\(
+$\langle$ C$_1$, E$_1$ $\rangle$ = e$_1$() $\parallel$ ...$\parallel$ $\langle$ C$_n$, E$_n$ $\rangle$ = e$_4$()), \\D $\leq$ 1.5 Km,\\ sum(C$_1$:C$_n$) $\leq$ 5, \\ sum(E$_1$:E$_n$) $\leq$ 1000 Kwatts/h, \\ totalResponseTime  $\leq$ 10 seg
+  \end{description}
+
+  In fact our apporaches would generate k service compoisions combining as much as possible the services available such that the constraints of the derived SLA are verified.
 
    \paragraph{Optimizing service compositions execution}
+% \begin{figure*}
+%\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
+%\caption{\label{fig:energyXChange} Energy exchange.}
+%\end{figure*}

### 2013-11-27 PositionPaper/useCase.tex
working...

@@
-Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
-Producers are characterized according to their location, the amount of energy in kWatts-hour that they can sell, the cost, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance.
-Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
-A energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
+Consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
+Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance.
+Consumers are described by their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
+An energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
 
-In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
+In our approach, energy producers are modelled as services with associated ``agreed'' SLAs. 
 In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
 An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. 
-In our example assume that there are several energy provision services ({\sf e$_1$, ...
-e$_n$}) that can be independent or hubs integrating several energy providers:
+In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
+Each of them is specified by a clause:
 \begin{itemize}
 \sf\footnotesize
-\item energyProvider.requestAvailability() $\rightarrow$ $\langle$KWatt/h, Ecost, rate, location$\rangle$
-
-\item energyHub.requestAvailability() $\rightarrow$  \{$\langle$ID, KWatt/h, cost, rate, location$\rangle$\}
-
+\item e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
 \end{itemize}
 
-Each service is deployed in different cloud provider and each exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the disponibility of the service, the average response time when a method is called, the reliability, the privace of the produced data (whether they can be stored or not), the precision,freshness and provenance of the produced data.
+Services are deployed in different cloud providers and each service exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data.
 As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
-In contrast, the other measures are constantly computed by monitoring the conversations between the service and the applications that contact it.
-Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transfering data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
-For exmaple some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
+In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  
+Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
 zone 1 is Europe).
@@
 
+    %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  
     \paragraph{Optimizing service compositions execution} 
+ %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .     
+    A service composition expressed in Datalog is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
+In the case of {\sf Q$_1$} the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially.
+Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1,5 Km., followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
+
+    Once the search space has been computed the QWs are filtered according to their economic and execution time costs.
+The QWs that minimize this cost are identified and ordered accoding to their conformance to the user preferences statement.
+
 % \begin{figure*}

### 2013-11-27 PositionPaper/useCase.tex
use case

@@
 Each of them is specified by a clause:
-\begin{itemize}
-\sf\footnotesize
-\item e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
-\end{itemize}
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
+\end{trivlist}
 
@@
 
-\begin{itemize}
-\sf\footnotesize
- \item {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
 
- \item  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
- \end{itemize}
+ \item[~$\bullet$ ]  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
+ \end{trivlist}
 
- Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}.
-The user preferences statement, includes her cloud provider contract and her quality preferences.
- \begin{itemize}
-\sf\footnotesize
+Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
+For instance, \textit{List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}. 
+The user preferences statement would include their cloud provider contract and quality preferences:
 
- \item  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}.
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ]  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}. 
+\item[~$\bullet$ ] {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}. 
+\end{trivlist}
 
- \item {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}.
+We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
+The user is ready to pay maximum {\sf \$5 as total query cost}; she requests that only {\sf green} energy providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} and with a response time of {\sf 0,01 seconds}.
 
- \end{itemize}
- We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure with {\sf 0,05 cents per call,  8 Gigabytes of I/O volume/month, free data transfert cost within the same region,  Gigabyte of storage}.
-The user is ready to pay maximum {\sf 5 euros as total query cost}, she wants only {\sf green} energy providers (provenance), at least {\sf 85$\%$} of precision of provided data, even if they are not fresh, she wants at least {\sf 90$\%$} available services, with a response time of {\sf 0,01 seconds}.
-
- Assume that there are four civilian energy providers are represented by services  {\sf e$_1$, ...
-e$_4$} and two {\sf hub}s which are also services integrating energy providers communities {\sf h$_1$ and h$_2$}; there are two free location services exporting  the following interface {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$} meaning that given an IP address it returns the geographic position expresses as {\sf X} and {\sf Y}.
-This services can potentially be combined for answering the query.
+Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
+Hubs will store information about (surplus) energy, available from particular users.
+We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
+We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
+All these services can potentially be combined for answering the query.
 
@@
 These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
- \begin{itemize}
-\sf\footnotesize
- \item  query total cost: $\Sigma_{i = 1 ... n}$ s$_i$ + data transfer cost $\leq$ 5 euros
- \item  total responseTime: $\Sigma_{j = 1 ... i}$ response time of services composed for ex(s$_j$) + data transfer cost $\leq$ 5 euros
- \item availability: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}, 
- \item freshness: non 
- \item precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
- \item provenance:  all services involved must be $green$
- \item storage: {\em partial results size} $\leq 1 Giga$ 
- \end{itemize}
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
+ \item[~$\bullet$ ] total response time: of services + data transfer
+ \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
+ \item[~$\bullet$ ] freshness: non 
+ \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
+ \item[~$\bullet$ ] provenance:  all services involved must be $green$
+ \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1 Giga$ 
+ \end{trivlist}
 
-  %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
+%...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---... 
   \paragraph{Computing service compositions} 
-%.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .   
-  Some of the inequations of the derived SLA are included in the service compositions that can potentially answer the query given a set of services that can possibly be composedL In the case of our query example the following composition can be used for answering it.
-  \begin{description}
-\sf\footnotesize
-\item Q$_1$ $\rightarrow$  \\$\langle$X$_1$,Y$_1$ $\rangle$ = loc$_1$(IP) $\parallel$  \\$\langle$ X$_2$,Y$_2$ $\rangle$ = loc$_1$(Eprovider), \\D= eucledianDistance(X$_1$,Y$_1$,X$_2$,Y$_2$), \\(
-$\langle$ C$_1$, E$_1$ $\rangle$ = e$_1$() $\parallel$ ...$\parallel$ $\langle$ C$_n$, E$_n$ $\rangle$ = e$_4$()), \\D $\leq$ 1.5 Km,\\ sum(C$_1$:C$_n$) $\leq$ 5, \\ sum(E$_1$:E$_n$) $\leq$ 1000 Kwatts/h, \\ totalResponseTime  $\leq$ 10 seg
-  \end{description}
+%...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---... ...---...
 
-  In fact our apporaches would generate k service compoisions combining as much as possible the services available such that the constraints of the derived SLA are verified.
+Given a a set of services that can possibly be composed and the derived SLA, a service cmposition must be produced.
+Some of the inequations of the derived SLA should be included in the service compositions that answer the query.
+In the case of our query example the following composition can be used for answering it:
+\begin{eqnarray*}
+Q_1 &\equiv&
+   \langle X_1,Y_1\rangle = loc_1(IP), \\
+&& \langle X_2,Y_2 \rangle = loc_1(Eprovider), \\
+&& D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
+&& \langle C_1, E_1 \rangle = e_1(\dots), \dots \langle C_4, E_4 \rangle = e_4(\dots), \\
+&& D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
+&& sum(E_1:E_4) \geq 1000\ \mathsf{kw-h}, \\
+&& \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
+\end{eqnarray*}
+
+  In fact our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
+One challenge of this is to generate incremental queries.
 
@@
 %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .     
-    A service composition expressed in Datalog is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
-In the case of {\sf Q$_1$} the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially.
-Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1,5 Km., followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
+A service composition (expressed in a Datalog-like syntax) is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
+In the case of $Q_1$ above, the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. 
+Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1.5 Km, followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
 
     Once the search space has been computed the QWs are filtered according to their economic and execution time costs.
-The QWs that minimize this cost are identified and ordered accoding to their conformance to the user preferences statement.
+The QWs that minimize this cost are identified and ordered according to their conformance to the user preferences statement.
 

### 2013-11-29 PositionPaper/incremental.tex
no message

@@
 
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it according as follows: (i) SLA derivation computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
-The results of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
+The output of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
 The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
-The following sections describe how this query is computed according to our approach.
+The following sections describe how this query is evaluated according to our approach.
 

### 2013-11-29 PositionPaper/useCase-old.tex
no message

Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
Producers are characterized according to their location, the amount of energy in kWatts-hour that they can sell, the cost, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance. 
Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy. 
A energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.

In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers:
\begin{itemize}
\sf\footnotesize
\item energyProvider.requestAvailability() $\rightarrow$ $\langle$KWatt/h, Ecost, rate, location$\rangle$

\item energyHub.requestAvailability() $\rightarrow$  \{$\langle$ID, KWatt/h, cost, rate, location$\rangle$\}

\end{itemize}

Each service is deployed in different cloud provider and each exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the disponibility of the service, the average response time when a method is called, the reliability, the privace of the produced data (whether they can be stored or not), the precision,freshness and provenance of the produced data. As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. In contrast, the other measures are constantly computed by monitoring the conversations between the service and the applications that contact it.  Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transfering data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}). For exmaple some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g. zone 1 is Europe). If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.

\begin{itemize}
\sf\footnotesize
 \item {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.

 \item  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
 \end{itemize}

 Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}. The user preferences statement, includes her cloud provider contract and her quality preferences. 
 \begin{itemize}
\sf\footnotesize

 \item  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}.

 \item {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}.

 \end{itemize}
 We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure with {\sf 0,05 cents per call,  8 Gigabytes of I/O volume/month, free data transfert cost within the same region,  Gigabyte of storage}. The user is ready to pay maximum {\sf 5 euros as total query cost}, she wants only {\sf green} energy providers (provenance), at least {\sf 85$\%$} of precision of provided data, even if they are not fresh, she wants at least {\sf 90$\%$} available services, with a response time of {\sf 0,01 seconds}.

 Assume that there are four civilian energy providers are represented by services  {\sf e$_1$, ... e$_4$} and two {\sf hub}s which are also services integrating energy providers communities {\sf h$_1$ and h$_2$}; there are two free location services exporting  the following interface {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$} meaning that given an IP address it returns the geographic position expresses as {\sf X} and {\sf Y}. This services can potentially be combined for answering the query.

 %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
 \paragraph{Derived SLA} 
 %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
 Some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query. These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
 \begin{itemize}
\sf\footnotesize
 \item  query total cost: $\Sigma_{i = 1 ... n}$ s$_i$ + data transfer cost $\leq$ 5 euros
 \item  total responseTime: $\Sigma_{j = 1 ... i}$ response time of services composed for ex(s$_j$) + data transfer cost $\leq$ 5 euros
 \item availability: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}, 
 \item freshness: non 
 \item precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
 \item provenance:  all services involved must be $green$
 \item storage: {\em partial results size} $\leq 1 Giga$ 
 \end{itemize}

  %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
  \paragraph{Computing service compositions} 
%.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .   
  Some of the inequations of the derived SLA are included in the service compositions that can potentially answer the query given a set of services that can possibly be composedL In the case of our query example the following composition can be used for answering it.
  \begin{description}
\sf\footnotesize
\item Q$_1$ $\rightarrow$  \\$\langle$X$_1$,Y$_1$ $\rangle$ = loc$_1$(IP) $\parallel$  \\$\langle$ X$_2$,Y$_2$ $\rangle$ = loc$_1$(Eprovider), \\D= eucledianDistance(X$_1$,Y$_1$,X$_2$,Y$_2$), \\(
$\langle$ C$_1$, E$_1$ $\rangle$ = e$_1$() $\parallel$ ...$\parallel$ $\langle$ C$_n$, E$_n$ $\rangle$ = e$_4$()), \\D $\leq$ 1.5 Km,\\ sum(C$_1$:C$_n$) $\leq$ 5, \\ sum(E$_1$:E$_n$) $\leq$ 1000 Kwatts/h, \\ totalResponseTime  $\leq$ 10 seg
  \end{description}

  In fact our apporaches would generate k service compoisions combining as much as possible the services available such that the constraints of the derived SLA are verified.

    %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  
    \paragraph{Optimizing service compositions execution} 
 %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .     
    A service composition expressed in Datalog is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective. In the case of {\sf Q$_1$} the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1,5 Km., followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.

    Once the search space has been computed the QWs are filtered according to their economic and execution time costs. The QWs that minimize this cost are identified and ordered accoding to their conformance to the user preferences statement.

% \begin{figure*}
%\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
%\caption{\label{fig:energyXChange} Energy exchange.}
%\end{figure*}

### 2013-11-29 PositionPaper/relwork.tex
no message

--- 2013-11-25 PositionPaper/relwork.tex
@@
 
-The advent of cloud computing imposed a new model for resource managing.
-The new model is not concerned with the \textit{limits} of resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources.
-Service Level Agreements (SLA)~\cite{SLA} can be used in thee context of cloud computing in order to establish those conditions.
-SLAs are bounding contracts between each service provider and their clients.
-The deployment of SLAs lies on two features: (i) the negotiation of conditions, agreed by both parts and (ii) the monitoring of these conditions during the use of each service.
+The advent of cloud computing imposed a new model for resource consuming that is not concerned
+ with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
+Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing in order to establish those conditions.
+The deployment of SLAs relies on two principles: (i) The negotiation of conditions, which are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
 
-=====================
-Recent research works on SLA are devoted to the SLA extension to security concerns. Hale
-and al. in \cite{6274042} propose an extension of the WSAgreement initially developed by the GRAAP
-working group. The extension allows security constraints to be expressed over the service description
+%The agreed conditions should be explicit and quantifiable.
+%They should be part of the contract between the client and the service provider.
+%Their quantifiable nature makes it possible for the conditions to appear as non-functional requirement to be imposed to each individual service.
+%SLA could concern all types of services on the cloud (IaaS, PaaS or SaaS).
+
+%SLA compliance may be ensured by construction or may be monitored during the execution of the service.
+%Monitoring SLAs is normally part of the infrastructure provided by the cloud.
+%Service monitoring may incur in extra processing costs.
+
+%SLA currently exploited in the cloud allows service providers and cloud clients to describe the amount of resources to be simultaneously used and also the conditions to use them.
+%This limit may apply both for the service provider and the client (in the case of service invocation).
+
+Negotiating a SLA may be a difficult task.
+Indeed, SLA are normally expressed in terms of \textit{low level} concepts, like size of the used storage or degree of virtualization. 
+On the client side, the interest is normally on \textit{higher level} concepts such as QoS requirements.
+Some recent proposals address this problem.  
+For instance,~\cite{5547150} propose a bottom-up approach, where a cloud component that acts autonomously based on low level monitored features after analysing them towards high level clauses expressed by the user.
+  \cite{Dastjerdi:2012:DOA:2275356.2275360} describe a \textit{Semantic SLA} which can be understood by all parties including providers, requestors, and monitoring services.
+Their goal is, starting from a high level SLA, to measure and identify how the SLA be declined at different layers in the cloud.
+In the domain of cloud data service, Ortiz and al  \cite{Ortiz:2013:VPS:2486767.2486772}
+  proposes a set of templates to the user of cloud data services, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
+The client has just to choose among proposed tempate the one that corresponds the best to her requirements.
+\cite{6141307} proposes a set of matching algorithms to identify compatible cloud provider for a given requirements by matching SLA parameters.
+In this work, SLA parameters of the cloud are defined in a cloud capable model and application's requirements are defined in an application requirement model.
+Those models specified firstly using RDF, are converted into graph structures
+From whom an Induced Propagation Graph is calculate to establish a correspondence between the cloud capability model and the application requirement model.
+
+%{\color{red}
+%One of the major objectives in the cloud is to anticipate SLA violation and to assess SLA failure cascading on violation detection. 
+%\cite{Dastjerdi:2012:DOA:2275356.2275360} proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.  
+%\cite{5547150} proposes to anticipate failure by analysing the monitored feature and to act by anticipation. 
+%In \cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs. 
+%}
+
+Some recent research works on SLA are devoted to the SLA extension to security concerns. 
+\cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
+working group. 
+The extension allows security constraints to be expressed over the service description
 terms (SDTs) and the service level objectives (SLOs) of the SLA. 
-Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different CSP.
-Luna and al
-work \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool.
-The designed template is then used both to express user security requirements and CSP security provisions.
+Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different cloud service provider. 
+\cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
+The designed template is then used both to express user security requirements and cloud service provider security provisions.
+Finally, some works tend to deal with SLA violation anticipation and SLA failure cascading on violation detection.
+\cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
+\cite{5614035} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
+in
+\cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
 
-Another issue in the SLA management domain is how to let CSP offer fit the best user requirements.
+%=====================================
+
+%Another issue in the SLA management domain is how to let cloud service provider offer fit the best user requirements.
 In fact, current SLA are only resource oriented and lacks in expressing client requirement in service quality and characteristics.
@@
 First by proposing predefined templates;.
-In \cite{Ortiz:2013:VPS:2486767.2486772}, the authors
-  a set of templates to the user of cloud data services, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
 
-  In \cite{LunaGarcia:2012:BCS:2381913.2381932,}, the authors propose to do a mapping of both user SecSLA requirements and CSP SecSLA provisions on a set of Quantitative Policy Tree(QPT), where atomic capabilities are mapped on leaves and intermediate represents coarse provisions with some logical operators (AND, OR).
+%  In \cite{LunaGarcia:2012:BCS:2381913.2381932,}, the authors propose to do a mapping of both user SecSLA requirements and CSP SecSLA provisions on a set of Quantitative Policy Tree(QPT), where atomic capabilities are mapped on leaves and intermediate represents coarse provisions with some logical operators (AND, OR).
 The mapping allows to give a quantitative benchmarking to each CSP offer with respect to user requirements that lets the user be able to make a choice.
@@
 Therefore in  \cite{Dastjerdi:2012:DOA:2275356.2275360}  the authors describe a semantic- SLA which can be understood by all parties including providers,requestors, and monitoring services.
-
-Finally, some works tend to deal with SLA violation anticipation and SLA failure cascading on violation detection.
-\cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
-\cite{5614035} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
-in
-\cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+% \cite{6141307} proposes a batterie of matching algorithms to identify compatible cloud provider for a given requirements by matching SLA parameters.
+%In this work, SLA parameters of the cloud are defined in a cloud capable model and application's requirements are defined
+%in an application requirement model. Those models specified firstly using RDF, are converted into graph structures using Jena APIs.
+%From those graphs a Pairwise Connectivity Graph is defined and an Induced Propagation Graph is calculated.
+%Pairwise Connectivity Graph is constituted by nodes called mappairs established when source and target nodes from initial graphs have the same property edge.
+%For the Propagation Graph each edge is given a weight.
+Finally, a Similarity propagation graph is constructed based on an initial mapping between the RDF models, where mapping nodes are compared (subclass, superclass, equivalence relation) and the mapping is used in a similarity flooding algorithm which is filtered out to only the instance node pairs that have similarity value greater than zero.
+%
 

### 2013-12-04 PositionPaper/incremental.tex
Use case within the sections and no longer in its own section

@@
 The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
-The following sections describe how this query is evaluated according to our approach.
+
+Consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
+Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance.
+Consumers are described by their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
+An energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
+
+In our approach, energy producers are modelled as services with associated ``agreed'' SLAs. 
+In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
+An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. 
+In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
+Each of them is specified by a clause:
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
+\end{trivlist}
+
+Services are deployed in different cloud providers and each service exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data.
+As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
+In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.  
+Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
+zone 1 is Europe).
+If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.
+
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+
+ \item[~$\bullet$ ]  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
+ \end{trivlist}
+
+Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
+For instance, \textit{List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}. 
+The user preferences statement would include their cloud provider contract and quality preferences:
+
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ]  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}. 
+\item[~$\bullet$ ] {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}. 
+\end{trivlist}
+
+We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
+The user is ready to pay maximum {\sf \$5 as total query cost}; she requests that only {\sf green} energy providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} and with a response time of {\sf 0,01 seconds}.
+
+Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
+Hubs will store information about (surplus) energy, available from particular users.
+We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
+We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
+All these services can potentially be combined for answering the query.
+
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/arch.png}
+\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
+\end{figure}
+
+Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
+These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
+The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following sections describe how this query is evaluated according to our approach.
 
 %-----------------------------------------------------------------
-\subsection{Deriving a query SLA}
+\section{Deriving a query SLA}
 \label{sec:slaModel}
@@
 
+Some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
+These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
+ \item[~$\bullet$ ] total response time: of services + data transfer
+ \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
+ \item[~$\bullet$ ] freshness: non 
+ \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
+ \item[~$\bullet$ ] provenance:  all services involved must be $green$
+ \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1 Giga$ 
+ \end{trivlist}
+
 %-----------------------------------------------------------------
-\subsection{Query Rewriting}
+\section{Query Rewriting}
 \label{sec:queryRew}
@@
 
+Given a a set of services that can possibly be composed and the derived SLA, a service cmposition must be produced.
+Some of the inequations of the derived SLA should be included in the service compositions that answer the query.
+In the case of our query example the following composition can be used for answering it:
+\begin{eqnarray*}
+Q_1 &\equiv&
+   \langle X_1,Y_1\rangle = loc_1(IP), \\
+&& \langle X_2,Y_2 \rangle = loc_1(Eprovider), \\
+&& D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
+&& \langle C_1, E_1 \rangle = e_1(\dots), \dots \langle C_4, E_4 \rangle = e_4(\dots), \\
+&& D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
+&& sum(E_1:E_4) \geq 1000\ \mathsf{kw-h}, \\
+&& \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
+\end{eqnarray*}
+
+  In fact our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
+One challenge of this is to generate incremental queries.
+
 %-----------------------------------------------------------------
@@
 One of these queries is executed by a workflow engine.
+
+A service composition (expressed in a Datalog-like syntax) is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
+In the case of $Q_1$ above, the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. 
+Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1.5 Km, followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
+
+    Once the search space has been computed the QWs are filtered according to their economic and execution time costs.
+The QWs that minimize this cost are identified and ordered according to their conformance to the user preferences statement.
 

### 2013-12-04 PositionPaper/incremental.tex
New version with example across all sections

@@
-We propose an SLA guided, continuous data provision and integration approach that proposes three steps  starting from the processing of the request  to the delivery of the result sets.
+We propose an SLA guided, continuous data provision and integration approach that proposes three steps  starting from the processing of the query  to the delivery of the results.
+Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries.
+Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
+%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
 
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) optimizing and integrating results.
-The output of these steps generate intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
-The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
+%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
+%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following lines describe how this query is evaluated according to our approach.
 
-Consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
-Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance.
+\begin{figure}
+\includegraphics[width=0.5\textwidth]{figs/arch.png}
+\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
+\end{figure}
+
+In order to illustrate our approach, consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
+Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it. 
 Consumers are described by their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
 An energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
-
-In our approach, energy producers are modelled as services with associated ``agreed'' SLAs. 
-In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
-An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. 
-In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
-Each of them is specified by a clause:
-\begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
-\end{trivlist}
 
@@
 
+According to our approach, energy producers are modelled as data services with associated ``agreed'' SLAs.
+In the example, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer.
+Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
+Hubs will store information about (surplus) energy, available from particular users.
+We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
+We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
+All these services can potentially be combined for answering queries.
+
+An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers. 
+In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
+Each of them is specified by a clause:
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
+\end{trivlist}
 Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
@@
 The user is ready to pay maximum {\sf \$5 as total query cost}; she requests that only {\sf green} energy providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} and with a response time of {\sf 0,01 seconds}.
-
-Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
-Hubs will store information about (surplus) energy, available from particular users.
-We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
-We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering the query.
-
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/arch.png}
-\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-\end{figure}
-
-Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
-These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following sections describe how this query is evaluated according to our approach.
 
@@
 This  leads to a {\em derived SLA} that guides the evaluation of a query.
+
 A query has associated preferences  expressed as macroscopic constraints (i.e.
@@
 These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
-Given a query and its preferences statement, the system  finds  service compositions that produce results   meeting the required constraints.
 
@@
 
-We assume that services export SLAs (i.e., agreed SLAs) that define measures  of finer granularity than those defined by the user.
-The service SLA measures  are: response time, availability, price/call, reliability, data production rate.
+We assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associted to services, and hybrid they can be statically stated  but they change at execution time.
+A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
+The service SLA measures  that we consider are: response time, availability, price/call, reliability, data production rate.
 Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-These measures are, in general, computed by monitoring the execution and conversations associted to services.
-For example the cost of retrieving the list of energy providers within a region with their KWatt cost provided that calls cost between 0,25 - 0,50 euros depending on the data service.
-This request  includes the price of calling a service, plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
-Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
- Measures can be also hybrid, in the sense that they can be statically stated partially but they require to be precised at execution time.
-A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
+
+An example of computed measure is the cost of retrieving the list of energy providers within a region with their KWatt cost.
+The cost is determined by the  cost of the calls.
+This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
+%Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
 
@@
 
- We propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements.
+In the example, some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
+These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
+ \item[~$\bullet$ ] total response time: of services + data transfer
+ \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
+ \item[~$\bullet$ ] freshness: non 
+ \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
+ \item[~$\bullet$ ] provenance:  all services involved must be $green$
+ \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1 Giga$ 
+ \end{trivlist}
+
+Therefore, we propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements.
 It specifies also how to compute coarse grained measures with fine grained ones.
@@
 
-Some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
-These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
-\begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
- \item[~$\bullet$ ] total response time: of services + data transfer
- \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
- \item[~$\bullet$ ] freshness: non 
- \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
- \item[~$\bullet$ ] provenance:  all services involved must be $green$
- \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1 Giga$ 
- \end{trivlist}
+ Given a query and its preferences statement, the system  finds  service compositions that produce results   meeting the required constraints, as discussed in the following section.
 
@@
 
-%-----------------------------------------------------------------
-\subsection{Executing optimized queries}
-\label{sec:queryOpt}
-%-----------------------------------------------------------------
-Given the query rewritten as a service composition, the idea is then to optimize them and execute them.
+%
+%%-----------------------------------------------------------------
+%\subsection{Executing optimized queries}
+%\label{sec:queryOpt}
+%%-----------------------------------------------------------------
+%Given the query rewritten as a service composition, the idea is then to optimize them and execute them.
 In our approach these queries are implemented as query worflows.
@@
 Service compositions defining subqueries are transformed into query workflows.
-
-A query worflow can be optimized with respect to the preferences expressed in a user profile: the economic cost, the execution time, the energy necessary to execute it.
+%
+%A query worflow can be optimized with respect to the preferences expressed in a user profile: the economic cost, the execution time, the energy necessary to execute it.
 Therefore, given a service coordination expressing a (sub)query we compute a search space of all possibile query workflows that can implement a query (all activities sequentially, as much activities in parallel as possible, conmuting activities).
@@
 One of these queries is executed by a workflow engine.
-
-A service composition (expressed in a Datalog-like syntax) is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
-In the case of $Q_1$ above, the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. 
-Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1.5 Km, followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
-
-    Once the search space has been computed the QWs are filtered according to their economic and execution time costs.
+%
+%
+%A service composition (expressed in a Datalog-like syntax) is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
+%In the case of $Q_1$ above, the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. 
+%Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1.5 Km, followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
+%    
+%    Once the search space has been computed the QWs are filtered according to their economic and execution time costs.
 The QWs that minimize this cost are identified and ordered according to their conformance to the user preferences statement.
@@
 %-----------------------------------------------------------------
-\subsection{Dealing with the resources consumed by the evaluation process}
+\section{Dealing with the resources consumed by the evaluation process}
 \label{sec:queryProcessOpt}
@@
 Second, precalculated queries and partial results can be also stored in cache or in a persistent supprt.
-Rewritting and optimization results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
-Being able of storing such SLAs will depend on the cloud subscription (data access, intermediate storage capacity , cost of storage , etc ...
+Rewritting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
+Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ...
 ).
@@
 
-%-----------------------------------------------------------------
-\subsection{SLA based data integration system}
-\label{sec:architecture}
-%-----------------------------------------------------------------
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/arch.png}
-\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-\end{figure}
-
-Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
-These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.
+%%-----------------------------------------------------------------
+%\subsection{SLA based data integration system}
+%\label{sec:architecture}
+%%-----------------------------------------------------------------
+%\begin{figure}
+%\includegraphics[width=0.5\textwidth]{figs/arch.png}
+%\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
+%\end{figure}
+%
+%Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
+%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
+%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.

### 2013-12-04 PositionPaper/introduction.tex
With conclusions
New version with example across all sections

@@
 The emergence of new architectures like the cloud opens new challenges to data processing. 
-The possibility of having unlimited Access to cloud resources and the ``pay as U go'' model make it possible to change the hypothesis under which current technology and solutions address the processing of huge volumes of data.
-Instead of designing processes and algorithms taking into consideration the limits on resources availability, the cloud sets the focus on the economic cost implied of using resources and producing results by parallelizing the use of computing resources while delivering data under subscription oriented cost models.
+The possibility of having unlimited access to cloud resources and the ``pay as U go'' model make it possible to change the hypothesis for addressing the processing of big  data collections. 
+Instead of designing processes and algorithms taking into consideration  limitations on resources availability, the cloud sets the focus on the economic cost implied of using resources and producing results by parallelizing their use owhile delivering data under subscription oriented cost models.
 
-Current data management approaches on the cloud tend to use NoSQL stores for managing huge heterogeneous data collections (graph, key-value, tables, relational). 
-Yet, having such heterogeneous schema-less data stores, calls for efficient methods for integrating (correlating, associating, filtering) heterogeneous data collections taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality of service, e.g., trust, freshness, provenance, partial or total consistency.
-Existing data integration techniques based on mappings, views management, ontologies have to be revisited in order to integrate data that are weakly curated and described through metadata or schemas.
+Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
+Existing data integration techniques have to be revisited considering weakly curated and modeled data sets according to quality of service requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
+% the economic cost derived of using computing, memory and storage resources for processing them.
 
@@
 
-Our work intends to address data integration on a hybrid cloud guided by the SLA exported by different cloud providers and by several QoS measures associated to data collections properties: trust, privacy, economic cost.
-We aim to address big data integration d in a multi-cloud hybrid context. 
+Our work addresses big data colections integration  in a multi-cloud hybrid context guided by user preferences statements and SLA contracts exported by different cloud providers.
+The objective is to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies a QoS requirement rather that a more powerful cloud.
+
+Therefore this paper presents and approach proposing strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting for integrating data sets  according to user profiles.
 This implies several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed along different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 
-The objectives of our work are to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider. 
-Therefore we propose strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting for integrating data sets  according to user profiles.
 %Given the computational cost of a query evaluation and a user profile, our approach uses automatic learning techniques for generating knowledge out of every task and reducing query evaluation economic cost.
-
-This paper proposes data integration (lookup, aggregation, correlation) strategies adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies security requirement rather that a more powerful cloud but with less security guarantees in the SLA.
 
@@
 %Section \ref{sec:incremental} introduces on demand and incremental data integration strategies. 
-Section \ref{sec:useCase}presents a use case for illustrating the interest and use of our approach. Finally \ref{sec:conclusions} concludes the papers and discusses future work.
+%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 
+Finally \ref{sec:conclusions} concludes the papers and discusses future work.

### 2013-12-04 PositionPaper/relwork.tex
New version with example across all sections

@@
 
-Negotiating a SLA may be a difficult task.
-Indeed, SLA are normally expressed in terms of \textit{low level} concepts, like size of the used storage or degree of virtualization. 
-On the client side, the interest is normally on \textit{higher level} concepts such as QoS requirements.
-Some recent proposals address this problem.  
-For instance,~\cite{5547150} propose a bottom-up approach, where a cloud component that acts autonomously based on low level monitored features after analysing them towards high level clauses expressed by the user.
-  \cite{Dastjerdi:2012:DOA:2275356.2275360} describe a \textit{Semantic SLA} which can be understood by all parties including providers, requestors, and monitoring services.
-Their goal is, starting from a high level SLA, to measure and identify how the SLA be declined at different layers in the cloud.
-In the domain of cloud data service, Ortiz and al  \cite{Ortiz:2013:VPS:2486767.2486772}
-  proposes a set of templates to the user of cloud data services, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
-The client has just to choose among proposed tempate the one that corresponds the best to her requirements.
-\cite{6141307} proposes a set of matching algorithms to identify compatible cloud provider for a given requirements by matching SLA parameters.
-In this work, SLA parameters of the cloud are defined in a cloud capable model and application's requirements are defined in an application requirement model.
-Those models specified firstly using RDF, are converted into graph structures
-From whom an Induced Propagation Graph is calculate to establish a correspondence between the cloud capability model and the application requirement model.
+%Negotiating a SLA may be a difficult task.
+%Indeed, 
+SLAs are normally expressed in terms of \textit{low level} concepts, like the storage space size  or the degree of virtualization. 
+On the user side, the interest is normally on \textit{higher level} concepts such as QoS requirements.
+The challenge is thus, to couple cloud SLA terms with user ones in order to agree the conditions in which they will interact.
+Existin works use matching and negociation techniques for addressing this challenge.
+For instance,~\cite{5547150} 
+proposes a bottom-up approach based on a cloud component that monitors low level measures, analyses and matches them to high level clauses expressed by the user.
+  \cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.
+Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  \cite{Ortiz:2013:VPS:2486767.2486772}
+  proposes a set of templates  cloud data services users, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
+The client  chooses among the proposed tempates the one that best corresponds   to her requirements.
+\cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters.
+Cloud SLA parameters and application requirements are represented by two models using RDF.
+RDF definitions are then converted into graph representations.
+An Induced Propagation Graph is calculated using both models to establish a correspondence between them.
 
@@
 
-Some recent research works on SLA are devoted to the SLA extension to security concerns. 
+Recent  works on SLA are devoted to extend  SLA for including  security concerns. 
 \cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
 working group. 
-The extension allows security constraints to be expressed over the service description
+Security constraints are expressed over the service description
 terms (SDTs) and the service level objectives (SLOs) of the SLA. 
-Consequently, this leads to a certain kind of security expression interoperability and lets the client to be able to compare security level of different cloud service provider. 
+This leads to an interoperable security expression that can be used by users for comparing security levels of different cloud service providers. 
 \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
-The designed template is then used both to express user security requirements and cloud service provider security provisions.
-Finally, some works tend to deal with SLA violation anticipation and SLA failure cascading on violation detection.
-\cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
-\cite{5614035} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
-in
-\cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+The designed template is then used both to express user security requirements and cloud service provider security provision.
+Finally, some works  deal with SLA violation anticipation and SLA failure cascading on violation detection.
+\cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency model using Web Service Modeling Ontology (WSMO) to build a knowledge database.
+\cite{5614035} proposes to anticipate failure by analysing the monitored feature.
+\cite{5614035} proposes LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
 

### 2013-12-05 PositionPaper/incremental.tex
Minor changes

@@
-We propose an SLA guided, continuous data provision and integration approach that proposes three steps  starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, time the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries.
+We propose an SLA guided, continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
+Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA’s. 
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries.
 Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
@@
 Services are deployed in different cloud providers and each service exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data.
+
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
+
+ \end{trivlist}
+
 As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
+
+In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
+Each of them is specified by a clause:
+\begin{trivlist}\sf\footnotesize
+\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
+\end{trivlist}
+
 Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
@@
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
-
+%\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}. 
+% 
  \item[~$\bullet$ ]  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
@@
 An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
-In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
-Each of them is specified by a clause:
-\begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
-\end{trivlist}
+
 Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.

### 2013-12-05 PositionPaper/introduction.tex
Minor changes

@@
-The emergence of new architectures like the cloud opens new challenges to data processing. 
-The possibility of having unlimited access to cloud resources and the ``pay as U go'' model make it possible to change the hypothesis for addressing the processing of big  data collections. 
+The emergence of new architectures like the cloud opens new opprtunities to data processing. 
+The possibility of having unlimited access to cloud resources and the ``pay as U go'' model make it possible to change the hypothesis for processing big  data collections. 
 Instead of designing processes and algorithms taking into consideration  limitations on resources availability, the cloud sets the focus on the economic cost implied of using resources and producing results by parallelizing their use owhile delivering data under subscription oriented cost models.
@@
 Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
-Existing data integration techniques have to be revisited considering weakly curated and modeled data sets according to quality of service requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
+Existing data integration techniques have to be revisited considering weakly curated and modeled data sets.
+This can be done according to quality of service requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
 % the economic cost derived of using computing, memory and storage resources for processing them.
@@
 
-Our work addresses big data colections integration  in a multi-cloud hybrid context guided by user preferences statements and SLA contracts exported by different cloud providers.
-The objective is to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies a QoS requirement rather that a more powerful cloud.
+Our work addresses big data collections integration  in a multi-cloud hybrid context guided by user preferences statements and SLA contracts exported by different cloud providers.
+The objective is to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies a QoS requirement rather that a more powerful one.
 
-Therefore this paper presents and approach proposing strategies for computing integrated SLA’s according to agreed SLA’s proposed by services and optimized and adaptable query rewriting for integrating data sets  according to user profiles.
-This implies several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed along different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
+Therefore this paper presents an approach proposing strategies for computing integrated SLA’s according to agreed SLA’s exported by services  and adaptable query rewriting for integrating data sets  according to user preference statements.
+This implies to consider several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 

### 2013-12-05 PositionPaper/incremental.tex
energy example...

@@
 The user is ready to pay maximum {\sf \$5 as total query cost}; she requests that only {\sf green} energy providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} and with a response time of {\sf 0,01 seconds}.
+
+As usual, SLAs will be represented as conditions over variables that will be used in the query.
+In this context, the compliance to the SLAs will drive the query rewriting process.
+Indeed, our rewriting process will proceed in stages.
+User preferences and user SLAs will be used to produce derived SLA to be added to the query. 
+These SLAs will influence the choice of data/service providers.
+The SLA proposed by the chosen providers need to be combined with the conditions on each proposed rewriting of the query.
+These combination will influence the decision about the actual services to be used.
 
@@
 \begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the case of generating sales reports for a global bookstore.
-This hypothetical bookstore sells books both at about 300 shops around the globe as well as via Internet.
-The bookstore has four international warehouses, located in four different continents.
-The bookstore uses the services of three different cloud providers.
+Let us consider the case of a smart city, where particulars can participate on an energy trading pool.
+We suppose that this hypothetical city has a large number of households that are capable of selling their energy surplus to other consumers. 
+The city has four information hubs, located in four different neighbourhoods, connected to very small energy producers.
+Some other producers may be contacted directly, though the services of three different cloud providers.
 Each cloud provider exports their own interfaces.
+There exist SLAs defined for each individual energy provider server, each hub, and each cloud provider.
 
-Local shops use the nearest cloud provider.
-Internet transactions are processed by the Asian and South American cloud providers.
+When an on-line consumer requires a list of servers to buy energy from them, a composed web service is generated, in order to fetch each individual or hub service and to put in motion the energy reservation procedures.
+Depending on the location of the consumer and producers, different conditions may apply.
+Also the cloud providers may publish the conditions for using their services.
+All these conditions are expressed as user preferences and SLAs.
+Additionally, other non-functional requirements (such as authentication or security requirements) may apply.
 
-When an on-line client requires a list of books, a composed web service is generated, in order to fetch each book (from the nearest warehouse where the book is available) and to put in motion the payment and packing procedures.
-Depending on the location of the client, different conditions may apply on the selling and payment procedures.
-So, for each country or region, a limited number of options may be available for payment, packaging and delivery.
-Additionally, non-functional requirements, defined by SLA may apply.
-
-In this context, the user supplies the list of books, his location and payment information and a composite web service should be generated to fulfill the order.
-The generated service composition should pick each book at the nearest warehouse, in order to minimize the costs of delivery and processing.
-Additional requirements, such as delivery time, may apply.
+In this context, the user supplies an energy demand, his location and payment information and a composite web service should be generated to fulfil the order.
+The generated service composition should pick the nearest providers, in accordance to the agreed SLA.
 
@@
 The specification of each available service is also considered (this specification should be given by the service provider).
+The algorithm should be modified to take into account the different SLA.
 ~\hfill\openbox
@@
 \begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the global bookstore of Example~\ref{Ex:rew1}.
-Let us suppose that the sales data is needed to produce daily and weekly ``\textit{Top 500}'' best-selling lists.
-In this case, each warehouse database will be queried and the list will be produced by adding data obtained from them.
-Let us supose that, in order to minimize the the communications between servers around the Globe, the \textit{Top 500} lists need to be produced incrementally.
-In this case, the composition produced by the service refinement may need to include an iteration.
-The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the size of 500 titles.
+Let us return to the energy trade system of Example~\ref{Ex:rew1}.
+Let us suppose that the available energy data is needed to produce daily and weekly ``\textit{Star Providers for One MegaWatt-hour}'' producers lists.
+In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the one MegaWatt-hour capacity is reached.
+Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
+In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
+The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.
 
@@
 
-Given a a set of services that can possibly be composed and the derived SLA, a service cmposition must be produced.
+Given a a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
 Some of the inequations of the derived SLA should be included in the service compositions that answer the query.

### 2013-12-08 PositionPaper/incremental.tex
no message

@@
 
-Query rewriting is a well-known problem for the database community.
-The problem consists in transforming an abstract query into a set (or list) of lower-level queries to the available databases.
-Traditionally, the abstract query is a query over a set of views and the lower-level queries are performed on the available databases whose information compose the view. 
-The rewriting is guided by the schema of both abstract and concrete databases.
+Query rewriting is a well-known problem in the database domain.
+The problem consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
+%Traditionally, an abstract query is expressed over a set of views and the lower-level queries are performed on the available databases for retrieving the information necessary for composing a view. 
+Query rewriting is guided by the schema of  abstract and concrete databases.
 The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
 
-The query rewriting problem may be generalized to the case of services.
-Both database queries and service invocations may be represented using a similar syntax.
-Indeed, the interfaces to relational databases and information-provision
+The query rewriting problem can be generalized to the case of services.
+%known in the database domain.
+%Both database queries and service invocations may be represented using a similar syntax.
+%Indeed, the interfaces to relational databases and information-provision
 %\footnote{Services that do not perform changes in the data they use.} 
-services are exactly the same.
+%services are exactly the same.
 In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
 %(which take the place of the available database queries). 
+Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
+In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
+The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
 
@@
 In the LAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available databases.
-In the case of general services, we can use the specification of the composition to be produced as well as the specification of each available service.
+The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
 These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
 
-Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
-In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
-%known in the database domain.
-The proposed approach consists in generating several translations of an abstract service specification into compositions
+We propose an approach consists in generating several translations of an abstract service specification into compositions
 over concrete  services. 
@@
 \begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the case of a smart city, where particulars can participate on an energy trading pool.
-We suppose that this hypothetical city has a large number of households that are capable of selling their energy surplus to other consumers. 
+Let us consider the case of the smart city scenario, where particulars can participate on an energy trading pool.
+We suppose that this hypothetical city has a large number of households that sell their energy surplus to other consumers. 
 The city has four information hubs, located in four different neighbourhoods, connected to very small energy producers.
-Some other producers may be contacted directly, though the services of three different cloud providers.
-Each cloud provider exports their own interfaces.
-There exist SLAs defined for each individual energy provider server, each hub, and each cloud provider.
+Other producers are be contacted directly, though the services of three different cloud providers.
+Each cloud provider exports its own interfaces.
+ SLAs are defined for each individual energy provider server, each hub, and each cloud provider.
 
-When an on-line consumer requires a list of servers to buy energy from them, a composed web service is generated, in order to fetch each individual or hub service and to put in motion the energy reservation procedures.
-Depending on the location of the consumer and producers, different conditions may apply.
-Also the cloud providers may publish the conditions for using their services.
-All these conditions are expressed as user preferences and SLAs.
+When an on-line consumer searches  servers to buy energy, a composed web service is generated, in order to fetch each individual or hub service and to start  energy reservation procedures.
+Depending on the location of the consumer and producers, different conditions and constraints may apply.
+Also  cloud providers  publish the conditions for using their services.
+These conditions are expressed as user preferences and SLAs.
 Additionally, other non-functional requirements (such as authentication or security requirements) may apply.
 
-In this context, the user supplies an energy demand, his location and payment information and a composite web service should be generated to fulfil the order.
-The generated service composition should pick the nearest providers, in accordance to the agreed SLA.
+In this context, the user  expresses an energy order, her location and payment information. A composite web service is  generated to fulfil the order.
+The generated service composition should consider the nearest providers, in accordance to the agreed SLA.
 
@@
 The specification of each available service is also considered (this specification should be given by the service provider).
-The algorithm should be modified to take into account the different SLA.
-~\hfill\openbox
-\end{example}
-
-The next example illustrates one of the limits of the automatic composition algorithm.
-
-\begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the energy trade system of Example~\ref{Ex:rew1}.
-Let us suppose that the available energy data is needed to produce daily and weekly ``\textit{Star Providers for One MegaWatt-hour}'' producers lists.
-In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the one MegaWatt-hour capacity is reached.
-Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
-In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
-The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.
-
-As far as our knowledge, the incremental production of a solution is outside of the scope of the current methods for rewriting service compositions and represents a challenge to the area.
 ~\hfill\openbox
@@
   In fact our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
-One challenge of this is to generate incremental queries.
+%One challenge of this is to generate incremental queries.
+ Yet, the algorithm should be modified to take into account the different SLAs. The next example illustrates one of the limits of the automatic composition algorithm.
+
+\begin{example}[Incremental queries]\label{Ex:rew2}
+Let us return to the energy trade system of Example~\ref{Ex:rew1}.
+ Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{One MegaWatt-hour}''.
+In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the one MegaWatt-hour capacity is reached.
+Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
+In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
+The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.
+
+To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
+~\hfill\openbox
+\end{example}
 

### 2015-02-09 Workshop2015/relwork.tex
V0 - workshop paper

--- 2013-12-04 PositionPaper/relwork.tex
@@
  with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
-Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing in order to establish those conditions.
+Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing to establish those conditions.
 The deployment of SLAs relies on two principles: (i) The negotiation of conditions, which are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
@@
 The challenge is thus, to couple cloud SLA terms with user ones in order to agree the conditions in which they will interact.
-Existin works use matching and negociation techniques for addressing this challenge.
+Existing works use matching and negociation techniques for addressing this challenge.
 For instance,~\cite{5547150} 
@@
 Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  \cite{Ortiz:2013:VPS:2486767.2486772}
-  proposes a set of templates  cloud data services users, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
+  proposes a set of templates to  cloud data services users, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
 The client  chooses among the proposed tempates the one that best corresponds   to her requirements.

### 2015-02-22 Workshop2015/incremental.tex
V0 - workshop paper
General modification of the paper, all sections and a new one for describing the new use case

--- 2013-12-08 PositionPaper/incremental.tex
@@
 
-\begin{figure}
-\includegraphics[width=0.5\textwidth]{figs/arch.png}
+\begin{figure*}
+\includegraphics[width=0.99\textwidth]{arch.png}
 \caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-\end{figure}
+\end{figure*}
 
@@
 \item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}. 
-
  \end{trivlist}
@@
 
-%\begin{itemize}
-%\item Expression haut niveau du SLA en termes de préférences qui doit converger avec le SLA technique des services.
-%  \begin{itemize}
-%  \item (Souhait de temps de réponse, coût des services, espace de stockage,  
-%  \item Templates pour exprimer le SLA
-%  \item Intégration: modèle pivot de SLA
-%\end{itemize}
-%
-%\item SLA violation contrôlée avec des mechanisms de monitoring.
-%\item Que ce que devient l’intégration de données par rapport au SLA
-%\item Création dynamique de SLA → niche de marché: étant donnée deux SLA fabriquer un SLA d’intégration
-%\end{itemize}
-
 The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs.
@@
 These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
-
-%One may think to a first filter to remove the individual services which do not meet some or all of the constraints expressed by the user.
 
@@
 This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
-%Since we assume that services can be deployed on different cloud providers, measures and SLA threasholds can vary.
 
@@
  \item[~$\bullet$ ] provenance:  all services involved must be $green$
- \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1 Giga$ 
+ \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1$ GB
  \end{trivlist}
@@
 This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
-%
-%
-% \begin{enumerate}
-%\item Computation of a global SLA given the existing possible SLA agreed by data providers that can be called for answering the query.
-Data providers are filtered in this way, since only those agreed SLA that can be combined into a global SLA that can fulfill the user preferences are considered for retrieving data.
-%
- % 
-%  \item Filter the data providers that can potentially participate in the evaluation of the query taking into consideration the preferences associated to the query.
-  %
- % \item 
- Negociation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
+ Negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
 This negotiation can be expensive and may not scale well.
- % \end{enumerate}
 
@@
 %-----------------------------------------------------------------
-%{\color{red}
-%See wether a similar Q has been already rewritten or rewrite it.
-Executing a query requires first a semantic analysis which will subdivide R into a set of sub-queries, in such a way that each sub-query can be processed by a DataService deployed on the cloud.
-The subqueries represent the possible combination of services that can answer the initial query with given SLA.
-%}
 
@@
 The problem consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
-%Traditionally, an abstract query is expressed over a set of views and the lower-level queries are performed on the available databases for retrieving the information necessary for composing a view. 
 Query rewriting is guided by the schema of  abstract and concrete databases.
@@
 The query rewriting problem can be generalized to the case of services.
-%known in the database domain.
-%Both database queries and service invocations may be represented using a similar syntax.
-%Indeed, the interfaces to relational databases and information-provision
-%\footnote{Services that do not perform changes in the data they use.} 
-%services are exactly the same.
 In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
-%(which take the place of the available database queries). 
 Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
@@
 We suppose that this hypothetical city has a large number of households that sell their energy surplus to other consumers. 
-The city has four information hubs, located in four different neighbourhoods, connected to very small energy producers.
+The city has four information hubs, located in four different neighborhoods, connected to very small energy producers.
 Other producers are be contacted directly, though the services of three different cloud providers.
@@
 Given a a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-Some of the inequations of the derived SLA should be included in the service compositions that answer the query.
+Some of the unequations of the derived SLA should be included in the service compositions that answer the query.
 In the case of our query example the following composition can be used for answering it:
@@
   In fact our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
-%One challenge of this is to generate incremental queries.
  Yet, the algorithm should be modified to take into account the different SLAs. The next example illustrates one of the limits of the automatic composition algorithm.
@@
 
-%
-%%-----------------------------------------------------------------
-%\subsection{Executing optimized queries}
-%\label{sec:queryOpt}
-%%-----------------------------------------------------------------
-%Given the query rewritten as a service composition, the idea is then to optimize them and execute them.
-In our approach these queries are implemented as query worflows.
-A query workflow implements a service composition defining activities and a control flow.
-An activity is a program that implements the interaction with a data service (through a method call) and the processing of the data it provides; it can also implement an data processing operation such as filter, aggregation, correlation.
-The control flow defines the order in which activities must be executed (sequencially or in parallel).
-Service compositions defining subqueries are transformed into query workflows.
-%
-%A query worflow can be optimized with respect to the preferences expressed in a user profile: the economic cost, the execution time, the energy necessary to execute it.
-Therefore, given a service coordination expressing a (sub)query we compute a search space of all possibile query workflows that can implement a query (all activities sequentially, as much activities in parallel as possible, conmuting activities).
-Each quey workflow has an estimated multi-dimensional cost, computing according to some measures of the computed SLA.
-The "optimum" query workflow is the one whose cost is the closest to the expected requirements of the user.
-Since the cost is multidimensional, several query workflows can be close to the user preferences.
-For this reason, we use a top-k algorithm for choosing an ordered set of "best" query workflows.
-One of these queries is executed by a workflow engine.
-%
-%
-%A service composition (expressed in a Datalog-like syntax) is then transformed into a query workflow search space consisting of workflows with different control flows and where constraints serve to determine an optimization objective.
-%In the case of $Q_1$ above, the corresponding search space contains for example a workflow {\sf QW$_1$} where all activities are executed sequentially. 
-%Another one, {\sf QW$_2$}, with parallel activities programming the call to a location service for the user and the energy providers, then a filter activity selecting only services located not farther to 1.5 Km, followed by  parallel activities that compute the total cost of the energy to buy, the total amount of energy.
-%    
-%    Once the search space has been computed the QWs are filtered according to their economic and execution time costs.
-The QWs that minimize this cost are identified and ordered according to their conformance to the user preferences statement.
-
 %-----------------------------------------------------------------
@@
 %-----------------------------------------------------------------
-% Indeed, let consider a request R launched by a user who specifies a %number of constraints on the environment execution.
-
- %It is  crucial to provide proactive mechanisms for optimizing the production of such SLA.
-
  Our data provision and integration approach relys on data services deployed on one or different providers and it is delivered as a DaaS.
@@
 ).
-%Given this proposal, we identify several issues:
-%- Level modeling would require a model that allows the representation of SLA integration.
-%- There should also be a template for representing the requirements expressed by the user
-%- A mining component to identify, from the requirements expressed in the template by the user, and before the analysis of the application, the candidate integration SLA to use or adapt according to the request.
-This implies mapping between property and expressed clauses being.
 
@@
 Since this is monitered dynamicalle, the evaluation of the query can be adapted if the SLA is not being respected anymore.
-
-%%-----------------------------------------------------------------
-%\subsection{SLA based data integration system}
-%\label{sec:architecture}
-%%-----------------------------------------------------------------
-%\begin{figure}
-%\includegraphics[width=0.5\textwidth]{figs/arch.png}
-%\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
-%\end{figure}
-%
-%Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system that is supported by data services which are data providers deployed in a cloud and that provide agreed SLA’s.
-%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.

### 2015-02-22 Workshop2015/introduction.tex
V0 - workshop paper
General modification of the paper, all sections and a new one for describing the new use case

--- 2013-12-05 PositionPaper/introduction.tex
@@
-The emergence of new architectures like the cloud opens new opprtunities to data processing. 
-The possibility of having unlimited access to cloud resources and the ``pay as U go'' model make it possible to change the hypothesis for processing big  data collections. 
-Instead of designing processes and algorithms taking into consideration  limitations on resources availability, the cloud sets the focus on the economic cost implied of using resources and producing results by parallelizing their use owhile delivering data under subscription oriented cost models.
+This paper presents an approach for addressing  data collections integration  in a multi-cloud hybrid context guided by user preferences statements and SLA contracts exported by different cloud providers.
+The objective is to propose an SLA guided  data provision and integration system exported as a DaaS by a cloud provider that can be adapted according to user preferences on the way data can be delivered  such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies a QoS requirement rather that a more powerful one.
 
-Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their ``structural'' characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
+Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their "structural" characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
 Existing data integration techniques have to be revisited considering weakly curated and modeled data sets.
 This can be done according to quality of service requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
-% the economic cost derived of using computing, memory and storage resources for processing them.
 
-%{\color{green} 
-%Furthermore, security aspects are crucial in integrating big data.
-Indeed, the integration task must guarantee the integrity and privacy of data, the willingness of the clouds to  contribute to the security process through acceptable runtime environment conditions, and the adequacy of the proposed security levels to the services behind the integration operation.
-%}
-
-Our work addresses big data collections integration  in a multi-cloud hybrid context guided by user preferences statements and SLA contracts exported by different cloud providers.
-The objective is to propose an SLA guided continuous data provision and integration system exported as a DaaS by a cloud provider adapted to the vision of the economic model of the cloud such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies a QoS requirement rather that a more powerful one.
-
-Therefore this paper presents an approach proposing strategies for computing integrated SLA’s according to agreed SLA’s exported by services  and adaptable query rewriting for integrating data sets  according to user preference statements.
+Therefore this paper presents an approach proposing strategies for computing integrated SLA's according to agreed SLA's exported by services  and adaptable query rewriting for integrating data sets  according to user preference statements.
 This implies to consider several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
-
-%Given the computational cost of a query evaluation and a user profile, our approach uses automatic learning techniques for generating knowledge out of every task and reducing query evaluation economic cost.
 
@@
 Section \ref{sec:incremental} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by concilating SLA's provided by services and user's profiles expressing QoS preferences about the data they want to consume and the conditions in which they must be processed and delivered.
-%Section \ref{sec:incremental} introduces on demand and incremental data integration strategies. 
-%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 
+Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 
 Finally \ref{sec:conclusions} concludes the papers and discusses future work.

### 2015-02-22 Workshop2015/relwork.tex
General modification of the paper, all sections and a new one for describing the new use case

@@
 Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing to establish those conditions.
-The deployment of SLAs relies on two principles: (i) The negotiation of conditions, which are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
+The adoption of SLAs relies on two principles: (i) The negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
 
@@
 %Indeed, 
-SLAs are normally expressed in terms of \textit{low level} concepts, like the storage space size  or the degree of virtualization. 
-On the user side, the interest is normally on \textit{higher level} concepts such as QoS requirements.
-The challenge is thus, to couple cloud SLA terms with user ones in order to agree the conditions in which they will interact.
+SLAs are normally expressed in terms of \textit{technical} measures, like the storage space size  or the degree of virtualization. 
+On the user side, the interest is normally on \textit{service} delivery measures such as QoS requirements.
+The challenge is to couple technical and service delivery measures expressed in SLA in order to agree on the conditions in which they will interact.
 Existing works use matching and negociation techniques for addressing this challenge.
 For instance,~\cite{5547150} 
-proposes a bottom-up approach based on a cloud component that monitors low level measures, analyses and matches them to high level clauses expressed by the user.
+proposes a bottom-up approach based on a cloud component that monitors technical measures, analyses and matches them to service delivery (high level) clauses expressed by the user.
   \cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.

### 2015-02-22 Workshop2015/incremental.tex
Figures and general organization
Incremental & Use Case

@@
 We propose an SLA guided, continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA’s. 
+Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
 Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries.
@@
 \begin{figure*}
-\includegraphics[width=0.99\textwidth]{arch.png}
-\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}
+\center{
+\includegraphics[width=0.75\textwidth]{arch.png}
+\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}}
 \end{figure*}
 
-In order to illustrate our approach, consider a smart city that aims at being energy self-sustainable and produce and consume, as much as possible, energy within its geographic area. 
-Producers are characterized according to their location, the amount of energy in Kilowatts-hour that they can sell, the cost of that energy, and the time window in which they can produce it. 
-Consumers are described by their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
-An energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
+In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
+Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
+cost, inscription, or exchange unit), and the time window in which they can produce it.
+Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
+An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
 
@@
 
-In our example assume that there are several energy provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several energy providers. 
+In our example assume that there are several content provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several content providers. 
 Each of them is specified by a clause:
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(KW-h, Ecost, rate, location), \textit{SLA}$_i$
+\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(Type, Cost, Size, location), \textit{SLA}$_i$
 \end{trivlist}
@@
 
-According to our approach, energy producers are modelled as data services with associated ``agreed'' SLAs.
-In the example, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer.
-Assume that there are four household energy providers that can be queried individually and two hubs that collect information from the community smartmeters.
-Hubs will store information about (surplus) energy, available from particular users.
+According to our approach, content producers are modelled as data services with associated ``agreed'' SLAs.
+In the example, we assume that several producers will be able to supply equivalent content for a given period of time given specific  preferences expressed by a consumer.
+Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
+Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
 We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
@@
 
-An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
+A content request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
 
 Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, \textit{List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}. 
+For instance, \textit{List of English poetry content providers that can provision commented Emily Dickinson poems, in the next hour, that are close to my city that are free and that are labeled as experts?}.
 The user preferences statement would include their cloud provider contract and quality preferences:
@@
 
-We assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associted to services, and hybrid they can be statically stated  but they change at execution time.
+We assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
 A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
@@
 
-An example of computed measure is the cost of retrieving the list of energy providers within a region with their KWatt cost.
+An example of computed measure is the cost of retrieving the list of "expert" Emily Dickinson poems providers within a region with their cost.
 The cost is determined by the  cost of the calls.
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmision according to the amount of trasnmitted MegaOctets through the network and the type of subscription of the user for using the network.
+This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaOctets through the network and the type of subscription of the user for using the network.
 
@@
  \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
- \item[~$\bullet$ ] provenance:  all services involved must be $green$
+ \item[~$\bullet$ ] provenance:  all services involved must be $expert$
  \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1$ GB
@@
 For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The derived SLA  can be seen as a set of inequations that have to be solved during the execution of a service composition.
+The derived SLA  can be seen as a set of unequations that have to be solved during the execution of a service composition.
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
@@
 \begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the case of the smart city scenario, where particulars can participate on an energy trading pool.
-We suppose that this hypothetical city has a large number of households that sell their energy surplus to other consumers. 
-The city has four information hubs, located in four different neighborhoods, connected to very small energy producers.
-Other producers are be contacted directly, though the services of three different cloud providers.
+Let us consider the case of the MOOC scenario, where people can participate on an content trading pool.
+We suppose that this hypothetical MOOC has a large number of participants that sell their content  to other consumers. 
+The MOOC has four information hubs, located in four different geographic locations, connected to other content providers.
+Other content providers are  contacted directly, through the services of three different cloud providers.
 Each cloud provider exports its own interfaces.
- SLAs are defined for each individual energy provider server, each hub, and each cloud provider.
+ SLAs are defined for each individual content provider server, each hub, and each cloud provider.
 
-When an on-line consumer searches  servers to buy energy, a composed web service is generated, in order to fetch each individual or hub service and to start  energy reservation procedures.
+When an on-line consumer searches  servers to buy/retrieve content, a composed web service is generated, in order to fetch each individual or hub service and to start  content retrieval procedures.
 Depending on the location of the consumer and producers, different conditions and constraints may apply.
@@
 
-In this context, the user  expresses an energy order, her location and payment information. A composite web service is  generated to fulfil the order.
+In this context, the user  expresses a content order, her location and payment information. A composite web service is  generated to fulfill the order.
 The generated service composition should consider the nearest providers, in accordance to the agreed SLA.
 
-In order to produce a personalised service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
+In order to produce a personalized service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
 The specification of each available service is also considered (this specification should be given by the service provider).
@@
 Given a a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-Some of the unequations of the derived SLA should be included in the service compositions that answer the query.
+Some of the un-equations of the derived SLA should be included in the service compositions that answer the query.
 In the case of our query example the following composition can be used for answering it:
@@
    \langle X_1,Y_1\rangle = loc_1(IP), \\
-&& \langle X_2,Y_2 \rangle = loc_1(Eprovider), \\
+&& \langle X_2,Y_2 \rangle = loc_1(Cprovider), \\
 && D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
@@
 && D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
-&& sum(E_1:E_4) \geq 1000\ \mathsf{kw-h}, \\
+&& union(E_1:E_4) \geq 5\ \mathsf{Go}, \\
 && \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
@@
 Let us return to the energy trade system of Example~\ref{Ex:rew1}.
- Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{One MegaWatt-hour}''.
-In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the one MegaWatt-hour capacity is reached.
+ Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson peotry.
+In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
 Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
@@
 %-----------------------------------------------------------------
- Our data provision and integration approach relys on data services deployed on one or different providers and it is delivered as a DaaS.
+ Our data provision and integration approach relies on data services deployed on one or different providers and it is delivered as a DaaS.
 This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
@@
 
-Second, precalculated queries and partial results can be also stored in cache or in a persistent supprt.
-Rewritting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
+Second, precalculated queries and partial results can be also stored in cache or in a persistent support.
+Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
 Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ...
@@
 As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
-In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transfered when services deliver results.
-These computations are used dynamically for instanciating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query.
-Since this is monitered dynamicalle, the evaluation of the query can be adapted if the SLA is not being respected anymore.
+In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results.
+These computations are used dynamically for instantiating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query.
+Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.

### 2015-02-22 Workshop2015/useCase.tex
Figures and general organization
Incremental & Use Case

--- 2013-11-26 PositionPaper/useCase.tex
@@
-Consider a smart city that aims at being energy self-sustainable and produce and consume as much as possible, energy within its geographic area. 
-Producers are characterized according to their location, the amount of energy in kWatts-hour that they can sell, the cost, and the time window in which they can produce it, with a given service level agreement concerning their availability and fault tolerance.
-Consumers, give also their location, their energy requirements during a certain interval of time, the maximum total cost they are ready to pay, and quality of service requirements such as availability and how critical it is to consume this amount of energy.
-A energy exchange market is established in order to continuously trade  energy provision/consumption ensuring that all consumers will have the energy they require at every moment.
+\begin{figure*}
+\center{
+\includegraphics[width=0.65\textwidth]{use-case.png}
+\caption{General distributed data storage service.\label{fig:storage}}}
+\end{figure*}
 
-In our approach energy producers are modelled as services with associated ``agreed'' SLAs. 
-In general, we assume that several producers will be able to supply energy for a given period of time given specific  preferences expressed by a consumer. 
-An energy request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
-In our example assume that there are several energy provision services ({\sf e$_1$, ...
-e$_n$}) that can be independent or hubs integrating several energy providers:
-\begin{itemize}
-\sf\footnotesize
-\item energyProvider.requestAvailability() $\rightarrow$ $\langle$KWatt/h, Ecost, rate, location$\rangle$
+According to our example scenario, we conducted an experimental experience for implementing our data integration approach on a multi-cloud environment.
+We focussed on the implementation of a data as a service layer that integrates content from different services related to education but also related on data producers and consumers.
+Figure \ref{fig:storage} shows the general architecture of our scenario, deployed on Window Azure data store services and on Jelastic (https://jelastic.com), an open free cloud provider where we installed NE4J and Mongo NoSQL stores.
+The multi-cloud data as a service layer is a data provision platform storing clean data sets stemming from public data services (Linked in, Tweeter, Facebook) accessible on Internet and also from private ones.
 
-\item energyHub.requestAvailability() $\rightarrow$  \{$\langle$ID, KWatt/h, cost, rate, location$\rangle$\}
-
-\end{itemize}
-
-Each service is deployed in different cloud provider and each exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the disponibility of the service, the average response time when a method is called, the reliability, the privace of the produced data (whether they can be stored or not), the precision,freshness and provenance of the produced data.
-As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider.
-In contrast, the other measures are constantly computed by monitoring the conversations between the service and the applications that contact it.
-Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transfering data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
-For exmaple some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
-zone 1 is Europe).
-If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.
-
-\begin{itemize}
-\sf\footnotesize
- \item {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}.
-
- \item  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
- \end{itemize}
-
- Given a query, expressed as an SQL like expression including spatio-temporal attributes and preferences, for example, {\em List of energy providers that can provision 1000 Kwatts/h, in the next 10 seconds, that are close to my city with a cost of 0,50 euros/Kwatt and that are labeled as green?}.
-The user preferences statement, includes her cloud provider contract and her quality preferences.
- \begin{itemize}
-\sf\footnotesize
-
- \item  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}.
-
- \item {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}.
-
- \end{itemize}
- We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure with {\sf 0,05 cents per call,  8 Gigabytes of I/O volume/month, free data transfert cost within the same region,  Gigabyte of storage}.
-The user is ready to pay maximum {\sf 5 euros as total query cost}, she wants only {\sf green} energy providers (provenance), at least {\sf 85$\%$} of precision of provided data, even if they are not fresh, she wants at least {\sf 90$\%$} available services, with a response time of {\sf 0,01 seconds}.
-
- Assume that there are four civilian energy providers are represented by services  {\sf e$_1$, ...
-e$_4$} and two {\sf hub}s which are also services integrating energy providers communities {\sf h$_1$ and h$_2$}; there are two free location services exporting  the following interface {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$} meaning that given an IP address it returns the geographic position expresses as {\sf X} and {\sf Y}.
-This services can potentially be combined for answering the query.
-
- %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
- \paragraph{Derived SLA} 
- %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
- Some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query.
-These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
- \begin{itemize}
-\sf\footnotesize
- \item  query total cost: $\Sigma_{i = 1 ... n}$ s$_i$ + data transfer cost $\leq$ 5 euros
- \item  total responseTime: $\Sigma_{j = 1 ... i}$ response time of services composed for ex(s$_j$) + data transfer cost $\leq$ 5 euros
- \item availability: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}, 
- \item freshness: non 
- \item precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
- \item provenance:  all services involved must be $green$
- \item storage: {\em partial results size} $\leq 1 Giga$ 
- \end{itemize}
-
-  %.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . 
-  \paragraph{Computing service compositions} 
-%.  .  .  .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  . .  .  .   
-  Some of the inequations of the derived SLA are included in the service compositions that can potentially answer the query given a set of services that can possibly be composedL In the case of our query example the following composition can be used for answering it.
-  \begin{description}
-\sf\footnotesize
-\item Q$_1$ $\rightarrow$  \\$\langle$X$_1$,Y$_1$ $\rangle$ = loc$_1$(IP) $\parallel$  \\$\langle$ X$_2$,Y$_2$ $\rangle$ = loc$_1$(Eprovider), \\D= eucledianDistance(X$_1$,Y$_1$,X$_2$,Y$_2$), \\(
-$\langle$ C$_1$, E$_1$ $\rangle$ = e$_1$() $\parallel$ ...$\parallel$ $\langle$ C$_n$, E$_n$ $\rangle$ = e$_4$()), \\D $\leq$ 1.5 Km,\\ sum(C$_1$:C$_n$) $\leq$ 5, \\ sum(E$_1$:E$_n$) $\leq$ 1000 Kwatts/h, \\ totalResponseTime  $\leq$ 10 seg
-  \end{description}
-
-  In fact our apporaches would generate k service compoisions combining as much as possible the services available such that the constraints of the derived SLA are verified.
-
-   \paragraph{Optimizing service compositions execution}
-% \begin{figure*}
-%\includegraphics[width=0.95\textwidth]{figs/exchange.pdf}
-%\caption{\label{fig:energyXChange} Energy exchange.}
-%\end{figure*}
+The DaaS platform interacts recurrently with services in order to retrieve data and build collections that can be accessed by consumers.
+Each data service is characterized by the quality of data it provides, its availability and also by privacy and data ownership contrats provided as SLA contracts and enforced by security protocols.

### 2015-02-22 Workshop2015/useCase.tex
more on use case and a bit on main

@@
 Each data service is characterized by the quality of data it provides, its availability and also by privacy and data ownership contrats provided as SLA contracts and enforced by security protocols.
+In the case of our MOOC scenario data concern public professional information about the users of our MOOC exported by Linked in.
+Such information and particularly their expertise supported by other contacts are used in order to determine the quality of the content they provide.
+Content and professional information are stored in data store deployed in Jelastic.
+Our NoSQL support is configured for ensuring data availability and good data processing performance, given that our content is heterogeneous and it can be "critical" in our MOOC.
+Indeed, consumers can specify time delivery constraints that must be respected by our DaaS layer.
+Data concerning private data about users of our MOOC are stored in SQL Server on Azure.
+They are maintained according the  SLA contract provided for the less costly subscription to Azure, that corresponds to an education grant licence.
+We decided to manage information about courses programs in SQL Server since it seems that the relational model is well adapted for these type of data.
+Given out subscription, and the storage space to which we have access we decided to store the less voluminous data collections on this cloud.

### 2015-02-22 Workshop2015/useCase.tex
Use case

@@
 We decided to manage information about courses programs in SQL Server since it seems that the relational model is well adapted for these type of data.
-Given out subscription, and the storage space to which we have access we decided to store the less voluminous data collections on this cloud.
+Given the conditions of our subscription, and that the storage space to which we have access to Azure we decided to store the less voluminous data collections on this cloud.
+Data collections are services that have associated CRUD front-ends implemented using the Spring Roo library.
+Thus, data collections can be accessed by applications through their API our through an application.
+
+We proposed a global service that gives access to these databases in an integrated way, and can receive queries using a pivot language, UNQL in our case.
+The global service implements a negotiation process for dealing with SLA and  the  query rewriting process.

### 2015-03-06 Workshop2015/introduction.tex
simple changes to the example - still working on it

@@
 
-Therefore this paper presents an approach proposing strategies for computing integrated SLA's according to agreed SLA's exported by services  and adaptable query rewriting for integrating data sets  according to user preference statements.
+In this context, this paper presents an approach proposing strategies for computing integrated SLA's according to agreed SLA's exported by services  and adaptable query rewriting for integrating data sets  according to user preference statements.
 This implies to consider several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).

### 2015-03-06 Workshop2015/incremental.tex
simple changes to the example - still working on it

@@
 Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering adata and launching and re-launching queries.
+Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering data and launching and re-launching queries.
 Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
@@
 Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
-cost, inscription, or exchange unit), and the time window in which they can produce it.
+cost, inscription, or exchange unit), and the time window in which they can produce contents.
 Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
-An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
+%An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
 
@@
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(Type, Cost, Size, location), \textit{SLA}$_i$
+\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(Id, ContentType, Cost, Size, Location), \textit{SLA}$_i$
 \end{trivlist}
 
-Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data centre or between data centres ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
 For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
@@
 
-According to our approach, content producers are modelled as data services with associated ``agreed'' SLAs.
+According to our approach, content producers are modeled as data services with associated ``agreed'' SLAs.
 In the example, we assume that several producers will be able to supply equivalent content for a given period of time given specific  preferences expressed by a consumer.
@@
 Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$ and h$_2$}.
+We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}.
 We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
@@
 
-A content request is expressed as a query that specifies an energy requirement with QoS preferences independently of the possible producers.
+A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible producers.
 
@@
 We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
-The user is ready to pay maximum {\sf \$5 as total query cost}; she requests that only {\sf green} energy providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} and with a response time of {\sf 0,01 seconds}.
+The user is ready to pay maximum {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} in the next three hours and with a maximmum response time of {\sf 30} seconds for tutored contents and {\sf 0,5} seconds for online contents.
 

### 2015-03-10 Workshop2015/incremental.tex
Cleaning "energy" from the example
little changes

@@
 We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
-The user is ready to pay maximum {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} in the next three hours and with a maximmum response time of {\sf 30} seconds for tutored contents and {\sf 0,5} seconds for online contents.
+The user is ready to pay maximum {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} in the next three hours and with a maximum response time of {\sf 30} seconds for tutored contents and {\sf 0,5} seconds for online contents.
 
@@
 For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The derived SLA  can be seen as a set of unequations that have to be solved during the execution of a service composition.
+The derived SLA  can be seen as a set of inequations that have to be solved during the execution of a service composition.
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
@@
 \begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the energy trade system of Example~\ref{Ex:rew1}.
- Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson peotry.
+Let us return to the content  trade system of the MOOC Example~\ref{Ex:rew1}.
+ Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
 In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
@@
 
-Second, precalculated queries and partial results can be also stored in cache or in a persistent support.
+Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
 Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.

### 2015-03-12 Workshop2015/incremental.tex
finished section IV... Working on sect V --Martin

@@
 
+%NOTE: Agreed SLA are client-provider slas... --MARTIN
+
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}. 
+\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, location, duration$\rangle$. 
  \end{trivlist}
@@
 
-In our example assume that there are several content provision services ({\sf e$_1$, ... e$_n$}) that can be independent or hubs integrating several content providers. 
-Each of them is specified by a clause:
+According to our approach, content producers are modeled as data services with associated \textit{agreed SLAs}. 
+In the example, we assume that several producers will be able to supply equivalent content for a given period of time given specific  preferences expressed by a consumer. 
+Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
+Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
+We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}.
+We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
+All these services can potentially be combined for answering queries.
+
+In our example, we assume that the content provision services ({\sf e$_1$, ... e$_4$}) have their interfaces defined as follows:
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ]   e$_i$ $\equiv$ provider(Id, ContentType, Cost, Size, Location), \textit{SLA}$_i$
+\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size), SLA$_\mathit{user}$.
+
+                engage$_i$(contents, req\_size, payment, course), agreedSLA$_i$.
 \end{trivlist}
 
-Cloud providers define also their SLA contracts defining normally subscription contracts that specify, the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+The first operation permits the user to ask for the budget of a given course (content).
+{\sf SLA}$_\mathit{user}$ is the user's proposal to the contents provider. 
+This SLA will become the {\sf agreedSLA}$_i$, in case of availability of the contents. 
+We suppose that availability is characterized by a non-zero value of size of the provided data ({\sf prov\_size}).
+The second operation is used to engage in a course. 
+The agreed SLAs are those containing the information described above in this example.
+The user will ask for a given SLA to which the provider may agree.
+
+We suppose that hubs will have the same interface as individual service providers.
+
+Cloud providers also define their SLA contracts that specify the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
 For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
@@
 \begin{trivlist}\sf\footnotesize
-%\item[~$\bullet$ ] {\sf agreedSLA:$\langle$cost/call, maxCalls/day, availability, responseTime, reliability, privacy, precision, freshness, provenance$\rangle$}. 
-% 
- \item[~$\bullet$ ]  {\sf cloudSLA:$\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$}. 
+ \item[~-~cloudSLA:]  $\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$.
  \end{trivlist}
 
-According to our approach, content producers are modeled as data services with associated ``agreed'' SLAs.
-In the example, we assume that several producers will be able to supply equivalent content for a given period of time given specific  preferences expressed by a consumer.
-Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
-Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}.
-We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\leftarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries.
-
-A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible producers.
+%A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
 
 Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, \textit{List of English poetry content providers that can provision commented Emily Dickinson poems, in the next hour, that are close to my city that are free and that are labeled as experts?}.
+For instance, let us have the query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar}''.
+This query has two parts: the one that corresponds to the content that will be solved by combining data services and the user preferences.
+For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance).
+
 The user preferences statement would include their cloud provider contract and quality preferences:
+\begin{trivlist}\sf\footnotesize
+\item[~-~cloudSLA:]  $\langle$0,05 cents per call, 8 GB I/0 volume/month, free, 1 GB storage$\rangle$. 
+\end{trivlist}
+
+We consider a simplified cloud SLA contract inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
+
+The user is ready to pay a maximum of {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); even if their data are not fresh; she requires a contract duration of one week.
 
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ]  {\sf cloudSLA:$\langle$0,05 cents per call, 8 Gigabytes I/0 volume/month, free, 1 Giga$\rangle$}. 
-\item[~$\bullet$ ] {\sf preferencesStatement:$\langle$query total cost,  total responseTime, reliability, freshness, precision, provenance, storage$\rangle$}. 
+\item[~-~SLA$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days$\rangle$. 
 \end{trivlist}
-
-We consider a simplified SLA cloud contract inspired in the lowest contract provided by Azure: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
-The user is ready to pay maximum {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); at least {\sf 85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least {\sf 90$\%$} in the next three hours and with a maximum response time of {\sf 30} seconds for tutored contents and {\sf 0,5} seconds for online contents.
 
@@
 Indeed, our rewriting process will proceed in stages.
-User preferences and user SLAs will be used to produce derived SLA to be added to the query. 
+User preferences (including cloud SLAs) and agreed SLAs will be used to produce derived SLAs to be added to the query. 
 These SLAs will influence the choice of data/service providers.
@@
 A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-The service SLA measures  that we consider are: response time, availability, price/call, reliability, data production rate.
+The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location and duration of the engagement.
 Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
 
-An example of computed measure is the cost of retrieving the list of "expert" Emily Dickinson poems providers within a region with their cost.
+An example of computed measure is the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
 The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaOctets through the network and the type of subscription of the user for using the network.
+This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network and the type of subscription of the user for using the network.
 
-Given agreed SLA's and a user preferences statement the challenge is to compute a  {\em derived SLA} that  maps SLA measures and preferences attributes.
+Given agreed SLAs and a user preferences statement the challenge is to compute a  {\em derived SLA} that  maps SLA measures and preferences attributes.  
 The derived SLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
-The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.
+The derived SLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
 
@@
 \begin{trivlist}\sf\footnotesize
-\item[~$\bullet$ ] query total cost: $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5
- \item[~$\bullet$ ] total response time: of services + data transfer
- \item[~$\bullet$ ] availability: {\em (of services involved)} $\leq$ {\sf 90$\%$}, 
- \item[~$\bullet$ ] freshness: non 
- \item[~$\bullet$ ] precision: {\em avg (precision of services involved)} $\leq$ {\sf 85$\%$}
- \item[~$\bullet$ ] provenance:  all services involved must be $expert$
- \item[~$\bullet$ ] storage: {\em partial results size} $\leq 1$ GB
+ \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5.
+ \item[~-~availability:] {\em (of services involved)} $\leq$ {\sf 90$\%$}.
+ \item[~-~freshness:] non.
+ \item[~-~provenance:] all services involved must be $expert$.
+ \item[~-~duration:] 7 days.
+ \item[~-~I/0 volume/month:] 8GB.
+ \item[~-~storageSpace:] 1GB.
  \end{trivlist}
 
-Therefore, we propose a classification of SLA measures that represents the relationship between fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements.
+Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. 
 It specifies also how to compute coarse grained measures with fine grained ones. 

### 2015-03-12 Workshop2015/incremental.tex
query rewriting...

@@
 \begin{trivlist}\sf\footnotesize
-\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size), SLA$_\mathit{user}$.
+\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), SLA$_\mathit{user}$.
 
-                engage$_i$(contents, req\_size, payment, course), agreedSLA$_i$.
+                engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
 \end{trivlist}
 
-The first operation permits the user to ask for the budget of a given course (content).
+The first operation permits the user to ask for the budget of a given course (content) and a required minimmum size.
+This operation will return the cost of the data, as well as its actual size and location.
 {\sf SLA}$_\mathit{user}$ is the user's proposal to the contents provider. 
@@
 \begin{trivlist}\sf\footnotesize
- \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$5.
- \item[~-~availability:] {\em (of services involved)} $\leq$ {\sf 90$\%$}.
+ \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$1.
+ \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
  \item[~-~freshness:] non.
@@
 In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
-In the LAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available databases.
+In the LAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available sources.
 The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
@@
 
-We propose an approach consists in generating several translations of an abstract service specification into compositions
-over concrete  services. 
+We propose an approach that consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
 The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.
-The next example shows the main features of the approach proposed in~\cite{CostaAMR13} and that is extended in the case of SLA guided services based data integration.
+The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
 
-\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the case of the MOOC scenario, where people can participate on an content trading pool.
-We suppose that this hypothetical MOOC has a large number of participants that sell their content  to other consumers. 
+%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
+Let us consider the MOOC scenario, where people can participate on an content trading pool.
+We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
 The MOOC has four information hubs, located in four different geographic locations, connected to other content providers.
-Other content providers are  contacted directly, through the services of three different cloud providers.
+Content providers may be  contacted directly, through the services of three different cloud providers.
 Each cloud provider exports its own interfaces.
@@
 The specification of each available service is also considered (this specification should be given by the service provider).
-~\hfill\openbox
-\end{example}
+%~\hfill\openbox
+%\end{example}
 
-Given a a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-Some of the un-equations of the derived SLA should be included in the service compositions that answer the query.
+Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
+Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
 In the case of our query example the following composition can be used for answering it:
-\begin{eqnarray*}
-Q_1 &\equiv&
-   \langle X_1,Y_1\rangle = loc_1(IP), \\
-&& \langle X_2,Y_2 \rangle = loc_1(Cprovider), \\
-&& D = distance(\langle X_1,Y_1\rangle, \langle X_2,Y_2\rangle), \\
-&& \langle C_1, E_1 \rangle = e_1(\dots), \dots \langle C_4, E_4 \rangle = e_4(\dots), \\
-&& D \leq 1.5 \mathsf{Km},\ \ sum(C_1:C_4) \leq 5, \\
-&& union(E_1:E_4) \geq 5\ \mathsf{Go}, \\
-&& \mathsf{totalResponseTime}  \leq 10\ \mathsf{seg}
-\end{eqnarray*}
 
-  In fact our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
+\begin{footnotesize}
+\sf
+\begin{tabbing}
+ -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
+ \>  myLoc = loc(myIPaddress), \\
+ \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
+ \>  query total cost + cost $\leq$ \$1,\\
+ \>  availability $\geq$ 90$\%$, \\
+ \>  freshness = any, \\
+ \>  provenance = ``expert'', \\
+ \>  duration = 7 days, \\
+ \>  I/0 volume/month $\leq$ 8GB, \\
+ \>  storageSpace $\leq$ 1GB, \\
+ \>  engage(``E.Dickinson'', size, myCreditCard).
+ \end{tabbing} 
+\end{footnotesize}
+
+Our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
  Yet, the algorithm should be modified to take into account the different SLAs. The next example illustrates one of the limits of the automatic composition algorithm.
@@
 \begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the content  trade system of the MOOC Example~\ref{Ex:rew1}.
+Let us return to the content  trade system of the MOOC Example.
  Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
@@
 In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results.
-These computations are used dynamically for instantiating free variables in the derived SLA and thus determine wether te contract is respected by the execution of a query.
+These computations are used dynamically for instantiating free variables in the derived SLA and thus determine whether the contract is respected by the execution of a query.
 Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.

### 2015-03-30 Workshop2015/incremental.tex
Nadia's version of the paper

@@
-We propose an SLA guided, continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
+We propose an SLA guided, security-aware continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
 Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-Given a requirement expressing a query and quality of service preferences: cost, provenance, reputation, execution time, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results, delivering data and launching and re-launching queries.
+Given a requirement expressing a query and quality of service preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results (including in  which location data is stored), delivering data (applying security controls during integration) and launching and re-launching queries.
 Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
@@
 
-In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
-Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
+%In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
+%Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
 cost, inscription, or exchange unit), and the time window in which they can produce contents.
-Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
+%Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
 %An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
@@
 \begin{trivlist}\sf\footnotesize
-\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, location, duration$\rangle$. 
+\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, data access control, certified reputatiion level, location, duration$\rangle$. 
  \end{trivlist}
@@
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
+It is the case for service reputation that will condition the way personal user data will be anonymized (Constraint1).
+Some among them will be instantiated depending of the context of service invoking in the multi-cloud.
+It is the case for constraint 2 expressed above:   user access credential should be calculated according to the clouds hosting the other data services.
 
 According to our approach, content producers are modeled as data services with associated \textit{agreed SLAs}. 
-In the example, we assume that several producers will be able to supply equivalent content for a given period of time given specific  preferences expressed by a consumer. 
+In our example of MOOC system presented above, we assume that several producers will be able to supply equivalent content for a given period of time  given specific  preferences expressed by a consumer.
 Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
@@
 This query has two parts: the one that corresponds to the content that will be solved by combining data services and the user preferences.
-For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance).
+For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) and that her privacy be saved by adapting the anonymity process with regard to services reputation.
+The maximum total cost will condition also which kind of privacy preserving algorithms to apply.
 
@@
 \begin{trivlist}\sf\footnotesize
-\item[~-~SLA$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days$\rangle$. 
+\item[~-~SLA$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
 \end{trivlist}
@@
 User preferences (including cloud SLAs) and agreed SLAs will be used to produce derived SLAs to be added to the query. 
-These SLAs will influence the choice of data/service providers.
+These derived SLAs will influence the choice of data/service providers.
 The SLA proposed by the chosen providers need to be combined with the conditions on each proposed rewriting of the query.
@@
 A query has associated preferences  expressed as macroscopic constraints (i.e.
-user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy, partial/full results, delivery mode.
+user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode.
 These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
@@
 A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location and duration of the engagement.
+The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location, duration of the engagement, privacy-preserving status.
 Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
 
-An example of computed measure is the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
+Examples of computed measure are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
 The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network and the type of subscription of the user for using the network.
+This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
+The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
 
@@
 
-In the example, some of the user preferences statement measures are used for defining a dervied SLA that, as said in previous section, will guide the evaluation of the query. 
+In the example, some of the user preferences statement measures are used for defining a derived SLA that, as said in previous section, will guide the evaluation of the query. 
 These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
 \begin{trivlist}\sf\footnotesize
- \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer $\leq$ \$1.
+ \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1.
  \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
@@
  \item[~-~I/0 volume/month:] 8GB.
+ \item[~-~reputation level :] $\geq$ threshold.
  \item[~-~storageSpace:] 1GB.
@@
 This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
-Negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the cloud.
+Negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
 This negotiation can be expensive and may not scale well.
@@
 
+\color{red}
+One point remain very crucial to fix: once the multi-cloud layer generate a list of derived SLA corresponding to Agreed-SLA of services that could match a part of the query, What should happen?
+Whith whom rewritten query using user preferences is matched with SLA and which one (not clear in the paper.
+This point should be discussed quickly.
+The workflow of SLA between the abstract layer and cloud is not so clearly described.
+
+\color{black}
 Query rewriting is a well-known problem in the database domain.
@@
 Each cloud provider exports its own interfaces.
-SLAs are defined for each individual content provider server, each hub, and each cloud provider.
+SLAs are defined for each individual content provider server and  each hub(agreed SLA)  , and also for each cloud provider (traditional SLA contracts).
 
@@
 Also  cloud providers  publish the conditions for using their services.
-These conditions are expressed as user preferences and SLAs.
-Additionally, other non-functional requirements (such as authentication or security requirements) may apply.
+These conditions and non-functional requirements (such as authentication or security requirements) should also been expressed in the user preferences and SLAs.
 
@@
  \>  I/0 volume/month $\leq$ 8GB, \\
+ \>reputation level :] $\geq \lambda$ (the threshold) \\
  \>  storageSpace $\leq$ 1GB, \\
@@
 
+\color{red}
 \begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the content  trade system of the MOOC Example.
+Let us return to the content  trade system of the MOOC example.
  Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
 In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
-Let us suppose that, in order to minimize the the communications between servers, the lists need to be produced incrementally.
+Let us suppose that, in order to minimize the  communications between servers, the lists need to be produced incrementally.
 In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
@@
 
+\color{black}
+
 %-----------------------------------------------------------------
@@
 %-----------------------------------------------------------------
- Our data provision and integration approach relies on data services deployed on one or different providers and it is delivered as a DaaS.
+ Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
 This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
@@
 Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.
+
+ Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
+In the example this has been illustrated by  the access control level constraints demanded by data services when they are implied in an integration process.
+Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration it self.

### 2015-03-30 Workshop2015/introduction.tex
Nadia's version of the paper

--- 2015-02-22 Workshop2015/introduction.tex
@@
-This paper presents an approach for addressing  data collections integration  in a multi-cloud hybrid context guided by user preferences statements and SLA contracts exported by different cloud providers.
-The objective is to propose an SLA guided  data provision and integration system exported as a DaaS by a cloud provider that can be adapted according to user preferences on the way data can be delivered  such as accepting partial results delivered on demand or under predefined subscription models that can affect the quality of the results; accepting specific data duplication that can respect privacy but ensure data availability; accepting to launch a task that contributes to an integration on a first cloud whose SLA verifies a QoS requirement rather that a more powerful one.
+%\color{red}
+%
 
+\color{black}
+The advent of cloud computing imposed a new model for resource consuming that is not concerned
+ with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources.
 Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their "structural" characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
@@
 This can be done according to quality of service requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
-
-Therefore this paper presents an approach proposing strategies for computing integrated SLA's according to agreed SLA's exported by services  and adaptable query rewriting for integrating data sets  according to user preference statements.
+In fact,  SLA demonstrated interests in data analysis but has not been yet enough considered on data integration.
+Therefore, we believe in the benefits of SLA-based data integration in meeting better user requirement.
+\color{red}
 This implies to consider several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 
+\color{black}
+%To better understand our problem, let us consider an example from the domain of energy
+%management.
+We assume we are interested in queries like: \textit{Give a list of energy providers that can provision 1000 KW-h, in the next 10 seconds, that are close to my city, with a cost of 0,50 Euro/KW-h and that are labelled as green?} \\
+% The user demanded to apply a special encryption algorithm to sensitive data if data has to be transferred between providers or between physical sites during the integration process (Constraint1).
+Furthermore, the data providers could wish also that in case of a common use of their data within  an integration process, that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data (Constraint 2).
+We consider a simplified SLA cloud contract inspired in the cheapest contract provided by Azure: \textit{cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  1~GB of storage.}
+%The user is ready to pay a maximum of \textit{\$5 as total query cost}; she requests that only  \textit{green} energy providers should be  listed (provenance), with at least  \textit{85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least 90$\%$ and a response time of  \textit{0,01 s}.
+She demands to contact only data providers with a threshold of trust .
+
+To better understand our problem, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
+Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
+cost, inscription, or exchange unit), and the time window in which they can produce contents.
+Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
+The user demanded to minimize personal data transferred to providers and according to the level of trust she has in data providers, to use privacy preserving technics to let her anonymous among users choosing these ressources (Constraint1).
+Furthermore, the data providers could wish also that in case of a common use of their data within  an integration process, that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data (Constraint 2).
+
+  This scenario faces a set of issues.
+First, how can the user efficiently obtain  results for her queries such that they meet her QoS requirements while respecting her subscribed contracts with the involved cloud provider(s)?
+The user knows the low-level clauses of her SLA contract but do not has any idea on the ressource level required to satisfy her requirements (example of Constraint 1).
+Second, data services contracts should not been neglected in an integration process (Constraint 2).
+As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made and in which conditions.
+In fact, integration could be sometimes realized enforcing all specified conditions; we can also expect situations where they can be verified partially.
+How then in all cases such heavy process should be made profitable for further integration trial?
+
+ In this paper, we present  a preliminary solution addressing the issues described below.
+Our solution is SLA-guided : We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
+Thank to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level SLA-user contracts.
+The derived SLA allow to choose individual services w.r.t user demands.
+Once data services to integrate are choosed, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
+%  Particularly, for queries that call several services deployed  on different clouds. 
+%  Among them first,Furthermore, for a non specialist user, she do not realize what is the level of ressources she need to apply the encryption level asked  for. 
+%  As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made. 
+%  concerns the context in which data will be used among clouds when data services are deployed in a multi-cloud configuration.
+How can the specified services requirements be enforced?
+And finally, data integration in this context faces an heterogeneity problem at different levels but specially in the scenario we are interested in, in data deployment conditions, the SLA expression language, the level security is taken into account in SLA contract.
+
+ \color{red}
 Accordingly, the remainder of this paper is organized as follows.
@@
 Finally \ref{sec:conclusions} concludes the papers and discusses future work.
+
+\color{black}

### 2015-03-31 Workshop2015/introduction.tex
Introduction

@@
 The advent of cloud computing imposed a new model for resource consuming that is not concerned
- with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources.
+ with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially unlimited resources.
 Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their "structural" characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
 Existing data integration techniques have to be revisited considering weakly curated and modeled data sets.
-This can be done according to quality of service requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
-In fact,  SLA demonstrated interests in data analysis but has not been yet enough considered on data integration.
-Therefore, we believe in the benefits of SLA-based data integration in meeting better user requirement.
+This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
+In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data.
+Therefore, we believe in the benefits of SLA-based data integration as an approach for better meeting  user requirements.
 \color{red}
-This implies to consider several granularities of SLA: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
+In order to do so, several granularities of SLA must be considered: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 
@@
 
-To better understand our problem, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
+To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and expertise of participants. 
 Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
 cost, inscription, or exchange unit), and the time window in which they can produce contents.
-Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
-The user demanded to minimize personal data transferred to providers and according to the level of trust she has in data providers, to use privacy preserving technics to let her anonymous among users choosing these ressources (Constraint1).
-Furthermore, the data providers could wish also that in case of a common use of their data within  an integration process, that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data (Constraint 2).
+Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content.
+The MOOC  aims at being privacy respectful of the students participating in courses.
+ Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.
+According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1).
+Furthermore,  data providers could  also wish to give restricted data access credentials w.r.t.
+to their own, when their data are used  within  an integration process (Constraint 2).
 
-  This scenario faces a set of issues.
+ %that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data
+
+  From this scenario we identify a set of issues that have to be addressed.
 First, how can the user efficiently obtain  results for her queries such that they meet her QoS requirements while respecting her subscribed contracts with the involved cloud provider(s)?
-The user knows the low-level clauses of her SLA contract but do not has any idea on the ressource level required to satisfy her requirements (example of Constraint 1).
-Second, data services contracts should not been neglected in an integration process (Constraint 2).
+The user knows the low-level clauses of her SLA contract but she does not have an idea about the resources required to satisfy her requirements (SLA exported by services, example of Constraint 1).
+Second, data services contracts should not be neglected in an integration process (Constraint 2).
 As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made and in which conditions.
 In fact, integration could be sometimes realized enforcing all specified conditions; we can also expect situations where they can be verified partially.
-How then in all cases such heavy process should be made profitable for further integration trial?
+In any case, how should the results of  such a  complex process  be capitalized for further integration requests?
 
  In this paper, we present  a preliminary solution addressing the issues described below.
-Our solution is SLA-guided : We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
-Thank to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level SLA-user contracts.
-The derived SLA allow to choose individual services w.r.t user demands.
-Once data services to integrate are choosed, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
+Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
+Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services.
+The derived SLA allows to choose  services (w.r.t user demands) that can contributed for answering a query.
+Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
 %  Particularly, for queries that call several services deployed  on different clouds. 
@@
 Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes.
-Section \ref{sec:incremental} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by concilating SLA's provided by services and user's profiles expressing QoS preferences about the data they want to consume and the conditions in which they must be processed and delivered.
+Section \ref{sec:incremental} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by conciliating SLA's provided by services and user's profiles expressing QoS preferences.
+Profiles specify preferences about the data they want to consume and the conditions in which they must be processed and delivered.
 Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 

### 2015-03-31 Workshop2015/incremental.tex
" The first cut is the deepest"

@@
-We propose an SLA guided, security-aware continuous data provision and integration approach that consists in three steps  starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch} shows the general architecture of an SLA guided data integration system. It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-Given a requirement expressing a query and quality of service preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots, the system processes it  as follows: (i) derived SLA  computation for filtering possible data providers; (ii) query rewriting for computing services compositions that can be used for building results; (iii) managing the integration process including storing partial results (including in  which location data is stored), delivering data (applying security controls during integration) and launching and re-launching queries.
-Intermediate results that are stored as knowledge in order to reduce the overhead of the query evaluation process.
+We propose an SLA guided, security-aware continuous data provision and integration approach performed within a cloud service oriented environment  (see
+%starting from the processing of the query  to the delivery of the results.
+Figure~\ref{fig:arch} )
+%shows the general architecture of an SLA guided data integration system. 
+%It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
 %The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
@@
 \begin{trivlist}\sf\footnotesize
-\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, data access control, certified reputatiion level, location, duration$\rangle$. 
+\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, data access control, certified reputation level, location, duration$\rangle$. 
  \end{trivlist}
 
-As said in previous sections, some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
+We suppose that some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
 It is the case for service reputation that will condition the way personal user data will be anonymized (Constraint1).
-Some among them will be instantiated depending of the context of service invoking in the multi-cloud.
-It is the case for constraint 2 expressed above:   user access credential should be calculated according to the clouds hosting the other data services.
+Some measures will be instantiated depending of the context of  the service invoked within a multi-cloud environment.
+It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the clouds hosting different data services.
 
 According to our approach, content producers are modeled as data services with associated \textit{agreed SLAs}. 
-In our example of MOOC system presented above, we assume that several producers will be able to supply equivalent content for a given period of time  given specific  preferences expressed by a consumer.
+In our example of MOOC system presented above, we assume that several producers will supply equivalent content for a given period of time  that will be chosen with respect to the  preferences expressed by a consumer.
 Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
 Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}.
+We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}. We suppose that hubs will have the same interface as individual service providers.
 We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
@@
 The agreed SLAs are those containing the information described above in this example.
-The user will ask for a given SLA to which the provider may agree.
-
-We suppose that hubs will have the same interface as individual service providers.
+%The user will ask for a given derived SLA to which the provider may agree.
 
@@
 In this context, the compliance to the SLAs will drive the query rewriting process.
-Indeed, our rewriting process will proceed in stages.
-User preferences (including cloud SLAs) and agreed SLAs will be used to produce derived SLAs to be added to the query. 
-These derived SLAs will influence the choice of data/service providers.
-The SLA proposed by the chosen providers need to be combined with the conditions on each proposed rewriting of the query.
-These combination will influence the decision about the actual services to be used.
+
+Given a requirement expressing a query and quality of service preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots, the data integration process for computing a result is done as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and agreed SLAs will be used to produce a derived SLA to be associated to the query.
+These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
+The agreed SLA proposed by the chosen services is added as  conditions in  each re-written   query expression; (iii) Managing the integration process particularly storing partial results (including in  which location data is stored), delivering data (applying security control during integration) and launching and re-launching queries.
+Intermediate results  are stored as knowledge in order to reduce the overhead of the query evaluation process.
 
@@
 
-We assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
+As said before, we assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
 A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
@@
 
-Examples of computed measure are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
+Examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
 The cost is determined by the  cost of the calls. 
@@
 One point remain very crucial to fix: once the multi-cloud layer generate a list of derived SLA corresponding to Agreed-SLA of services that could match a part of the query, What should happen?
-Whith whom rewritten query using user preferences is matched with SLA and which one (not clear in the paper.
+With whom rewritten query using user preferences is matched with SLA and which one (not clear in the paper.
 This point should be discussed quickly.
@@
 The problem consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
-Query rewriting is guided by the schema of  abstract and concrete databases.
-The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
-
+%Query rewriting is guided by the schema of  abstract and concrete databases.
+%The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
 The query rewriting problem can be generalized to the case of services.
@@
 Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
-In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
-In the LAV approach, the rewriting process is guided by the specification of both the query to be rewritten and the available sources.
-The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
-These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
+%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
+%In the LAV approach, 
+The rewriting process is guided by the specification of both the query to be rewritten and the available services.
+%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
+%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
 
 We propose an approach that consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.
+%The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.  
 The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
@@
 %-----------------------------------------------------------------
-\section{Dealing with the resources consumed by the evaluation process}
-\label{sec:queryProcessOpt}
+%\section{Dealing with the resources consumed by the evaluation process}
+%\label{sec:queryProcessOpt}
 %-----------------------------------------------------------------
- Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
+ %Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
 This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
@@
 
- We believe that the optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
+ %We believe that the optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
 Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service).
@@
 
-Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
+%Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
 Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
@@
 
-As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
+%As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
 In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results.
@@
 
- Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
+ %Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
 In the example this has been illustrated by  the access control level constraints demanded by data services when they are implied in an integration process.

### 2015-04-02 Workshop2015/current version/incremental.tex
no message

--- 2015-03-31 Workshop2015/incremental.tex
@@
-We propose an SLA guided, security-aware continuous data provision and integration approach performed within a cloud service oriented environment  (see
+To answer the needs expressed above, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
 %starting from the processing of the query  to the delivery of the results.
@@
 \center{
-\includegraphics[width=0.75\textwidth]{arch.png}
-\caption{General architecture of an SLA guided  data integration system.\label{fig:arch}}}
+\includegraphics[width=0.75\textwidth]{workflow.pdf}
+\caption{Phases of an SLA guided  data integration workflow.\label{fig:arch}}}
 \end{figure*}
@@
 
-We suppose that some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
+Some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
 It is the case for service reputation that will condition the way personal user data will be anonymized (Constraint1).
-Some measures will be instantiated depending of the context of  the service invoked within a multi-cloud environment.
+Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment.
 It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the clouds hosting different data services.
@@
 
-In our example, we assume that the content provision services ({\sf e$_1$, ... e$_4$}) have their interfaces defined as follows:
+In our example, non-functional characteristics of the content provision services ({\sf e$_1$, ... e$_4$}) are calculated by services that enforce SLAs  as follows:
 \begin{trivlist}\sf\footnotesize
-\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), SLA$_\mathit{user}$.
+\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$.
 
@@
 
+\color{red}
+
 The first operation permits the user to ask for the budget of a given course (content) and a required minimmum size.
 This operation will return the cost of the data, as well as its actual size and location.
-{\sf SLA}$_\mathit{user}$ is the user's proposal to the contents provider. 
+{QoS preferences}$_\mathit{user}$ is the user's proposal to the contents provider. 
 This SLA will become the {\sf agreedSLA}$_i$, in case of availability of the contents. 
@@
 
+\color{black}
 %-----------------------------------------------------------------
-\section{Deriving a query SLA}
+\section{Derived SLA}
 \label{sec:slaModel}

### 2015-04-02 Workshop2015/current version/introduction.tex
Introduction: changes to the red part

--- 2015-03-31 Workshop2015/introduction.tex
@@
 \color{red}
-In order to do so, several granularities of SLA must be considered: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
+In order to do so, several granularities of SLA must be considered: (i) at the cloud level: the SLA ensured by providers regarding data; (ii) at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally (iii) at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 
@@
 
- In this paper, we present  a preliminary solution addressing the issues described below.
+ In this paper, we present  a preliminary solution addressing the issues described above.
 Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
@@
 Profiles specify preferences about the data they want to consume and the conditions in which they must be processed and delivered.
-Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 
+%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach. 
 Finally \ref{sec:conclusions} concludes the papers and discusses future work.

### 2015-04-02 Workshop2015/current version/incremental-ge.tex
Some modifications to avoid inconsistencies

--- 2015-04-02 Workshop2015/current version/incremental.tex
@@
 
-In our example, non-functional characteristics of the content provision services ({\sf e$_1$, ... e$_4$}) are calculated by services that enforce SLAs  as follows:
-\begin{trivlist}\sf\footnotesize
-\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$.
-
-                engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
-\end{trivlist}
+%In our example, non-functional characteristics of the content provision services ({\sf e$_1$, ... e$_4$}) are calculated by services that enforce SLAs  as follows:
+%\begin{trivlist}\sf\footnotesize
+%\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc).
+%QoS preferences$_\mathit{user}$.
+%
+%                engage$_i$(contents, req\_size, payment)
+                %agreedSLA$_i$.
+%\end{trivlist}
 
@@
 
-The first operation permits the user to ask for the budget of a given course (content) and a required minimmum size.
-This operation will return the cost of the data, as well as its actual size and location.
-{QoS preferences}$_\mathit{user}$ is the user's proposal to the contents provider. 
-This SLA will become the {\sf agreedSLA}$_i$, in case of availability of the contents. 
-We suppose that availability is characterized by a non-zero value of size of the provided data ({\sf prov\_size}).
+The first operation permits the user to ask for the budget of a given  content and a required minimum size.
+This operation  returns the cost of the data, as well as its actual size and location.
+%{QoS preferences}$_\mathit{user}$ expresses the user's preferences with respect to  the way she will receive content from a provider. 
+%The requirements will be matched with the agreedSLAs of the services that can provide the content, in order to derive an {\sf agreedSLA}$_i$. 
+We suppose that availability is characterized by a non-zero value representing the size of the provided data ({\sf prov\_size}) by a given service.
 The second operation is used to engage in a course. 
-The agreed SLAs are those containing the information described above in this example.
+The agreed SLAs are those containing the information described above.
 %The user will ask for a given derived SLA to which the provider may agree.
 
-Cloud providers also define their SLA contracts that specify the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+Cloud providers also define their agreed SLA contracts that specify the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
 For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
@@
 For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) and that her privacy be saved by adapting the anonymity process with regard to services reputation.
-The maximum total cost will condition also which kind of privacy preserving algorithms to apply.
+The maximum total cost will determine the kind of privacy preserving algorithms to apply.
 
-The user preferences statement would include their cloud provider contract and quality preferences:
+The user preferences statement  includes her cloud provider contract and quality preferences:
 \begin{trivlist}\sf\footnotesize
@@
 
-We consider a simplified cloud SLA contract inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
+As shown above, we consider a simplified cloud SLA contract inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
 
-The user is ready to pay a maximum of {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); even if their data are not fresh; she requires a contract duration of one week.
+As expressed in the query example, the user is ready to pay a maximum of {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); even if their data are not fresh; she requires a contract duration of one week.
 
@@
 
-As usual, SLAs will be represented as conditions over variables that will be used in the query.
-In this context, the compliance to the SLAs will drive the query rewriting process.
+%As usual, SLAs will be represented as conditions over variables that will be used in the rewritten query.
+In this context, the compliance between the QoS preferences of the user, her cloud SLAs (given by her subscriptions) and the  agreed SLAs will drive the query rewriting process.
 
 Given a requirement expressing a query and quality of service preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots, the data integration process for computing a result is done as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and agreed SLAs will be used to produce a derived SLA to be associated to the query.
-These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
-The agreed SLA proposed by the chosen services is added as  conditions in  each re-written   query expression; (iii) Managing the integration process particularly storing partial results (including in  which location data is stored), delivering data (applying security control during integration) and launching and re-launching queries.
-Intermediate results  are stored as knowledge in order to reduce the overhead of the query evaluation process.
+The derived SLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
+%These derived SLA will influence the choice of (data) services that will actually be used for building the result; 
+(ii) Query rewriting for computing service compositions that can be used for  building query results.
+The derived SLA (that copes agreed SLAs with user preferences) is added as  conditions in  each re-written   query expression; (iii) Integration SLA is computed according to the conditions in which the query will be executed.
+It will help to  manage the integration process particularly storing partial results (including in  which location data is stored), delivering data (applying security control during integration) and launching and re-launching queries.
+%Intermediate results  are stored as knowledge in order to reduce the overhead of the query evaluation process.
 
@@
 The derived SLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures.
-The derived SLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
 

### 2015-04-03 Workshop2015/current-version/incremental.tex
new current version

--- 2015-04-02 Workshop2015/current version/incremental.tex
@@
 %starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch} )
+Figure~\ref{fig:arch}). In this section, we present  step-by-step data integration process with the implied  SLA categories.
+
+In our context, data are exposed as  a set of data services on different clouds.
+In our example of MOOC system presented above, several producers will supply equivalent content for a given period of time  that will be chosen with respect to the  preferences expressed by a consumer.
+
+Given a query $Q_1$ expressed as Datalog-like program or an SQL-like expression, including spatio-temporal attributes and preferences.
+For instance, the following query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
+
+The abstract Inter-Cloud Layer (ICL) is in charge of delivering a result to the received query.
+ICL will first identify a set of semantic functionalities that fit the  query and associated services, stored in the service description registry.
+
+Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
+Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
+We represent these services by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs will have the same interface as individual service providers.
+We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
+All these services can potentially be combined for answering queries.
+
 %shows the general architecture of an SLA guided data integration system. 
@@
 
-Services are deployed in different cloud providers and each service exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data.
+Each deployed service exposes an \textit{agreed SLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
 
@@
 
-Some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
+Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
@@
 It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the clouds hosting different data services.
+An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
 
-According to our approach, content producers are modeled as data services with associated \textit{agreed SLAs}. 
-In our example of MOOC system presented above, we assume that several producers will supply equivalent content for a given period of time  that will be chosen with respect to the  preferences expressed by a consumer.
-Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
-Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}. We suppose that hubs will have the same interface as individual service providers.
-We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries.
+Examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
+The cost is determined by the  cost of the calls. 
+This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
+The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
 
-In our example, non-functional characteristics of the content provision services ({\sf e$_1$, ... e$_4$}) are calculated by services that enforce SLAs  as follows:
+As aforementioned, an a-priori SLA enforcement mechanism is mandatory to assess data integration feasibility.
+To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ...
+e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which should present an API, composed of a set of methods such as:
+
 \begin{trivlist}\sf\footnotesize
-\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$.
+\item[~-~S$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$, agreedSLA$_i$.
 
@@
 
-\color{red}
+Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, the first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
+In other words, it will returns the cost of the data, as well as its actual size and location.
 
-The first operation permits the user to ask for the budget of a given course (content) and a required minimmum size.
-This operation will return the cost of the data, as well as its actual size and location.
-{QoS preferences}$_\mathit{user}$ is the user's proposal to the contents provider. 
-This SLA will become the {\sf agreedSLA}$_i$, in case of availability of the contents. 
-We suppose that availability is characterized by a non-zero value of size of the provided data ({\sf prov\_size}).
-The second operation is used to engage in a course. 
-The agreed SLAs are those containing the information described above in this example.
+ The second method is used to engage in a data service (in our example a course data service) and will be used later if the service is retained for a composition that answer the query.
+
 %The user will ask for a given derived SLA to which the provider may agree.
 
-Cloud providers also define their SLA contracts that specify the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
+ICL by asking SCS for each semantic functionality, obtain the set of potential services that satisfy either user preferences and  service offering described through their \textit{Agreed SLAs}.
+Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the user preferences.
+For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires a contract duration of one week.
+Besides, she wishes her privacy be saved by adapting the anonymity process with regard to service reputation.
+The maximum total cost will condition also which kind of privacy preserving algorithms to apply.
+
+\begin{trivlist}\sf\footnotesize
+\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
+\end{trivlist}
+
+Cloud providers also define their SLA contracts that specify the cost per request ({cost/request}), the volume of data that can be exchanged per month ({I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({datatransferCost/region}), the storage space ({storageSpace}).
 For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
@@
 
-%A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
-
-Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, let us have the query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar}''.
-This query has two parts: the one that corresponds to the content that will be solved by combining data services and the user preferences.
-For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) and that her privacy be saved by adapting the anonymity process with regard to services reputation.
-The maximum total cost will condition also which kind of privacy preserving algorithms to apply.
-
-The user preferences statement would include their cloud provider contract and quality preferences:
+Illustration inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: 
  \begin{trivlist}\sf\footnotesize
@@
 
-We consider a simplified cloud SLA contract inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
+%A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
 
-The user is ready to pay a maximum of {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); even if their data are not fresh; she requires a contract duration of one week.
+The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process that complies both the user cloud SLAs and QoS preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots.
+ This allows computing a result as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} will be used to produce a \textit{derived SLA} to be associated to the query.
+These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
+The \textit{agreed SLA} exposed by the chosen services is added as  conditions in  each re-written query expression; Two situations could arise: a full compliance of a composition with the \textit{derived SLA} or a partial compliance that requires a negotiation step.
+For both alternatives, an \textit{integration SLA} will be produced indicating the negotiation conditions and the implementation of the final integration; (iii) and Managing the integration process according to the \textit{integration SLA}.
 
-\begin{trivlist}\sf\footnotesize
-\item[~-~SLA$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
-\end{trivlist}
-
-As usual, SLAs will be represented as conditions over variables that will be used in the query.
-In this context, the compliance to the SLAs will drive the query rewriting process.
-
-Given a requirement expressing a query and quality of service preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots, the data integration process for computing a result is done as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and agreed SLAs will be used to produce a derived SLA to be associated to the query.
-These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
-The agreed SLA proposed by the chosen services is added as  conditions in  each re-written   query expression; (iii) Managing the integration process particularly storing partial results (including in  which location data is stored), delivering data (applying security control during integration) and launching and re-launching queries.
-Intermediate results  are stored as knowledge in order to reduce the overhead of the query evaluation process.
-
-\color{black}
 %-----------------------------------------------------------------
@@
 
-The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs.
+The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs of potential com posable services.
 This  leads to a {\em derived SLA} that guides the evaluation of a query.
 
-A query has associated preferences  expressed as macroscopic constraints (i.e.
+%A query has associated preferences  expressed as macroscopic constraints (i.e.
 user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode.
@@
 
-As said before, we assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
+%As said before, we assume that services export their \textit{agreed SLAs} that define measures that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
 A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
@@
 Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-
-Examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
-The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
-The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
 
@@
 %-----------------------------------------------------------------
-%\section{Dealing with the resources consumed by the evaluation process}
-%\label{sec:queryProcessOpt}
+\section{Towards an integration SLA}
+\label{sec:queryProcessOpt}
 %-----------------------------------------------------------------
- %Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
+ Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
 This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
@@
 
- %We believe that the optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
+The optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
 Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service).
 Instead of recomputing the derived SLA every time, we propose to store it and reuse it for other queries.
-
-%Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
+Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
 Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
@@
 ).
+
+Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
+In the example this has been illustrated by  the access control level constraints demanded by data services when they are implied in an integration process.
+Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration it self.
+This leads to the build of the \textit{integration SLA}
 
@@
 Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.
-
- %Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
-In the example this has been illustrated by  the access control level constraints demanded by data services when they are implied in an integration process.
-Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration it self.
+%

### 2015-04-03 Workshop2015/current-version/incremental.tex
no message

@@
 
+\color{green}
 \begin{trivlist}\sf\footnotesize
-\item[~-~S$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$, agreedSLA$_i$.
+\item[~-~]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), 
+%QoS preferences$_\mathit{user}$, -- These should be in the query... not in the concrete services specification.
+agreedSLA$_i$.
 
-                engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
+\item[~-~]engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
 \end{trivlist}
 
-Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, the first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
+%Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
+The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
 In other words, it will returns the cost of the data, as well as its actual size and location.
@@
 
-ICL by asking SCS for each semantic functionality, obtain the set of potential services that satisfy either user preferences and  service offering described through their \textit{Agreed SLAs}.
-Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the user preferences.
-For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires a contract duration of one week.
+ICL by asking SCS for each semantic functionality, obtain the set of potential services that satisfy both user preferences and  service offering described through their \textit{Agreed SLAs}. 
+Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the \textit{user preferences}, noted by {QoS preferences}$_\mathit{user}$:
+\begin{trivlist}\sf\footnotesize
+\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost, freshness, provenance, location, duration, privacy-preserving$\rangle$. 
+\end{trivlist}
+
+\color{black}
+
+Let us suppose that for this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires a contract duration of one week.
 Besides, she wishes her privacy be saved by adapting the anonymity process with regard to service reputation.
@@
 \begin{trivlist}\sf\footnotesize
-\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
+\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
 \end{trivlist}
@@
 
-The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process that complies both the user cloud SLAs and QoS preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots.
+\color{green}
+
+The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process:
+Given the user query, specified as a sequence of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
+The algorithm in~\cite{CostaAMR13} is being modified to deal with SLA and QoS user preferences.
+
+\color{black}
+
+In this paper, we are interested in rewritten queries that comply with the user preferences,  cloud SLAs and QoS preferences.
  This allows computing a result as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} will be used to produce a \textit{derived SLA} to be associated to the query.
@@
 
+\color{green}
+Answer by Martin: The agreedSLA will be included and merged with the SLA conditions obtained by the rewriting process.
+Only those compositions that comply with the agreedSLA will be presented as solutions to the user.
+
 \color{black}
@@
 
-Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
+\color{green}
+%Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
+%Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
+
+The agreedSLA will be included and merged with the SLA conditions obtained by the rewriting process.
+Only those compositions that comply with the agreedSLA will be presented as possible solutions to the user.
+\color{black}
+
 In the case of our query example the following composition can be used for answering it:
@@
  \>  I/0 volume/month $\leq$ 8GB, \\
- \>reputation level :] $\geq \lambda$ (the threshold) \\
+ \>  reputation level $\geq \lambda$ (the threshold) \\
  \>  storageSpace $\leq$ 1GB, \\

### 2015-04-03 Workshop2015/toSubmit/introduction.tex
Version by Nadia et Chirine

--- 2015-04-02 Workshop2015/current version/introduction.tex
@@
 Therefore, we believe in the benefits of SLA-based data integration as an approach for better meeting  user requirements.
-\color{red}
-In order to do so, several granularities of SLA must be considered: (i) at the cloud level: the SLA ensured by providers regarding data; (ii) at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally (iii) at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 
-\color{black}
+To do so, several granularities of SLA must be considered: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
+
 %To better understand our problem, let us consider an example from the domain of energy
@@
 
- \color{red}
 Accordingly, the remainder of this paper is organized as follows.
-Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes.
-Section \ref{sec:incremental} gives an overview of our approach for integrating data sets provided by services (i.e., DaaS) by conciliating SLA's provided by services and user's profiles expressing QoS preferences.
-Profiles specify preferences about the data they want to consume and the conditions in which they must be processed and delivered.
+Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments.
+Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process.
+Section \ref{sec:derivedSla}, \ref{sec:queryRew} and \ref{sec:queryProcessOpt} give an idea of the main steps of our proposal.
+Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.
 %Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach.
-Finally \ref{sec:conclusions} concludes the papers and discusses future work.
-
-\color{black}

### 2015-04-29 Workshop2015/camera-ready/incremental.tex
new fie for working on the camera ready

--- 2015-04-03 Workshop2015/current-version/incremental.tex
@@
 
-Each deployed service exposes an \textit{agreed SLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
+Each deployed service exposes an \textit{agreedSLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
 
@@
 It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the clouds hosting different data services.
-An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
+An \textit{agreedSLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
 
@@
 
-\color{green}
 \begin{trivlist}\sf\footnotesize
@@
 
-ICL by asking SCS for each semantic functionality, obtain the set of potential services that satisfy both user preferences and  service offering described through their \textit{Agreed SLAs}. 
+ICL by asking SCS for each semantic functionality, obtains the set of potential services that satisfy both user preferences and  service offering described through their \textit{agreed SLAs}. 
 Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the \textit{user preferences}, noted by {QoS preferences}$_\mathit{user}$:
@@
 \end{trivlist}
-
-\color{black}
 
@@
 
-\color{green}
+The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process.
+Given the user query, specified as a sequence of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
+The algorithm in~\cite{CostaAMR13} is being modified to deal with agreedSLA and QoS user preferences.
 
-The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process:
-Given the user query, specified as a sequence of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
-The algorithm in~\cite{CostaAMR13} is being modified to deal with SLA and QoS user preferences.
-
-\color{black}
-
-In this paper, we are interested in rewritten queries that comply with the user preferences,  cloud SLAs and QoS preferences.
- This allows computing a result as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} will be used to produce a \textit{derived SLA} to be associated to the query.
-These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
-The \textit{agreed SLA} exposed by the chosen services is added as  conditions in  each re-written query expression; Two situations could arise: a full compliance of a composition with the \textit{derived SLA} or a partial compliance that requires a negotiation step.
-For both alternatives, an \textit{integration SLA} will be produced indicating the negotiation conditions and the implementation of the final integration; (iii) and Managing the integration process according to the \textit{integration SLA}.
+In this paper, we are interested in rewritten queries that comply with the QoS user preferences and cloudSLAs.
+ This allows computing a result as follows: (i) User preferences (including cloudSLAs according to user subscriptions) and \textit{agreedSLAs} will be used to produce a \textit{derivedSLA} to be associated to the query.
+These derivedSLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
+The \textit{agreedSLA} exposed by the chosen services is added as  conditions in  each re-written query expression; Two situations could arise: a full compliance of a composition with the \textit{derivedSLA} or a partial compliance that requires a negotiation step.
+For both alternatives, an \textit{integrationSLA} will be produced indicating the negotiation conditions and the implementation of the final integration; (iii) and Managing the integration process according to the \textit{integrationSLA}.
 
 %-----------------------------------------------------------------
-\section{Derived SLA}
-\label{sec:slaModel}
+\section{DerivedSLA}
+\label{sec:derivedSla}
 %-----------------------------------------------------------------
 
-The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs of potential com posable services.
-This  leads to a {\em derived SLA} that guides the evaluation of a query.
+The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedSLAs of potential com posable services.
+This  leads to a {\em derivedSLA} that guides the evaluation of a query and maps SLA measures and preferences attributes.
 
@@
 
-Given agreed SLAs and a user preferences statement the challenge is to compute a  {\em derived SLA} that  maps SLA measures and preferences attributes.  
-The derived SLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
-The derived SLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
+The derivedSLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
+The derivedSLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
 
-In the example, some of the user preferences statement measures are used for defining a derived SLA that, as said in previous section, will guide the evaluation of the query. 
-These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
+In the example, some of the user preferences statement measures are used for defining a derivedSLA that, as said in previous section, will guide the evaluation of the query. 
+These measures are defined as a function of the measures used by the agreedSLAs and by the cloud SLA contract. For example: 
 \begin{trivlist}\sf\footnotesize
@@
 
-Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. 
+Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by agreedSLAs and coarse grained measures used in user preferences statements. 
 It specifies also how to compute coarse grained measures with fine grained ones. 
 For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The derived SLA can be seen as a set of inequations that have to be solved during the execution of a service composition.
+The derivedSLA can be seen as a set of inequations that have to be solved during the execution of a service composition.
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
-We will discuss this issue in the next sections.
-
-This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
-Negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
+This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between agreedSLAs and the derivedSLA, which  leads us to the proposal for a negotiated integration SLA  and thus the need for an adaptive setting.
+Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
 This negotiation can be expensive and may not scale well.
 
-Given a query and its preferences statement, the system  finds  service compositions that produce results   meeting the required constraints, as discussed in the following section.
+%Given a query and its preferences statement, the system  finds  service compositions that produce results meeting the required constraints, as discussed in the following section.
+The resulting derivedSLA will be used in the query rewriting step described in the next section.
 
@@
 
-\color{red}
-One point remain very crucial to fix: once the multi-cloud layer generate a list of derived SLA corresponding to Agreed-SLA of services that could match a part of the query, What should happen?
-With whom rewritten query using user preferences is matched with SLA and which one (not clear in the paper.
-This point should be discussed quickly.
-The workflow of SLA between the abstract layer and cloud is not so clearly described.
-
-\color{green}
-Answer by Martin: The agreedSLA will be included and merged with the SLA conditions obtained by the rewriting process.
-Only those compositions that comply with the agreedSLA will be presented as solutions to the user.
-
-\color{black}
 Query rewriting is a well-known problem in the database domain.
@@
 We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
-The MOOC has four information hubs, located in four different geographic locations, connected to other content providers.
-Content providers may be  contacted directly, through the services of three different cloud providers.
-Each cloud provider exports its own interfaces.
-SLAs are defined for each individual content provider server and  each hub(agreed SLA)  , and also for each cloud provider (traditional SLA contracts).
+The MOOC has four information hubs described by their agreedSLAs, located in four different geographic locations, connected to other content providers.
+These laters may be  contacted directly, through the services of three different cloud providers that exposes their CloudSLA.
 
@@
 Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should also been expressed in the user preferences and SLAs.
+These conditions and non-functional requirements (such as authentication or security requirements) should also been expressed in the QoS user preferences and agreedSLAs.
 
 In this context, the user  expresses a content order, her location and payment information. A composite web service is  generated to fulfill the order.
-The generated service composition should consider the nearest providers, in accordance to the agreed SLA.
+The generated service composition should consider the nearest providers, in accordance to the agreedSLA.
 
-In order to produce a personalized service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
-The specification of each available service is also considered (this specification should be given by the service provider).
+In order to produce a personalized service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
+The specification of each available service is also considered is given.
 %~\hfill\openbox
@@
 
-\color{green}
 %Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
@@
 Only those compositions that comply with the agreedSLA will be presented as possible solutions to the user.
-\color{black}
 
@@
 
-Our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
- Yet, the algorithm should be modified to take into account the different SLAs. The next example illustrates one of the limits of the automatic composition algorithm.
-
-\color{red}
-\begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the content  trade system of the MOOC example.
- Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
-In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
-Let us suppose that, in order to minimize the  communications between servers, the lists need to be produced incrementally.
-In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
-The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.
-
-To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
-~\hfill\openbox
-\end{example}
-
-\color{black}
+Our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derivedSLA are verified. 
+ Yet, the algorithm should be modified to take into account the different SLAs.
 
@@
 
-The optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
+The optimization of this process can occur at two levels: first at the level of agreedSLA exported by services.
 Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service).
-Instead of recomputing the derived SLA every time, we propose to store it and reuse it for other queries.
+Instead of recomputing the derivedSLA every time, we propose to store it and reuse it for other queries.
 Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.

### 2015-04-29 Workshop2015/camera-ready/incrementalbis.tex
new fie for working on the camera ready

--- 2015-04-02 Workshop2015/current version/incremental.tex
@@
 %starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch} )
+Figure~\ref{fig:arch}). In this section, we present  a step-by-step data integration process with the implied  SLA categories.
+
 %shows the general architecture of an SLA guided data integration system. 
@@
 
-In our example, non-functional characteristics of the content provision services ({\sf e$_1$, ... e$_4$}) are calculated by services that enforce SLAs  as follows:
+As aforementioned, an a-priori SLA enforcement mechanism is mandatory to assess data integration feasibility.
+To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ...
+e$_4$}) are calculated by specific cloud services that enforce SLAs  and which should present an API, composed of a set of methods such as:
+
 \begin{trivlist}\sf\footnotesize
-\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$.
+\item[~-~S$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$, agreedSLA$_i$.
 
@@
 
-\color{red}
+Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, the first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
+In other words, it will returns the cost of the data, as well as its actual size and location.
 
-The first operation permits the user to ask for the budget of a given course (content) and a required minimmum size.
-This operation will return the cost of the data, as well as its actual size and location.
-{QoS preferences}$_\mathit{user}$ is the user's proposal to the contents provider. 
-This SLA will become the {\sf agreedSLA}$_i$, in case of availability of the contents. 
-We suppose that availability is characterized by a non-zero value of size of the provided data ({\sf prov\_size}).
-The second operation is used to engage in a course. 
-The agreed SLAs are those containing the information described above in this example.
+ The second method is used to engage in a data service (in our example a course data service) and will be used later if the service is retained for a composition that answer the query.
+
 %The user will ask for a given derived SLA to which the provider may agree.
@@
 
+Illustration inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: 
+ \begin{trivlist}\sf\footnotesize
+\item[~-~cloudSLA:]  $\langle$0,05 cents per call, 8 GB I/0 volume/month, free, 1 GB storage$\rangle$. 
+\end{trivlist}
+
 %A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
@@
 Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, let us have the query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar}''.
+For instance, let us have the query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
 This query has two parts: the one that corresponds to the content that will be solved by combining data services and the user preferences.
@@
 The user preferences statement would include their cloud provider contract and quality preferences:
-\begin{trivlist}\sf\footnotesize
-\item[~-~cloudSLA:]  $\langle$0,05 cents per call, 8 GB I/0 volume/month, free, 1 GB storage$\rangle$. 
-\end{trivlist}
-
-We consider a simplified cloud SLA contract inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
 
@@
 \begin{trivlist}\sf\footnotesize
-\item[~-~SLA$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
+\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
 \end{trivlist}
@@
 
-\color{black}
 %-----------------------------------------------------------------

### 2015-04-29 Workshop2015/camera-ready/relwork.tex
new fie for working on the camera ready

--- 2015-02-22 Workshop2015/relwork.tex
@@
 
-The advent of cloud computing imposed a new model for resource consuming that is not concerned
- with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
-Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing to establish those conditions.
-The adoption of SLAs relies on two principles: (i) The negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
+%Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing to establish those conditions. 
+In the cloud, the adoption of SLAs relies on two principles: (i) The negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
 
@@
 %Indeed, 
-SLAs are normally expressed in terms of \textit{technical} measures, like the storage space size  or the degree of virtualization. 
+SLAs are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size  or the degree of virtualization. 
 On the user side, the interest is normally on \textit{service} delivery measures such as QoS requirements.
@@
 This leads to an interoperable security expression that can be used by users for comparing security levels of different cloud service providers.
+Hale and Al.
+in \cite{6655684} extends their first work proposing an ontology representation of security concerns and let security services expressed in SLA connected to documents regulating security controls.
 \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
@@
 \cite{5614035} proposes LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+
+Regarding recent work on SLA modeling in the cloud, it clearly appears that no work has been proposed before using SLA for data integration.
+Furthermore, SLA are exclusively used in a mono-cloud context, low level oriented and serve to express condition in which a user could exploit cloud ressources.
+Whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels (users, services, clouds and inter-cloud environnements).
+Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility.
 

### 2015-04-30 Workshop2015/camera-ready/incremental.tex
First changes

@@
 %-----------------------------------------------------------------
-\section{DerivedSLA}
+\section{Deriving SLA}
 \label{sec:derivedSla}
@@
 The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedSLAs of potential com posable services.
-This  leads to a {\em derivedSLA} that guides the evaluation of a query and maps SLA measures and preferences attributes.
+This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and preferences attributes.
 
@@
 
-The derivedSLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
+The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
 The derivedSLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
@@
 %-----------------------------------------------------------------
-\section{Towards an integration SLA}
+\section{First approach for deriving an Integration SLA}
 \label{sec:queryProcessOpt}

### 2015-04-30 Workshop2015/toSubmit/introduction.tex
First changes

@@
 \color{black}
-The advent of cloud computing imposed a new model for resource consuming that is not concerned
- with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially unlimited resources.
-Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them taking into consideration their "structural" characteristics (due to the different data models) but also their quality, e.g., trust, freshness, provenance, partial or total consistency.
+The advent of cloud computing imposed a new   resource consuming model concerned
+with the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources.
+Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them considering their "structural" characteristics (due to the different data models) and  their quality, e.g., trust, freshness, provenance, partial or total consistency.
 Existing data integration techniques have to be revisited considering weakly curated and modeled data sets.
-This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by the cloud providers that host  these collections and deliver resources for executing the associated management processes.
+This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services and cloud providers that host  these collections and deliver resources for executing the associated processing and integration processes.
 In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. 
-Therefore, we believe in the benefits of SLA-based data integration as an approach for better meeting  user requirements.
+We believe in the benefits of SLA-based data integration as an approach for better meeting  user  requirements related to the conditions in which data is integrated and delivered and on the quality of the data provided by services.
 
-To do so, several granularities of SLA must be considered: first, at the cloud level; the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fit particular service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
+To do so, several granularities of SLA must be considered: first, at the cloud level: the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fulfill  specific service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
 
@@
 
- In this paper, we present  a preliminary solution addressing the issues described above.
+This paper introduces a preliminary solution addressing the issues described above.
 Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.

### 2015-04-30 Workshop2015/toSubmit/introduction.tex
More changes on introduction

@@
 
-To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and expertise of participants. 
-Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
-cost, inscription, or exchange unit), and the time window in which they can produce contents.
-Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content.
-The MOOC  aims at being privacy respectful of the students participating in courses.
+To better understand our problem, consider a massive open online course system (MOOC) where users produce and consume content according to the geographic area and the expertise of participants. 
+Producers are characterized according to their location, the type and topic of  content  they can provide, the access conditions (e.g.
+cost, inscription, or exchange unit), and the time window in which they can produce content.
+Consumers are characterized by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content.
+Both producers and consumers have subscriptions to different cloud providers for dealing with contents exchange.
+The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
  Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.
 According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1).
-Furthermore,  data providers could  also wish to give restricted data access credentials w.r.t.
+Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t.
 to their own, when their data are used  within  an integration process (Constraint 2).
@@
 In any case, how should the results of  such a  complex process  be capitalized for further integration requests?
+The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a result for a given query.
 
-This paper introduces a preliminary solution addressing the issues described above.
+ We have proposed such architecture in \cite{ghediraetal2014}.
+With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process.
+Therefore, this paper introduces a preliminary solution addressing the issues described above.
 Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.

### 2015-04-30 Workshop2015/camera-ready/incremental.tex
New version

--- 2015-04-29 Workshop2015/camera-ready/incremental.tex
@@
 
-In our context, data are exposed as  a set of data services on different clouds.
-In our example of MOOC system presented above, several producers will supply equivalent content for a given period of time  that will be chosen with respect to the  preferences expressed by a consumer.
+In our context, data are provided by services deployed on different clouds.
+In the example of the MOOC system presented above, several producers will supply equivalent content for a given period of time.
+They    will be chosen with respect to the  preferences expressed by a consumer.
 
-Given a query $Q_1$ expressed as Datalog-like program or an SQL-like expression, including spatio-temporal attributes and preferences.
-For instance, the following query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
+Consumers will express queries  expressed as  Datalog-like programs or  SQL-like expressions, including spatio-temporal attributes and preferences.
+For instance, the following query $Q_1$ ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
 
-The abstract Inter-Cloud Layer (ICL) is in charge of delivering a result to the received query.
-ICL will first identify a set of semantic functionalities that fit the  query and associated services, stored in the service description registry.
+The abstract Inter-Cloud Layer (ICL) delivers the results to the  query.
+The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query.
+These descriptions are stored in a service description registry (SCS).
 
 Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
-Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these services by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs will have the same interface as individual service providers.
+Hubs  store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
+We represent these providers respectively by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs  have the same interface as individual service providers.
 We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries.
+All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements associated to the query.
 
@@
 \includegraphics[width=0.75\textwidth]{workflow.pdf}
-\caption{Phases of an SLA guided  data integration workflow.\label{fig:arch}}}
+\caption{SLA guided  data integration workflow.\label{fig:arch}}}
 \end{figure*}
@@
 
-Each deployed service exposes an \textit{agreedSLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
+Each deployed service exports an \textit{agreed SLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
 
@@
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
-It is the case for service reputation that will condition the way personal user data will be anonymized (Constraint1).
+It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).
 Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment.
-It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the clouds hosting different data services.
-An \textit{agreedSLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
+It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
+An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
 
-Examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
+In our scenario, examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
 The cost is determined by the  cost of the calls. 
@@
 To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ...
-e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which should present an API, composed of a set of methods such as:
+e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which export  an API, composed of the following set of methods:
 
@@
 The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
-In other words, it will returns the cost of the data, as well as its actual size and location.
-
-The second method is used to engage in a data service (in our example a course data service) and will be used later if the service is retained for a composition that answer the query.
+In other words, it  returns the cost of the data, as well as its  size and location.
+The second method is used to engage to a data service (in our example a content data service) and will be used  if the service is retained for a composition to answer the query.
 
@@
 
-ICL by asking SCS for each semantic functionality, obtains the set of potential services that satisfy both user preferences and  service offering described through their \textit{agreed SLAs}. 
-Indeed, the query $Q_1$ has two parts: the one that corresponds to the content asked for by the user  that will be solved by combining data services and the \textit{user preferences}, noted by {QoS preferences}$_\mathit{user}$:
+The ICL  obtains the set of potential services that satisfy both user preferences and   \textit{agreed SLAs} associated to services. 
+For instance, the query $Q_1$ has two parts: the one that corresponds to the content required by the user  that will be solved by combining data services and the \textit{user preferences}, given by {QoS preferences}$_\mathit{user}$:
 \begin{trivlist}\sf\footnotesize
@@
 
-Let us suppose that for this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires a contract duration of one week.
-Besides, she wishes her privacy be saved by adapting the anonymity process with regard to service reputation.
-The maximum total cost will condition also which kind of privacy preserving algorithms to apply.
+Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week.
+Besides, she wishes to keep the content exchange private and she wants to order services by reputation.
+The maximum total cost will condition also the kind of privacy preserving algorithms that will be applied.
 
@@
 
-Cloud providers also define their SLA contracts that specify the cost per request ({cost/request}), the volume of data that can be exchanged per month ({I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({datatransferCost/region}), the storage space ({storageSpace}).
-For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
+Cloud providers also define their SLA contracts that specify the cost per request ({cost/request}), the volume of data that can be exchanged per month ({I/0 volume/month}), the cost of transferring data or applications within the same data center or across other data centers ({datatransferCost/region}), the storage space ({storageSpace}).
+For example, some cloud providers let the customer  choose the geographical zone to install PaaS services and deploy applications (e.g.
 zone 1 is Europe).
@@
 The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process.
-Given the user query, specified as a sequence of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
+Given the user query, specified as a set of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
 The algorithm in~\cite{CostaAMR13} is being modified to deal with agreedSLA and QoS user preferences.
 
-In this paper, we are interested in rewritten queries that comply with the QoS user preferences and cloudSLAs.
- This allows computing a result as follows: (i) User preferences (including cloudSLAs according to user subscriptions) and \textit{agreedSLAs} will be used to produce a \textit{derivedSLA} to be associated to the query.
-These derivedSLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
-The \textit{agreedSLA} exposed by the chosen services is added as  conditions in  each re-written query expression; Two situations could arise: a full compliance of a composition with the \textit{derivedSLA} or a partial compliance that requires a negotiation step.
-For both alternatives, an \textit{integrationSLA} will be produced indicating the negotiation conditions and the implementation of the final integration; (iii) and Managing the integration process according to the \textit{integrationSLA}.
+In this paper, we are interested in the process of rewriting queries  considering QoS user preferences and SLAs.
+This process includes the following phases: 
+\begin{enumerate}
+\item  User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} are  used to produce a \textit{derived SLA} to be associated to the query.
+The {\em derived SLA}  influences the choice of (data) services that will actually be used for building the result;
+\item Computing service compositions that rewrite the initial query and that can be used for  building query results.
+The \textit{agreed SLA} exported by the chosen services is added as  conditions in  each re-written query expression.
+Rewritten queries expressed as service composition can fully or partially comply with the \textit{derived SLA}.
+An \textit{integration SLA} is  computed for guiding  negotiation (in the case of partial compliance)  and the implementation of the final integration;
+\item   Managing the integration process according to the \textit{integration SLA}.
+\end{enumerate}
 
 %-----------------------------------------------------------------
-\section{DerivedSLA}
+\section{Computing a derived SLA}
 \label{sec:derivedSla}
@@
 
-The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedSLAs of potential com posable services.
-This  leads to a {\em derivedSLA} that guides the evaluation of a query and maps SLA measures and preferences attributes.
+The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedS LAs of potential composable services.
+This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and QoS preferences attributes.
 
@@
 
-The derivedSLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
-The derivedSLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
+The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures that can come from the evaluation of measures expressed in the cloud subscription of the user.
+The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.
 
-In the example, some of the user preferences statement measures are used for defining a derivedSLA that, as said in previous section, will guide the evaluation of the query. 
-These measures are defined as a function of the measures used by the agreedSLAs and by the cloud SLA contract. For example: 
+In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
+These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
 \begin{trivlist}\sf\footnotesize
@@
 
-Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by agreedSLAs and coarse grained measures used in user preferences statements. 
+Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by {\em agreed SLAs} and coarse grained measures used in user preferences statements.
 It specifies also how to compute coarse grained measures with fine grained ones. 
 For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The derivedSLA can be seen as a set of inequations that have to be solved during the execution of a service composition.
+The {\em derived SLA} can be seen as a set of inequations that have to be solved during the execution of a service composition.
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
-This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between agreedSLAs and the derivedSLA, which  leads us to the proposal for a negotiated integration SLA  and thus the need for an adaptive setting.
-Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
+This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}.
+In order to address this problem we introduce the notion of  {\em integration SLA}.
+%and thus the need for an adaptive setting.
+%Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
 This negotiation can be expensive and may not scale well.
@@
 %Given a query and its preferences statement, the system  finds  service compositions that produce results meeting the required constraints, as discussed in the following section.
-The resulting derivedSLA will be used in the query rewriting step described in the next section.
+%The resulting derivedSLA will be used in the query rewriting step described in the next section.
 
@@
 
-Query rewriting is a well-known problem in the database domain.
-The problem consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
+Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
 %Query rewriting is guided by the schema of  abstract and concrete databases.
@@
 %\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the MOOC scenario, where people can participate on an content trading pool.
+Let us consider the MOOC scenario, where people can participate on a content trading pool.
 We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
-The MOOC has four information hubs described by their agreedSLAs, located in four different geographic locations, connected to other content providers.
-These laters may be  contacted directly, through the services of three different cloud providers that exposes their CloudSLA.
+The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
+These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.
 
-When an on-line consumer searches servers to buy/retrieve content, a composed web service is generated, in order to fetch each individual or hub service and to start  content retrieval procedures.
+When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
 Depending on the location of the consumer and producers, different conditions and constraints may apply.
 Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should also been expressed in the QoS user preferences and agreedSLAs.
+These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.
 
-In this context, the user  expresses a content order, her location and payment information. A composite web service is  generated to fulfill the order.
-The generated service composition should consider the nearest providers, in accordance to the agreedSLA.
+In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
+The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.
 
-In order to produce a personalized service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
-The specification of each available service is also considered is given.
+In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
+The specification of each available service is also considered.
 %~\hfill\openbox
@@
 
-The agreedSLA will be included and merged with the SLA conditions obtained by the rewriting process.
-Only those compositions that comply with the agreedSLA will be presented as possible solutions to the user.
+The {\em agreed SLA} is included and merged with the SLA conditions obtained by the rewriting process.
+Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
 
@@
 
-Our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derivedSLA are verified. 
- Yet, the algorithm should be modified to take into account the different SLAs.
+Our approach  generates a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the {\em derived SLA} are verified. 
+ Yet, the current version of the algorithm should be modified to take into account the different SLAs.
 
 %-----------------------------------------------------------------
-\section{Towards an integration SLA}
+\section{Deriving an Integration SLA: first approach}
 \label{sec:queryProcessOpt}
 %-----------------------------------------------------------------
- Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
-This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
+ Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of the clouds involved.
+This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be used in a query evaluation process.
 It is thus important to optimize the use of these resources.
 
-The optimization of this process can occur at two levels: first at the level of agreedSLA exported by services.
-Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service).
-Instead of recomputing the derivedSLA every time, we propose to store it and reuse it for other queries.
+The optimization of this process can occur at two levels: first at the level of the {\em agreed SLA} exported by services.
+Indeed, queries requesting the same service compositions will have clauses that are  conditions of use of the infrastructure (i.e., not storing the data produced by a service).
+Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it for other queries.
 Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
 Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
-Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ...
-).
+Storing or not such SLAs  depends on the cloud subscription of the user that issued the query (data access, intermediate storage capacity, cost of storage, etc.).
 
-Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
-In the example this has been illustrated by  the access control level constraints demanded by data services when they are implied in an integration process.
-Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration it self.
-This leads to the build of the \textit{integration SLA}
+Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account as integration constraints.
+In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process.
+Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself.
+This leads to the build of the \textit{integration SLA}.
 

### 2015-04-30 Workshop2015/camera-ready/introduction.tex
New version

--- 2015-04-30 Workshop2015/toSubmit/introduction.tex
@@
 \color{black}
-The advent of cloud computing imposed a new   resource consuming model concerned
-with the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources.
-Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, filtering them considering their "structural" characteristics (due to the different data models) and  their quality, e.g., trust, freshness, provenance, partial or total consistency.
+The advent of cloud computing has imposed a new   resource consuming model that focusses on
+ the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources.
+Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, and filtering them considering their "structural" characteristics (data variety that implies different formats and data models) and  their quality, e.g., trust, freshness, provenance, partial or total consistency.
 Existing data integration techniques have to be revisited considering weakly curated and modeled data sets.
-This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services and cloud providers that host  these collections and deliver resources for executing the associated processing and integration processes.
+This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services and cloud providers that host  these collections and deliver resources for executing  associated processing and integration processes.
 In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. 
-We believe in the benefits of SLA-based data integration as an approach for better meeting  user  requirements related to the conditions in which data is integrated and delivered and on the quality of the data provided by services.
-
-To do so, several granularities of SLA must be considered: first, at the cloud level: the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fulfill  specific service needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties to data (trust, privacy, reliability, etc).
+We believe in the benefits of SLA-based data integration as an approach for better meeting  user  requirements related to the conditions in which data is delivered and integrated, and on the quality of the data provided by services.
+To do so, several granularities of SLA must be considered: first, at the cloud level: the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fulfill  specific  needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties for data (trust, privacy, reliability, etc).
 
@@
 cost, inscription, or exchange unit), and the time window in which they can produce content.
-Consumers are characterized by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content.
-Both producers and consumers have subscriptions to different cloud providers for dealing with contents exchange.
+Consumers are characterized by their location, their interests  during a certain interval of time, the maximum total cost they are ready to pay consuming content, or the resources they are ready to provide in order to get the service, and QoS requirements such as availability and how critical it is to consume a given type of content.
+Both producers and consumers have subscriptions to different cloud providers for dealing with content storage, processing and exchange.
 The MOOC  aims at being privacy respectful of the producers and consumers participating in courses.
@@
 Second, data services contracts should not be neglected in an integration process (Constraint 2).
-As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made and in which conditions.
-In fact, integration could be sometimes realized enforcing all specified conditions; we can also expect situations where they can be verified partially.
-In any case, how should the results of  such a  complex process  be capitalized for further integration requests?
+As data services are deployed in a multi-cloud context, there is a need to establish the rules to determine how integration can be done and in which conditions.
+Intuitively, integration can be  done enforcing all specified conditions; but it is also possible to  expect situations where conditions can only be verified partially.
+Furthermore,  matching data providers with requests and QoS preferences with SLA's can be computationally costly.
+For this reason  the results of  such a  complex process  should be capitalized for further integration requests.
+How can this be done?
 The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a result for a given query.
 
- We have proposed such architecture in \cite{ghediraetal2014}.
+ We have proposed such architecture in \cite{DBLP:conf/IEEEcloud/2014}.
 With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process.
-Therefore, this paper introduces a preliminary solution addressing the issues described above.
-Our solution is SLA-guided: We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
+Then, this paper introduces a preliminary solution addressing SLA-guided data integration focussing particularly on security issues.
+We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
 Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services.
-The derived SLA allows to choose  services (w.r.t user demands) that can contributed for answering a query.
+The derived SLA allows to choose  services (w.r.t user demands) that can contribute for answering a query.
 Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.

### 2015-04-30 Workshop2015/camera-ready/relwork.tex
New version

--- 2015-02-22 Workshop2015/relwork.tex
@@
-%\begin{itemize}
-%\item Cloud computing represents a novel on-demand computing approach where resources are provided in compliance to a set of predefined non-functional properties specified and negotiated by means of Service Level Agreements (SLAs).
-SLA currently exploited in the cloud allows service providers and cloud client to fix the resource level that should be used either by a service for the service provider or by the client in the case of service invokation.
-SLA could concern all types of the services on the cloud (IAAS, PAAS or SAAS).
-One of the weakness of SLA for the client is that they express low level clauses like storage amount use or virtualization level.
-In fact when a client launches a task on the cloud, she has unlikely Q \& S requirement rather than low level features.
-Recently we notice the existing of a lot of works with the objective to fill the gap.
-Emeakaroha and al propose in \cite{5547150}  a cloud component that acts autonomously based on low level  monitored features after analysing them towards high level clauses expressed by the user.
-Moreover, another difficulty to enforce an SLA is to measure and identify, starting from a high level SLA clause, how could it be declined at different layers in the cloud.
-Therefore in \cite{Dastjerdi:2012:DOA:2275356.2275360} the authors describe a semanticSLA which can be understood by all parties including providers,
-%requestors, and monitoring services.
-One of the major objectives in the cloud is to anticipate SLA violation and to assess SLA failure cascading on violation detection.
-\cite{Dastjerdi:2012:DOA:2275356.2275360} proposes an SLA dependency modeling using Web Service Modeling Ontology (WSMO) to build a knowledge database.
-\cite{5547150} proposes to anticipate failure by analysing the monitored feature and to act by anticipation.
-in \cite{5614035}, the authors propose LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
-%On the other hand SLA contracts do not cover all client requirement. There is still a lack in some domain.....(to be completed)
-
-%\item some
-
-The advent of cloud computing imposed a new model for resource consuming that is not concerned
- with resource availability but with the \textit{technical and economic} conditions to be fulfilled in order to access a potentially infinite set of resources. 
-Service Level Agreements (SLA)~\cite{SLA} can be used in the context of cloud computing to establish those conditions.
-The adoption of SLAs relies on two principles: (i) The negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii) The monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
+In the cloud, the   SLA's rely on two principles: (i)  negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii)  monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
 
@@
 %Indeed, 
-SLAs are normally expressed in terms of \textit{technical} measures, like the storage space size  or the degree of virtualization. 
-On the user side, the interest is normally on \textit{service} delivery measures such as QoS requirements.
-The challenge is to couple technical and service delivery measures expressed in SLA in order to agree on the conditions in which they will interact.
-Existing works use matching and negociation techniques for addressing this challenge.
+SLA's are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
+From the user point of view, the interest is normally on \textit{service} delivery measures that are related with her QoS requirements like service availability, resilience, recovery time or cost.
+The challenge is to couple technical and service delivery measures expressed in SLA's in order to agree on the conditions in which they will be considered for executing tasks for a user.
+Existing works use matching and negotiation techniques for addressing this challenge.
 For instance,~\cite{5547150} 
@@
   proposes a set of templates to  cloud data services users, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
-The client  chooses among the proposed tempates the one that best corresponds   to her requirements.
+The client  chooses among the proposed templates the one that best corresponds   to her requirements.
 \cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters.
@@
 
-Recent  works on SLA are devoted to extend  SLA for including  security concerns. 
+Recent  works on SLA are devoted to extend  SLA specifications for including  security concerns. 
 \cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
@@
 terms (SDTs) and the service level objectives (SLOs) of the SLA. 
-This leads to an interoperable security expression that can be used by users for comparing security levels of different cloud service providers. 
+This leads to an interoperable security expression that can be used by users for comparing security levels of different cloud  providers.
+Hale and Al.
+in \cite{6655684} extend their first work proposing an ontology representation of security concerns and connect security services expressed in SLA  to documents regulating security controls.
 \cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
@@
 \cite{Dastjerdi:2012:DOA:2275356.2275360}  proposes an SLA dependency model using Web Service Modeling Ontology (WSMO) to build a knowledge database.
-\cite{5614035} proposes to anticipate failure by analysing the monitored feature.
+\cite{5614035} proposes to anticipate failure by analyzing the monitored feature.
 \cite{5614035} proposes LAYSI, a layered solution that minimizes user interactions with the system and prevents violations of agreed SLAs.
+
+ Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, maybe because measures concern data services and not data itself.
+Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources.
+Whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).
+Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility.
+\cite{anisetti2014auctions} proposed an e-auctions based approach for matching services with requirements in multi-cloud settings.
+Our work aims at going further in the use of SLA for integrating data and it provides strategies to guide the whole data integration process.
 

### 2015-05-01 Workshop2015/camera-ready/computingDerivSLA.tex
explanations about rewritings

--- 2015-04-30 Workshop2015/camera-ready/incremental.tex
@@
-To answer the needs expressed above, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
-%starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch}). In this section, we present  step-by-step data integration process with the implied  SLA categories.
-
-In our context, data are provided by services deployed on different clouds.
-In the example of the MOOC system presented above, several producers will supply equivalent content for a given period of time.
-They    will be chosen with respect to the  preferences expressed by a consumer.
-
-Consumers will express queries  expressed as  Datalog-like programs or  SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, the following query $Q_1$ ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
-
-The abstract Inter-Cloud Layer (ICL) delivers the results to the  query.
-The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query.
-These descriptions are stored in a service description registry (SCS).
-
-Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
-Hubs  store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these providers respectively by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs  have the same interface as individual service providers.
-We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements associated to the query.
-
-%shows the general architecture of an SLA guided data integration system. 
-%It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
-
-%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following lines describe how this query is evaluated according to our approach.
-
-\begin{figure*}
-\center{
-\includegraphics[width=0.75\textwidth]{workflow.pdf}
-\caption{SLA guided  data integration workflow.\label{fig:arch}}}
-\end{figure*}
-
-%In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
-%Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
-cost, inscription, or exchange unit), and the time window in which they can produce contents.
-%Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
-%An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
-
-Each deployed service exports an \textit{agreed SLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
-
-%NOTE: Agreed SLA are client-provider slas... --MARTIN
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, data access control, certified reputation level, location, duration$\rangle$. 
- \end{trivlist}
-
-Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
-In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
-It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).
-Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment.
-It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
-An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-
-In our scenario, examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
-The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
-The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
-
-As aforementioned, an a-priori SLA enforcement mechanism is mandatory to assess data integration feasibility.
-To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ...
-e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which export  an API, composed of the following set of methods:
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), 
-%QoS preferences$_\mathit{user}$, -- These should be in the query... not in the concrete services specification.
-agreedSLA$_i$.
-
-\item[~-~]engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
-\end{trivlist}
-
-%Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
-The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
-In other words, it  returns the cost of the data, as well as its  size and location.
-The second method is used to engage to a data service (in our example a content data service) and will be used  if the service is retained for a composition to answer the query.
-
-%The user will ask for a given derived SLA to which the provider may agree.
-
-The ICL  obtains the set of potential services that satisfy both user preferences and   \textit{agreed SLAs} associated to services. 
-For instance, the query $Q_1$ has two parts: the one that corresponds to the content required by the user  that will be solved by combining data services and the \textit{user preferences}, given by {QoS preferences}$_\mathit{user}$:
-\begin{trivlist}\sf\footnotesize
-\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost, freshness, provenance, location, duration, privacy-preserving$\rangle$. 
-\end{trivlist}
-
-Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week.
-Besides, she wishes to keep the content exchange private and she wants to order services by reputation.
-The maximum total cost will condition also the kind of privacy preserving algorithms that will be applied.
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
-\end{trivlist}
-
-Cloud providers also define their SLA contracts that specify the cost per request ({cost/request}), the volume of data that can be exchanged per month ({I/0 volume/month}), the cost of transferring data or applications within the same data center or across other data centers ({datatransferCost/region}), the storage space ({storageSpace}).
-For example, some cloud providers let the customer  choose the geographical zone to install PaaS services and deploy applications (e.g.
-zone 1 is Europe).
-If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.
-
-\begin{trivlist}\sf\footnotesize
- \item[~-~cloudSLA:]  $\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$.
- \end{trivlist}
-
-Illustration inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: 
- \begin{trivlist}\sf\footnotesize
-\item[~-~cloudSLA:]  $\langle$0,05 cents per call, 8 GB I/0 volume/month, free, 1 GB storage$\rangle$. 
-\end{trivlist}
-
-%A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
-
-The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process.
-Given the user query, specified as a set of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
-The algorithm in~\cite{CostaAMR13} is being modified to deal with agreedSLA and QoS user preferences.
-
-In this paper, we are interested in the process of rewriting queries  considering QoS user preferences and SLAs.
-This process includes the following phases: 
-\begin{enumerate}
-\item  User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} are  used to produce a \textit{derived SLA} to be associated to the query.
-The {\em derived SLA}  influences the choice of (data) services that will actually be used for building the result;
-\item Computing service compositions that rewrite the initial query and that can be used for  building query results.
-The \textit{agreed SLA} exported by the chosen services is added as  conditions in  each re-written query expression.
-Rewritten queries expressed as service composition can fully or partially comply with the \textit{derived SLA}.
-An \textit{integration SLA} is  computed for guiding  negotiation (in the case of partial compliance)  and the implementation of the final integration;
-\item   Managing the integration process according to the \textit{integration SLA}.
-\end{enumerate}
-
-%-----------------------------------------------------------------
-\section{Computing a derived SLA}
-\label{sec:derivedSla}
-%-----------------------------------------------------------------
+%%-----------------------------------------------------------------
+%\section{Computing a derived SLA}
+%\label{sec:derivedSla}
+%%-----------------------------------------------------------------
 
@@
 %The resulting derivedSLA will be used in the query rewriting step described in the next section.
-
-%-----------------------------------------------------------------
-\section{Query Rewriting}
-\label{sec:queryRew}
-%-----------------------------------------------------------------
-
-Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
-%Query rewriting is guided by the schema of  abstract and concrete databases.
-%The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
-The query rewriting problem can be generalized to the case of services.
-In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
-Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
-In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
-
-The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
-Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
-%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
-%In the LAV approach, 
-The rewriting process is guided by the specification of both the query to be rewritten and the available services.
-%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
-%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
-
-We propose an approach that consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-%The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.  
-The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
-
-%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the MOOC scenario, where people can participate on a content trading pool.
-We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
-The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
-These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.
-
-When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
-Depending on the location of the consumer and producers, different conditions and constraints may apply.
-Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.
-
-In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
-The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.
-
-In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
-The specification of each available service is also considered.
-%~\hfill\openbox
-%\end{example}
-
-%Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-%Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
-
-The {\em agreed SLA} is included and merged with the SLA conditions obtained by the rewriting process.
-Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
-
-In the case of our query example the following composition can be used for answering it:
-
-\begin{footnotesize}
-\sf
-\begin{tabbing}
- -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
- \>  myLoc = loc(myIPaddress), \\
- \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
- \>  query total cost + cost $\leq$ \$1,\\
- \>  availability $\geq$ 90$\%$, \\
- \>  freshness = any, \\
- \>  provenance = ``expert'', \\
- \>  duration = 7 days, \\
- \>  I/0 volume/month $\leq$ 8GB, \\
- \>  reputation level $\geq \lambda$ (the threshold) \\
- \>  storageSpace $\leq$ 1GB, \\
- \>  engage(``E.Dickinson'', size, myCreditCard).
- \end{tabbing} 
-\end{footnotesize}
-
-Our approach  generates a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the {\em derived SLA} are verified. 
- Yet, the current version of the algorithm should be modified to take into account the different SLAs.
-
-%-----------------------------------------------------------------
-\section{Deriving an Integration SLA: first approach}
-\label{sec:queryProcessOpt}
-%-----------------------------------------------------------------
- Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of the clouds involved.
-This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be used in a query evaluation process.
-It is thus important to optimize the use of these resources.
-
-The optimization of this process can occur at two levels: first at the level of the {\em agreed SLA} exported by services.
-Indeed, queries requesting the same service compositions will have clauses that are  conditions of use of the infrastructure (i.e., not storing the data produced by a service).
-Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it for other queries.
-Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
-Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
-Storing or not such SLAs  depends on the cloud subscription of the user that issued the query (data access, intermediate storage capacity, cost of storage, etc.).
-
-Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account as integration constraints.
-In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process.
-Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself.
-This leads to the build of the \textit{integration SLA}.
-
-%As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
-In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results.
-These computations are used dynamically for instantiating free variables in the derived SLA and thus determine whether the contract is respected by the execution of a query.
-Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.
-%

### 2015-05-01 Workshop2015/camera-ready/derivingSLA.tex
explanations about rewritings

--- 2015-04-30 Workshop2015/camera-ready/incremental.tex
@@
-To answer the needs expressed above, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
-%starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch}). In this section, we present  step-by-step data integration process with the implied  SLA categories.
-
-In our context, data are provided by services deployed on different clouds.
-In the example of the MOOC system presented above, several producers will supply equivalent content for a given period of time.
-They    will be chosen with respect to the  preferences expressed by a consumer.
-
-Consumers will express queries  expressed as  Datalog-like programs or  SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, the following query $Q_1$ ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
-
-The abstract Inter-Cloud Layer (ICL) delivers the results to the  query.
-The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query.
-These descriptions are stored in a service description registry (SCS).
-
-Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
-Hubs  store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these providers respectively by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs  have the same interface as individual service providers.
-We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements associated to the query.
-
-%shows the general architecture of an SLA guided data integration system. 
-%It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
-
-%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following lines describe how this query is evaluated according to our approach.
-
-\begin{figure*}
-\center{
-\includegraphics[width=0.75\textwidth]{workflow.pdf}
-\caption{SLA guided  data integration workflow.\label{fig:arch}}}
-\end{figure*}
-
-%In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
-%Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
-cost, inscription, or exchange unit), and the time window in which they can produce contents.
-%Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
-%An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
-
-Each deployed service exports an \textit{agreed SLA} that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data, as defined below:
-
-%NOTE: Agreed SLA are client-provider slas... --MARTIN
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, data access control, certified reputation level, location, duration$\rangle$. 
- \end{trivlist}
-
-Some of these measures ({cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
-In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
-It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).
-Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment.
-It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
-An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-
-In our scenario, examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
-The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
-The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
-
-As aforementioned, an a-priori SLA enforcement mechanism is mandatory to assess data integration feasibility.
-To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ...
-e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which export  an API, composed of the following set of methods:
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), 
-%QoS preferences$_\mathit{user}$, -- These should be in the query... not in the concrete services specification.
-agreedSLA$_i$.
-
-\item[~-~]engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
-\end{trivlist}
-
-%Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
-The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
-In other words, it  returns the cost of the data, as well as its  size and location.
-The second method is used to engage to a data service (in our example a content data service) and will be used  if the service is retained for a composition to answer the query.
-
-%The user will ask for a given derived SLA to which the provider may agree.
-
-The ICL  obtains the set of potential services that satisfy both user preferences and   \textit{agreed SLAs} associated to services. 
-For instance, the query $Q_1$ has two parts: the one that corresponds to the content required by the user  that will be solved by combining data services and the \textit{user preferences}, given by {QoS preferences}$_\mathit{user}$:
-\begin{trivlist}\sf\footnotesize
-\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost, freshness, provenance, location, duration, privacy-preserving$\rangle$. 
-\end{trivlist}
-
-Let us suppose that for $Q_1$  the user is ready to pay a total cost of maximum  \$1; she requests that content providers be certified as experts (provenance) even if their data are not fresh; she requires to receive content  during  one week.
-Besides, she wishes to keep the content exchange private and she wants to order services by reputation.
-The maximum total cost will condition also the kind of privacy preserving algorithms that will be applied.
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~QoS preferences$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
-\end{trivlist}
-
-Cloud providers also define their SLA contracts that specify the cost per request ({cost/request}), the volume of data that can be exchanged per month ({I/0 volume/month}), the cost of transferring data or applications within the same data center or across other data centers ({datatransferCost/region}), the storage space ({storageSpace}).
-For example, some cloud providers let the customer  choose the geographical zone to install PaaS services and deploy applications (e.g.
-zone 1 is Europe).
-If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.
-
-\begin{trivlist}\sf\footnotesize
- \item[~-~cloudSLA:]  $\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$.
- \end{trivlist}
-
-Illustration inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: 
- \begin{trivlist}\sf\footnotesize
-\item[~-~cloudSLA:]  $\langle$0,05 cents per call, 8 GB I/0 volume/month, free, 1 GB storage$\rangle$. 
-\end{trivlist}
-
-%A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
-
-The next step supervised by the ICL consists in elaborating a set of potential composition specifications via a query rewriting process.
-Given the user query, specified as a set of abstract operations and the available services, specified in the same way, we use a Local-as-View approach~\cite{CostaAMR13} to obtain a combination of services that match the query specification.
-The algorithm in~\cite{CostaAMR13} is being modified to deal with agreedSLA and QoS user preferences.
-
-In this paper, we are interested in the process of rewriting queries  considering QoS user preferences and SLAs.
-This process includes the following phases: 
-\begin{enumerate}
-\item  User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} are  used to produce a \textit{derived SLA} to be associated to the query.
-The {\em derived SLA}  influences the choice of (data) services that will actually be used for building the result;
-\item Computing service compositions that rewrite the initial query and that can be used for  building query results.
-The \textit{agreed SLA} exported by the chosen services is added as  conditions in  each re-written query expression.
-Rewritten queries expressed as service composition can fully or partially comply with the \textit{derived SLA}.
-An \textit{integration SLA} is  computed for guiding  negotiation (in the case of partial compliance)  and the implementation of the final integration;
-\item   Managing the integration process according to the \textit{integration SLA}.
-\end{enumerate}
-
 %-----------------------------------------------------------------
-\section{Computing a derived SLA}
-\label{sec:derivedSla}
-%-----------------------------------------------------------------
-
-The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedS LAs of potential composable services.
-This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and QoS preferences attributes.
-
-%A query has associated preferences  expressed as macroscopic constraints (i.e.
-user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode.
-These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
-
-%As said before, we assume that services export their \textit{agreed SLAs} that define measures that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
-A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location, duration of the engagement, privacy-preserving status.
-Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-
-The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures that can come from the evaluation of measures expressed in the cloud subscription of the user.
-The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.
-
-In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
-These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
-\begin{trivlist}\sf\footnotesize
- \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1.
- \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
- \item[~-~freshness:] non.
- \item[~-~provenance:] all services involved must be $expert$.
- \item[~-~duration:] 7 days.
- \item[~-~I/0 volume/month:] 8GB.
- \item[~-~reputation level :] $\geq$ threshold.
- \item[~-~storageSpace:] 1GB.
- \end{trivlist}
-
-Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by {\em agreed SLAs} and coarse grained measures used in user preferences statements.
-It specifies also how to compute coarse grained measures with fine grained ones. 
-For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The {\em derived SLA} can be seen as a set of inequations that have to be solved during the execution of a service composition.
-Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
-This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}.
-In order to address this problem we introduce the notion of  {\em integration SLA}.
-%and thus the need for an adaptive setting.
-%Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
-This negotiation can be expensive and may not scale well.
-
-%Given a query and its preferences statement, the system  finds  service compositions that produce results meeting the required constraints, as discussed in the following section.
-%The resulting derivedSLA will be used in the query rewriting step described in the next section.
-
-%-----------------------------------------------------------------
-\section{Query Rewriting}
-\label{sec:queryRew}
-%-----------------------------------------------------------------
-
-Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
-%Query rewriting is guided by the schema of  abstract and concrete databases.
-%The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
-The query rewriting problem can be generalized to the case of services.
-In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
-Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
-In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
-
-The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
-Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
-%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
-%In the LAV approach, 
-The rewriting process is guided by the specification of both the query to be rewritten and the available services.
-%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
-%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
-
-We propose an approach that consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-%The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.  
-The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
-
-%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the MOOC scenario, where people can participate on a content trading pool.
-We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
-The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
-These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.
-
-When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
-Depending on the location of the consumer and producers, different conditions and constraints may apply.
-Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.
-
-In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
-The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.
-
-In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
-The specification of each available service is also considered.
-%~\hfill\openbox
-%\end{example}
-
-%Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-%Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
-
-The {\em agreed SLA} is included and merged with the SLA conditions obtained by the rewriting process.
-Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
-
-In the case of our query example the following composition can be used for answering it:
-
-\begin{footnotesize}
-\sf
-\begin{tabbing}
- -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
- \>  myLoc = loc(myIPaddress), \\
- \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
- \>  query total cost + cost $\leq$ \$1,\\
- \>  availability $\geq$ 90$\%$, \\
- \>  freshness = any, \\
- \>  provenance = ``expert'', \\
- \>  duration = 7 days, \\
- \>  I/0 volume/month $\leq$ 8GB, \\
- \>  reputation level $\geq \lambda$ (the threshold) \\
- \>  storageSpace $\leq$ 1GB, \\
- \>  engage(``E.Dickinson'', size, myCreditCard).
- \end{tabbing} 
-\end{footnotesize}
-
-Our approach  generates a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the {\em derived SLA} are verified. 
- Yet, the current version of the algorithm should be modified to take into account the different SLAs.
-
-%-----------------------------------------------------------------
-\section{Deriving an Integration SLA: first approach}
-\label{sec:queryProcessOpt}
+%\section{Deriving an Integration SLA: first approach}
+%\label{sec:queryProcessOpt}
 %-----------------------------------------------------------------

### 2015-05-01 Workshop2015/camera-ready/incremental.tex
explanations about rewritings

@@
 \end{enumerate}
-
-%-----------------------------------------------------------------
-\section{Computing a derived SLA}
-\label{sec:derivedSla}
-%-----------------------------------------------------------------
-
-The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedS LAs of potential composable services.
-This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and QoS preferences attributes.
-
-%A query has associated preferences  expressed as macroscopic constraints (i.e.
-user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode.
-These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
-
-%As said before, we assume that services export their \textit{agreed SLAs} that define measures that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
-A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location, duration of the engagement, privacy-preserving status.
-Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-
-The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures that can come from the evaluation of measures expressed in the cloud subscription of the user.
-The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.
-
-In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
-These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
-\begin{trivlist}\sf\footnotesize
- \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1.
- \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
- \item[~-~freshness:] non.
- \item[~-~provenance:] all services involved must be $expert$.
- \item[~-~duration:] 7 days.
- \item[~-~I/0 volume/month:] 8GB.
- \item[~-~reputation level :] $\geq$ threshold.
- \item[~-~storageSpace:] 1GB.
- \end{trivlist}
-
-Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by {\em agreed SLAs} and coarse grained measures used in user preferences statements.
-It specifies also how to compute coarse grained measures with fine grained ones. 
-For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The {\em derived SLA} can be seen as a set of inequations that have to be solved during the execution of a service composition.
-Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
-This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}.
-In order to address this problem we introduce the notion of  {\em integration SLA}.
-%and thus the need for an adaptive setting.
-%Negotiation of implied SLAs depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
-This negotiation can be expensive and may not scale well.
-
-%Given a query and its preferences statement, the system  finds  service compositions that produce results meeting the required constraints, as discussed in the following section.
-%The resulting derivedSLA will be used in the query rewriting step described in the next section.
-
-%-----------------------------------------------------------------
-\section{Query Rewriting}
-\label{sec:queryRew}
-%-----------------------------------------------------------------
-
-Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
-%Query rewriting is guided by the schema of  abstract and concrete databases.
-%The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
-The query rewriting problem can be generalized to the case of services.
-In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
-Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
-In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
-
-The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
-Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
-%In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
-%In the LAV approach, 
-The rewriting process is guided by the specification of both the query to be rewritten and the available services.
-%The specification of the composition to be produced as well as the specification of each available service are used in the case of general services.
-%These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
-
-We propose an approach that consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-%The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.  
-The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
-
-%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the MOOC scenario, where people can participate on a content trading pool.
-We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
-The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
-These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.
-
-When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
-Depending on the location of the consumer and producers, different conditions and constraints may apply.
-Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.
-
-In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
-The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.
-
-In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
-The specification of each available service is also considered.
-%~\hfill\openbox
-%\end{example}
-
-%Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-%Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
-
-The {\em agreed SLA} is included and merged with the SLA conditions obtained by the rewriting process.
-Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
-
-In the case of our query example the following composition can be used for answering it:
-
-\begin{footnotesize}
-\sf
-\begin{tabbing}
- -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
- \>  myLoc = loc(myIPaddress), \\
- \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
- \>  query total cost + cost $\leq$ \$1,\\
- \>  availability $\geq$ 90$\%$, \\
- \>  freshness = any, \\
- \>  provenance = ``expert'', \\
- \>  duration = 7 days, \\
- \>  I/0 volume/month $\leq$ 8GB, \\
- \>  reputation level $\geq \lambda$ (the threshold) \\
- \>  storageSpace $\leq$ 1GB, \\
- \>  engage(``E.Dickinson'', size, myCreditCard).
- \end{tabbing} 
-\end{footnotesize}
-
-Our approach  generates a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the {\em derived SLA} are verified. 
- Yet, the current version of the algorithm should be modified to take into account the different SLAs.
-
-%-----------------------------------------------------------------
-\section{Deriving an Integration SLA: first approach}
-\label{sec:queryProcessOpt}
-%-----------------------------------------------------------------
- Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of the clouds involved.
-This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be used in a query evaluation process.
-It is thus important to optimize the use of these resources.
-
-The optimization of this process can occur at two levels: first at the level of the {\em agreed SLA} exported by services.
-Indeed, queries requesting the same service compositions will have clauses that are  conditions of use of the infrastructure (i.e., not storing the data produced by a service).
-Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it for other queries.
-Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
-Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
-Storing or not such SLAs  depends on the cloud subscription of the user that issued the query (data access, intermediate storage capacity, cost of storage, etc.).
-
-Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account as integration constraints.
-In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process.
-Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself.
-This leads to the build of the \textit{integration SLA}.
-
-%As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
-In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results.
-These computations are used dynamically for instantiating free variables in the derived SLA and thus determine whether the contract is respected by the execution of a query.
-Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.
-%

### 2015-05-01 Workshop2015/camera-ready/queryRewriting.tex
explanations about rewritings

--- 2015-04-02 Workshop2015/current version/incremental.tex
@@
-To answer the needs expressed above, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
-%starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch} )
-%shows the general architecture of an SLA guided data integration system. 
-%It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
-
-%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following lines describe how this query is evaluated according to our approach.
-
-\begin{figure*}
-\center{
-\includegraphics[width=0.75\textwidth]{workflow.pdf}
-\caption{Phases of an SLA guided  data integration workflow.\label{fig:arch}}}
-\end{figure*}
-
-%In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
-%Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
-cost, inscription, or exchange unit), and the time window in which they can produce contents.
-%Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
-%An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
-
-Services are deployed in different cloud providers and each service exports an agreed SLA that specifies the economic cost per call, the maximum number of calls that can be done per day, the availability of the service, the average response time when a method is called, the reliability, the privacy of the produced data (whether they can be stored or not), the precision, freshness and provenance of the produced data.
-
-%NOTE: Agreed SLA are client-provider slas... --MARTIN
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~agreedSLA$_i$:] $\langle$cost, availability, freshness, provenance, data access control, certified reputation level, location, duration$\rangle$. 
- \end{trivlist}
-
-Some of these measures ({\sf cost/call, maxCall/day}) are static and explicitly specified by the service provider. 
-In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
-It is the case for service reputation that will condition the way personal user data will be anonymized (Constraint1).
-Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment.
-It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the clouds hosting different data services.
-
-According to our approach, content producers are modeled as data services with associated \textit{agreed SLAs}. 
-In our example of MOOC system presented above, we assume that several producers will supply equivalent content for a given period of time  that will be chosen with respect to the  preferences expressed by a consumer.
-Assume that there are four content providers on English poetry that can be queried individually and two hubs that collect information from other sources like social network groups and hash tags.
-Hubs will store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these services by {\sf e$_1$, \dots, e$_4$} and {\sf h$_1$} and {\sf h$_2$}. We suppose that hubs will have the same interface as individual service providers.
-We also suppose the existence of two free location services exporting the following interface: {\sf loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries.
-
-In our example, non-functional characteristics of the content provision services ({\sf e$_1$, ... e$_4$}) are calculated by services that enforce SLAs  as follows:
-\begin{trivlist}\sf\footnotesize
-\item[~-~e$_i$:]estim-cost$_i$(contents, req\_size, cost, prov\_size, loc), QoS preferences$_\mathit{user}$.
-
-                engage$_i$(contents, req\_size, payment), agreedSLA$_i$.
-\end{trivlist}
-
-\color{red}
-
-The first operation permits the user to ask for the budget of a given course (content) and a required minimmum size.
-This operation will return the cost of the data, as well as its actual size and location.
-{QoS preferences}$_\mathit{user}$ is the user's proposal to the contents provider. 
-This SLA will become the {\sf agreedSLA}$_i$, in case of availability of the contents. 
-We suppose that availability is characterized by a non-zero value of size of the provided data ({\sf prov\_size}).
-The second operation is used to engage in a course. 
-The agreed SLAs are those containing the information described above in this example.
-%The user will ask for a given derived SLA to which the provider may agree.
-
-Cloud providers also define their SLA contracts that specify the cost per request ({\sf cost/request}), the volume of data that can be exchanged per month ({\sf I/0 volume/month}), the cost of transferring data or applications within the same data center or between data centers ({\sf datatransferCost/region}), the storage space ({\sf storageSpace}).
-For example some cloud providers enable the customer to choose the zone to install PaaS services and deploy applications (e.g.
-zone 1 is Europe).
-If the customer wishes to deploy services in zone 1 but store data in zone 2 the transfer cost will change.
-
-\begin{trivlist}\sf\footnotesize
- \item[~-~cloudSLA:]  $\langle$cost/request, I/0 volume/month, datatransferCost/region, storageSpace$\rangle$.
- \end{trivlist}
-
-%A content request is expressed as a query that specifies contents about a given topic with QoS preferences, independently of the possible providers.
-
-Queries may be expressed as Datalog-like programs or an SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, let us have the query ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar}''.
-This query has two parts: the one that corresponds to the content that will be solved by combining data services and the user preferences.
-For this query the user is ready to pay a maximum of \$1 as total cost; she requests that content providers be certified as experts (provenance) and that her privacy be saved by adapting the anonymity process with regard to services reputation.
-The maximum total cost will condition also which kind of privacy preserving algorithms to apply.
-
-The user preferences statement would include their cloud provider contract and quality preferences:
-\begin{trivlist}\sf\footnotesize
-\item[~-~cloudSLA:]  $\langle$0,05 cents per call, 8 GB I/0 volume/month, free, 1 GB storage$\rangle$. 
-\end{trivlist}
-
-We consider a simplified cloud SLA contract inspired in the lowest contract provided by Azure\footnote{Azure is a trademark of Microsoft Corporation.}: {\sf cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  01~GB of storage}.
-
-The user is ready to pay a maximum of {\sf \$1 as total query cost}; she requests that only {\sf certified} content providers are listed (provenance); even if their data are not fresh; she requires a contract duration of one week.
-
-\begin{trivlist}\sf\footnotesize
-\item[~-~SLA$_\mathit{user}$: ] $\langle$cost $\leq$ \$1, availability, freshness = ``any'', provenance = ``certified'', location = ``close'', duration = 7 days, privacy-preserving=``reputation-based''$\rangle$.
-\end{trivlist}
-
-As usual, SLAs will be represented as conditions over variables that will be used in the query.
-In this context, the compliance to the SLAs will drive the query rewriting process.
-
-Given a requirement expressing a query and quality of service preferences: cost, provenance, trust requirement, execution time, data confidentiality needs, \dots, the data integration process for computing a result is done as follows: (i) User preferences (including cloud SLAs according to user subscriptions) and agreed SLAs will be used to produce a derived SLA to be associated to the query.
-These derived SLA will influence the choice of (data) services that will actually be used for building the result; (ii) Query rewriting for computing service compositions that can be used for  building query results.
-The agreed SLA proposed by the chosen services is added as  conditions in  each re-written   query expression; (iii) Managing the integration process particularly storing partial results (including in  which location data is stored), delivering data (applying security control during integration) and launching and re-launching queries.
-Intermediate results  are stored as knowledge in order to reduce the overhead of the query evaluation process.
-
-\color{black}
 %-----------------------------------------------------------------
-\section{Derived SLA}
-\label{sec:slaModel}
+%\section{Query Rewriting}
+%\label{sec:queryRew}
 %-----------------------------------------------------------------
 
-The key and original aspect of   our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLAs.
-This  leads to a {\em derived SLA} that guides the evaluation of a query.
-
-A query has associated preferences  expressed as macroscopic constraints (i.e.
-user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode.
-These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
-
-As said before, we assume that services export SLAs (i.e., agreed SLAs) that define measures   that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
-A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location, duration of the engagement, privacy-preserving status.
-Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-
-Examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
-The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
-The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
-
-Given agreed SLAs and a user preferences statement the challenge is to compute a  {\em derived SLA} that  maps SLA measures and preferences attributes.  
-The derived SLA is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures. 
-The derived SLA  will guide the way the query will be evaluated, and the way results will be computed and delivered.
-
-In the example, some of the user preferences statement measures are used for defining a derived SLA that, as said in previous section, will guide the evaluation of the query. 
-These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract.
-\begin{trivlist}\sf\footnotesize
- \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1.
- \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
- \item[~-~freshness:] non.
- \item[~-~provenance:] all services involved must be $expert$.
- \item[~-~duration:] 7 days.
- \item[~-~I/0 volume/month:] 8GB.
- \item[~-~reputation level :] $\geq$ threshold.
- \item[~-~storageSpace:] 1GB.
- \end{trivlist}
-
-Therefore, we propose a classification of SLA measures that represents the combination of fine grained measures used by agreed SLAs and coarse grained measures used in user preferences statements. 
-It specifies also how to compute coarse grained measures with fine grained ones. 
-For example, data precision will be computed as a function of availability, freshness and provenance exported by data services.
-The derived SLA can be seen as a set of inequations that have to be solved during the execution of a service composition.
-Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
-We will discuss this issue in the next sections.
-
-This step may lead either to the rejection of integration in case of total incompatibility, or to a negotiation between SLA which will lead us to the proposal for a negotiated SLA integration and thus the need for an adaptive setting.
-Negotiation of this type of SLA depends strongly on the request sent and the services deployed at the arrival time of the application on the involved  clouds (i.e clouds holding services that satisfies user requests and that are candidate to service composition to answer the query).
-This negotiation can be expensive and may not scale well.
-
-Given a query and its preferences statement, the system  finds  service compositions that produce results   meeting the required constraints, as discussed in the following section.
-
-%-----------------------------------------------------------------
-\section{Query Rewriting}
-\label{sec:queryRew}
-%-----------------------------------------------------------------
-
-\color{red}
-One point remain very crucial to fix: once the multi-cloud layer generate a list of derived SLA corresponding to Agreed-SLA of services that could match a part of the query, What should happen?
-With whom rewritten query using user preferences is matched with SLA and which one (not clear in the paper.
-This point should be discussed quickly.
-The workflow of SLA between the abstract layer and cloud is not so clearly described.
-
-\color{black}
-Query rewriting is a well-known problem in the database domain.
-The problem consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
+Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
 %Query rewriting is guided by the schema of  abstract and concrete databases.
-%The answers to the lower level queries are combined in order to obtain the result to be returned to the user.
+The answers to the lower level queries are combined in order to obtain the result for the higher-level query.
 The query rewriting problem can be generalized to the case of services.
-In this case, the query to be rewritten is seen as an abstract service composition, to be expressed in terms of concrete services.
-Query rewriting techniques have been adapted to the context of service composition~\cite{BBM10,ZLC11,CostaAMR13}. 
-In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
-
+In this case, the query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
+Query rewriting techniques have been adapted to the context of data providing services~\cite{BBM10,ZLC11} as well as for general service compositions~\cite{CostaAMR13}. 
 The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
@@
 %In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
+
+In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
+The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
 %In the LAV approach, 
@@
 %These specifications may detail both the functional and non-functional behaviour of each service, including SLA.
-
-We propose an approach that consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-%The solutions proposed are ranked and may be coded into concrete workflows as shown in the following section.  
+The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
+The solutions proposed are ranked and may be coded into concrete workflows as shown in the following sections.  
 The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
 
-%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
-Let us consider the MOOC scenario, where people can participate on an content trading pool.
+\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
+Let us consider the MOOC scenario, where people can participate on a content trading pool.
 We suppose that this hypothetical MOOC has a large number of participants that sell their content  to  consumers. 
-The MOOC has four information hubs, located in four different geographic locations, connected to other content providers.
-Content providers may be  contacted directly, through the services of three different cloud providers.
-Each cloud provider exports its own interfaces.
-SLAs are defined for each individual content provider server and  each hub(agreed SLA)  , and also for each cloud provider (traditional SLA contracts).
+The MOOC has four information hubs described by their {\em agreed SLA}s, located in four different geographic locations, connected to other content providers.
+These later may be  contacted directly, through the services of three different cloud providers that expose their {\em Cloud SLA}.
 
-When an on-line consumer searches servers to buy/retrieve content, a composed web service is generated, in order to fetch each individual or hub service and to start  content retrieval procedures.
+When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
 Depending on the location of the consumer and producers, different conditions and constraints may apply.
 Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should also been expressed in the user preferences and SLAs.
+These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.
 
-In this context, the user  expresses a content order, her location and payment information. A composite web service is  generated to fulfill the order.
-The generated service composition should consider the nearest providers, in accordance to the agreed SLA.
+In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
+The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.
 
-In order to produce a personalized service composition for each user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition (which may be produced by the user's browser, including context information).
-The specification of each available service is also considered (this specification should be given by the service provider).
+In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
+The specification of each available service is also considered.
 %~\hfill\openbox
-%\end{example}
+\end{example}
 
-Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
-Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
+It is worth to notice that the algorithm in~\cite{CostaAMR13} shows an exponential behavior, since it produces all combinations of concrete services that satisfy the abstract specification.
+In order to solve this problem, we propose to use the \textit{agreed SLA} and user preferences to guide the choice of concrete services, to allow that the most preferred ones are combined first.
+This will allow to produce the top \textit{k} rewritings first (in accordance to the user preferences), thus avoiding the cost of producing all the solutions.
+%Given a set of services that can possibly be composed and the derived SLA, a service composition must be produced.
+%Some of the inequations of the derived SLA should be included in the service compositions that answers the query.
+
+The {\em agreed SLA} is included and merged with other SLA conditions that may be obtained by the rewriting process.
+Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
+
 In the case of our query example the following composition can be used for answering it:
@@
 
-Our approach would generate a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the derived SLA are verified. 
- Yet, the algorithm should be modified to take into account the different SLAs. The next example illustrates one of the limits of the automatic composition algorithm.
-
-\color{red}
-\begin{example}[Incremental queries]\label{Ex:rew2}
-Let us return to the content  trade system of the MOOC example.
- Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
-In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
-Let us suppose that, in order to minimize the  communications between servers, the lists need to be produced incrementally.
-In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
-The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.
-
-To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
-~\hfill\openbox
-\end{example}
-
-\color{black}
-
-%-----------------------------------------------------------------
-%\section{Dealing with the resources consumed by the evaluation process}
-%\label{sec:queryProcessOpt}
-%-----------------------------------------------------------------
- %Our data provision and integration approach relies on data services deployed on one or different clouds providers and it is delivered as a distributed DaaS on top of the clouds involved.
-This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be invested in a query evaluation process.
-It is thus important to optimize the use of these resources.
-
- %We believe that the optimization of this process can occur at two levels: first at the level of agreed SLA exported by services.
-Indeed, queries requesting the same services compositions will have clauses in their SLAs that are more conditions of use of the infrastructure (ie not storing the data produced by a service).
-Instead of recomputing the derived SLA every time, we propose to store it and reuse it for other queries.
-
-%Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
-Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
-Storing or not such SLAs will depend on the cloud subscription of the user the issued the query (data access, intermediate storage capacity , cost of storage , etc ...
-).
-
-%As discussed in previous sections, the derived SLA associated to service compositions can have free measures that can only be evaluated at run-time.
-In order to do so, we assume that there is a monitoring system observing and aggregating events for computing resources consumption, execution and time cost, volumes of data transferred when services deliver results.
-These computations are used dynamically for instantiating free variables in the derived SLA and thus determine whether the contract is respected by the execution of a query.
-Since this is monitored dynamically, the evaluation of the query can be adapted if the SLA is not being respected anymore.
-
- %Furthermore, the way the integration will take place after the choice of the concrete service composition will require to enforce functional and non functional user and service preferences to take into account the integration constraints.
-In the example this has been illustrated by  the access control level constraints demanded by data services when they are implied in an integration process.
-Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration it self.
+Our approach  generates a number $k$ of service compositions, combining as much as possible the services available such that the constraints of the {\em derived SLA} are verified. 
+We are working on the modified version of the algorithm in~\cite{CostaAMR13} to take into account the different SLAs.

### 2015-05-04 Workshop2015/camera-ready/conclusions.tex
Camera-ready Nadia/Chirine

This paper introduces the challenge of integrating data from distributed data services deployed on different cloud providers guided by service level agreements (SLA) and user preferences statements. The data integration problem is stated as a continuous data provision problem that has an associated economic cost and that uses automatic learning techniques for ensuring different qualities of delivered data (fresh, precise, partial).

Current big data settings impose  to consider SLA and different data delivery models. We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-known solutions  adapted to these contexts. We are currently developing the strategies and algorithms sketched here applied to energy consumption applications and also to elections and political campaign data integration in order to guide decision making on campaign strategies.

The diversity of mentioned application domains highlights the difficulty regarding SLA manipulation. Indeed, cloud, service, and user SLAs could be expressed differently in term of clauses, formalism and content. The multi-cloud environment emphasizes these heterogeneities.

The main issue when launching an integration process is to obtain the most accurate answer meeting the best user preferences. One of the possibilities when studying the integration is to accept the integration process in an incremental  manner so that the query will continue to be evaluated till satisfying the set of QoS and non functional constraints expressed by the user. To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
Furthermore, the integration SLA generation step is outstanding study. In fact the integration SLA should indicate the negotiation result with the aim to reuse it in further integration.

% 
%\begin{example}[Incremental queries]\label{Ex:rew2}
%Let us return to the content  trade system of the MOOC example.
% Suppose that the user requires to retrieve a list of star providers  daily and weekly that can deliver ``\textit{5 Go}'' of expert content about Emily Dickinson poetry.
%In this case, each individual and hub database will be queried and the list will be produced by adding data obtained from them, until the 5Go  capacity is reached.
%Let us suppose that, in order to minimize the  communications between servers, the lists need to be produced incrementally.
%In this case, the composition produced by the service refinement may need to include an iteration (to aggregate partial results). 
%The data produced by the warehouse servers will be processed in batch and the process will end once the list reaches the desired capacity.
%
%
%~\hfill\openbox
%\end{example}
%
%\color{black}

### 2015-05-04 Workshop2015/camera-ready/derivingSLA.tex
Camera-ready Nadia/Chirine

@@
 
-Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account as integration constraints.
+Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account  integration constraints.
 In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process.
 Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself.
+Finally, query time execution will be stored  for further partial or similar queries.
 This leads to the build of the \textit{integration SLA}.

### 2015-05-04 Workshop2015/camera-ready/introduction.tex
explanations about rewritings
Camera-ready Nadia/Chirine

@@
 
- We have proposed such architecture in \cite{DBLP:conf/IEEEcloud/2014}.
-With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process.
-Then, this paper introduces a preliminary solution addressing SLA-guided data integration focussing particularly on security issues.
+We have proposed such architecture in \cite{BennaniGMV14}.
+With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process, taking into account SLA formalism and clauses -especially security concerns-  heterogeneities among clouds.
+Furthermore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing particularly on query rewriting addressing security issues.
 We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.

### 2015-05-05 Workshop2015/camera-ready/computingDerivSLA.tex
version à 6 pages

@@
 
-The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreedS LAs of potential composable services.
+The key and original aspect of  our proposed data integration and provision process is  defined as a vertical mapping of user QoS preferences and agreed SLA of potentially composable services. 
 This  leads to a {\em derived SLA} that guides the evaluation of a query and maps SLA measures and QoS preferences attributes.
@@
 \begin{trivlist}\sf\footnotesize
- \item[~-~query total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1.
- \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$}.
- \item[~-~freshness:] non.
- \item[~-~provenance:] all services involved must be $expert$.
- \item[~-~duration:] 7 days.
- \item[~-~I/0 volume/month:] 8GB.
- \item[~-~reputation level :] $\geq$ threshold.
+ \item[~-~ total cost:] $\sum_{i = 1\dots n}$ cost(s$_i$) + data transfer + encryption cost $\leq$ \$1;
+ \item[~-~availability:] {\em (of services involved)} $\geq$ {\sf 90$\%$};
+ ~-~freshness: non;
+ \item[~-~provenance:] all services involved must be $expert$;
+  ~-~duration: 7 days;
+ \item[~-~I/0 volume/month:] 8GB;
+  ~-~reputation level: $\geq$ threshold;
  \item[~-~storageSpace:] 1GB.

### 2015-05-05 Workshop2015/camera-ready/derivingSLA.tex
version à 6 pages

--- 2015-05-01 Workshop2015/camera-ready/derivingSLA.tex
@@
 %-----------------------------------------------------------------
- Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of the clouds involved.
-This DaaS  uses resources from a cloud and this use  is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources to be used in a query evaluation process.
+ Our data provision and integration approach relies on data services deployed on one or different cloud providers and it is delivered as a distributed DaaS on top of those clouds.  
+The use of resources from a cloud is  guided by an economic model (stated in a cloud subscription) that puts a threshold on the amount of resources used for query evaluation. 
 It is thus important to optimize the use of these resources.
@@
 The optimization of this process can occur at two levels: first at the level of the {\em agreed SLA} exported by services.  
-Indeed, queries requesting the same service compositions will have clauses that are  conditions of use of the infrastructure (i.e., not storing the data produced by a service).
-Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it for other queries.
+Indeed, queries requesting the same service compositions may have clauses that are conditions of use of the infrastructure (i.e., not storing the data produced by a service). 
+Instead of recomputing the {\em derived SLA} every time, we propose to store it and reuse it in future queries. 
 Second, pre-computed queries and partial results can be also stored in cache or in a persistent support.
-Rewriting results can be also stored and reduce execution and resources consumption time when evaluating similar queries.
-Storing or not such SLAs  depends on the cloud subscription of the user that issued the query (data access, intermediate storage capacity, cost of storage, etc.).
+%Rewriting results can be stored and reduce execution and resources consumption time when evaluating similar queries.
+Storing or not these results depends on the cloud subscription SLA of the user (data access, intermediate storage capacity, storage cost, etc.).
 
-Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account as integration constraints.
+%Furthermore, the execution of the concrete service composition  must enforce functional and non functional preferences taken into account  integration constraints.
 In the example this is illustrated by  the access control level constraints required by data services when they are involved in an integration process.
-Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself.
-This leads to the build of the \textit{integration SLA}.
+%Another important point is to consider the existing inter-cloud contracts as described in \cite{} to decide how to implement the integration itself.
+Finally, query time execution will be stored  for further partial or similar queries.
+%This leads to the build of the \textit{integration SLA}.
 

### 2015-05-05 Workshop2015/camera-ready/incremental.tex
version à 6 pages

@@
-To answer the needs expressed above, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
-%starting from the processing of the query  to the delivery of the results.
-Figure~\ref{fig:arch}). In this section, we present  step-by-step data integration process with the implied  SLA categories.
+To answer this question, we propose an SLA guided, security-aware continuous data provision and integration approach performed within a multi-cloud service oriented environment  (see
+Figure~\ref{fig:arch}). 
+We present a step-by-step data integration process and the implied  SLA categories.
 
@@
 
-Consumers will express queries  expressed as  Datalog-like programs or  SQL-like expressions, including spatio-temporal attributes and preferences.
-For instance, the following query $Q_1$ ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and that are labelled as experts, where the total cost is not higher to 1 dollar, with using only services that preserve her anonymity}''.
+Consumers will specify queries as Datalog- or SQL-like programs including spatio-temporal attributes and preferences.
+For instance, the following query $Q_1$: ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and are labeled as experts, where the total cost is less than 1 dollar, using only services that preserve their anonymity}''.
 
-The abstract Inter-Cloud Layer (ICL) delivers the results to the  query.
-The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query.
-These descriptions are stored in a service description registry (SCS).
+The Abstract Inter-Cloud Layer (ICL) delivers the results to the  query. 
+The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query. These descriptions are stored in a service description registry.
 
@@
 Hubs  store content about given topics on  English poetry, available from particular producers (e.g., participants of a given course).
-We represent these providers respectively by { e$_1$, \dots, e$_4$} and {h$_1$} and {h$_2$}. We suppose that hubs  have the same interface as individual service providers.
-We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position expressed as a pair of coordinates.
-All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements associated to the query.
+We represent these providers respectively by { e$_1$ - e$_4$}, {h$_1$}, {h$_2$}. 
+We suppose that hubs  have the same interface as individual service providers.
+We also suppose the existence of two free location services exporting the following interface: {loc(IP) $\rightarrow$ $\langle$ X, Y$\rangle$}, meaning that given an IP address it returns a geographic position.
+All these services can potentially be combined for answering queries. Each combination will answer the query and fulfill in a specific degree the QoS requirements of the query.
 
@@
 \center{
-\includegraphics[width=0.75\textwidth]{workflow.pdf}
+\includegraphics[width=0.65\textwidth]{workflow.pdf}
 \caption{SLA guided  data integration workflow.\label{fig:arch}}}
@@
 It is the case for constraint 2 expressed above:   user data access credentials should be calculated according to the policies adopted by the clouds  hosting  data services.
-An \textit{agreed SLA} is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
+An \textit{agreed SLA} is given as an  XML document using the specification WSLA (Web service level agreement\footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
 
-In our scenario, examples of computed measures are the cost of retrieving the list of ``expert'' Emily Dickinson poems providers within a region with their cost. 
+In our scenario, an example of computed measure is the cost of retrieving ``expert'' Emily Dickinson poems providers within a region, with their cost. 
 The cost is determined by the  cost of the calls. 
-This request  includes the price of calling a service (e.g.,  between 0,25 - 0,50 euros depending on the data service), plus the price of data transmission according to the amount of transmitted MegaBytes through the network, the type of subscription of the user for using the network and also the cost of applying encryption algorithm if asked for.
+This request  includes the price of calling a service (e.g.,  between \$0,25 - 0,50, depending on the data service), plus the price of data transmission (amount of transmitted MB through the network), the type of subscription of the user for using the network and also the cost of applying encryption algorithms if required.
 The second computed measure is service reputation that is calculated according to the feedback obtained when application contacts the service.
 
-As aforementioned, an a-priori SLA enforcement mechanism is mandatory to assess data integration feasibility.
-To this end, non-functional characteristics of the content provision services ({i.e e$_1$, ...
-e$_4$}) are calculated by specific cloud services (SCS) that enforce SLAs  and which export  an API, composed of the following set of methods:
+As aforementioned, an \textit{a-priori} SLA enforcement mechanism is mandatory to assess data integration feasibility.
+To this end, non-functional characteristics of the content provision services ({i.e e$_1$-e$_4$}) are calculated by specific cloud services that enforce SLA and which should export  an API, composed of the following methods:
 
@@
 This process includes the following phases: 
-\begin{enumerate}
-\item  User preferences (including cloud SLAs according to user subscriptions) and \textit{agreed SLAs} are  used to produce a \textit{derived SLA} to be associated to the query.
-The {\em derived SLA}  influences the choice of (data) services that will actually be used for building the result;
-\item Computing service compositions that rewrite the initial query and that can be used for  building query results.
+\begin{trivlist}
+\item[~1)]  User preferences (including cloud SLA according to user subscriptions) and \textit{agreed SLA} are  used to produce a \textit{derived SLA} to be associated to the query. 
+{\em Derived SLA}  influences the choice of services that will be used to build the result; 
+\item[~2)] Computing service compositions that rewrite the initial query and that are used to  build query results. 
 The \textit{agreed SLA} exported by the chosen services is added as conditions in  each re-written query expression. 
@@
 An \textit{integration SLA} is  computed for guiding  negotiation (in the case of partial compliance)  and the implementation of the final integration;
-\item   Managing the integration process according to the \textit{integration SLA}.
-\end{enumerate}
+\item[~3)]   Integration process guided by the \textit{integration SLA}.
+\end{trivlist}

### 2015-05-05 Workshop2015/camera-ready/introduction.tex
version à 6 pages

@@
 \color{black}
-The advent of cloud computing has imposed a new   resource consuming model that focusses on
+The advent of cloud computing has imposed a new   resource consuming model that focuses on
  the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources.
@@
 How can this be done?
-The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a result for a given query.
+The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a given query.
 
-We have proposed such architecture in \cite{BennaniGMV14}.
-With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process, taking into account SLA formalism and clauses -especially security concerns-  heterogeneities among clouds.
+We have proposed such architecture in~\cite{BennaniGMV14}.
+With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process, taking into account SLA formalism and clauses -especially security concerns-  heterogeneity among clouds.
 Furthermore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing particularly on query rewriting addressing security issues.
@@
 
-Accordingly, the remainder of this paper is organized as follows.
+This paper is organized as follows.
 Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments.

### 2015-05-05 Workshop2015/camera-ready/queryRewriting.tex
version à 6 pages

@@
 
-Query rewriting is a well-known problem in the database domain that consists in transforming an abstract query into a set (or list) of lower-level queries that can be solved by  available databases.
+Query rewriting is a well-known problem for databases.
+It consists in transforming an abstract query into lower-level queries that can be answered by available databases.
 %Query rewriting is guided by the schema of  abstract and concrete databases.
-The answers to the lower level queries are combined in order to obtain the result for the higher-level query.
-The query rewriting problem can be generalized to the case of services.
-In this case, the query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
+The answers to the lower level queries are combined in order to obtain the result.
+The query rewriting problem can be generalized to the case of services:
+The query to be rewritten is seen as an \textit{abstract} service composition, to be expressed in terms of \textit{concrete} services.
 Query rewriting techniques have been adapted to the context of data providing services~\cite{BBM10,ZLC11} as well as for general service compositions~\cite{CostaAMR13}. 
-The case of more general services (\textit{i.e}, services that maintain and update information) is a generalization of the information-provision case.
-Unlike the simpler case, where only the service interfaces need to be considered, the general case requires considering the functional and non-functional aspects of the query and available services.
+The latter case (\textit{i.e}, services that maintain and update information) is a generalization of the data provision case.
+The general case requires considering the functional and non-functional aspects of the query and available services.
 %In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
-
-In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
-The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
+%In~\cite{CostaAMR13} the authors present an algorithm to automatically refine high-level specifications of service compositions into lower-level ones. 
+%The method is based on the MiniCon algorithm~\cite{PH01} for query rewriting.
 %In the LAV approach, 
@@
 The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-The solutions proposed are ranked and may be coded into concrete workflows as shown in the following sections.  
-The next example shows the main features of the approach proposed in~\cite{CostaAMR13} which is extended to the case of SLA-guided service-based data integration.
+The solutions proposed are ranked and may be coded into concrete workflows.
 
-\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
+The approach proposed in~\cite{CostaAMR13} which may be extended to the case of SLA-guided service-based data integration. 
+%
+%\begin{example}[Service Refinement by Rewriting]\label{Ex:rew1}
 Let us consider the MOOC scenario, where people can participate on a content trading pool.
@@
 
-When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed, in order to fetch each individual or hub service and to start  content retrieval procedures.
+When an on-line consumer searches servers to buy/retrieve content, a composed  service is computed.
+%, in order to fetch each individual or hub service and to start  content retrieval procedures.
 Depending on the location of the consumer and producers, different conditions and constraints may apply.
-Also  cloud providers  publish the conditions for using their services.
-These conditions and non-functional requirements (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}s.
-
-In this context, the user  expresses a content order, her location and payment information. A composite  service is  generated to fulfill the order.
+%Also  cloud providers  publish the conditions for using their services.
+These conditions (such as authentication or security requirements) should  be also expressed in the QoS user preferences and {\em agreed SLA}.
+In this context, the user  expresses a content order, her location and payment information. 
+A composite  service is  generated to fulfill the order.
 The generated service composition should consider the nearest providers, in accordance to the {\em derived SLA}.
 
-In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
+%In order to produce a personalized service composition for a user, the algorithm in~\cite{CostaAMR13} takes into account the specification of the composition.
 The specification of each available service is also considered.
-%~\hfill\openbox
-\end{example}
+%%~\hfill\openbox
+%\end{example}
 
@@
 Only those compositions that comply with the {\em derived SLA} will be presented as possible solutions to the user.
-
 In the case of our query example the following composition can be used for answering it:
@@
 \begin{tabbing}
- -~Q(myIPad\=dress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
+ -~Q\=(myIPaddress, ``E.Dickinson'', 1MB, ``expert'', \$1, myCreditCard) $\equiv$ \\
  \>  myLoc = loc(myIPaddress), \\
  \>  estim$\_$cost(``E.Dickinson'', 1MB, cost, size, theirLocation), \\
- \>  query total cost + cost $\leq$ \$1,\\
- \>  availability $\geq$ 90$\%$, \\
- \>  freshness = any, \\
- \>  provenance = ``expert'', \\
- \>  duration = 7 days, \\
- \>  I/0 volume/month $\leq$ 8GB, \\
- \>  reputation level $\geq \lambda$ (the threshold) \\
- \>  storageSpace $\leq$ 1GB, \\
+ \>  query total cost + cost $\leq$ \$1, 
+ \   availability $\geq$ 90$\%$, 
+ \  freshness = any, \\
+ \>  provenance = ``expert'', 
+ \   duration = 7 days, 
+ \   storageSpace $\leq$ 1GB, \\
+ \>  I/0 volume/month $\leq$ 8GB, 
+ \   reputation level $\geq \lambda$ (the threshold) \\
  \>  engage(``E.Dickinson'', size, myCreditCard).

### 2015-05-05 Workshop2015/camera-ready/relwork.tex
version à 6 pages

@@
-In the cloud, the   SLA's rely on two principles: (i)  negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii)  monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
+The use of cloud SLA rely on two principles: (i)  negotiation of conditions in which services will be provided and that are statically agreed between the parts and (ii)  monitoring of these conditions during the use of cloud resources in order to detect SLA contract violation.
 
@@
 %Indeed, 
-SLA's are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
+SLA are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
 From the user point of view, the interest is normally on \textit{service} delivery measures that are related with her QoS requirements like service availability, resilience, recovery time or cost.
-The challenge is to couple technical and service delivery measures expressed in SLA's in order to agree on the conditions in which they will be considered for executing tasks for a user.
+The challenge is to couple technical and service delivery measures expressed in SLA in order to agree on the conditions in which they will be considered for executing tasks for a user.
 Existing works use matching and negotiation techniques for addressing this challenge.
@@
 \cite{Dastjerdi:2012:DOA:2275356.2275360} describes a \textit{Semantic SLA} that can be understood by all parties including providers, consumers, and monitoring services.
-Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  \cite{Ortiz:2013:VPS:2486767.2486772}
-  proposes a set of templates to  cloud data services users, each specifying the query type that can be executed with some tread-off in time and corresponding cost.
+Their goal is, starting from a high level SLA, to measure and identify how to derive SLA measures  at different layers of the cloud.  
+\cite{Ortiz:2013:VPS:2486767.2486772} proposes a set of templates to cloud users, each specifying the query type that can be executed with their tread-off in time and cost.  
 The client  chooses among the proposed templates the one that best corresponds   to her requirements.
-\cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters.
-Cloud SLA parameters and application requirements are represented by two models using RDF.
+\cite{6141307} proposes a set of matching algorithms to identify compatible cloud providers for a given requirements specification by matching SLA parameters, represented in RDF.
 RDF definitions are then converted into graph representations.
-An Induced Propagation Graph is calculated using both models to establish a correspondence between them.
+An \textit{Induced Propagation Graph} is calculated from both models to establish correspondences.
 
@@
 
-Recent  works on SLA are devoted to extend  SLA specifications for including  security concerns. 
+Recent  works on SLA are devoted to extend  SLA specifications to include  security concerns. 
 \cite{6274042} propose an extension of the WSAgreement, initially developed by the GRAAP
@@
 terms (SDTs) and the service level objectives (SLOs) of the SLA. 
-This leads to an interoperable security expression that can be used by users for comparing security levels of different cloud  providers.
+This leads to an interoperable security expression that can be used by users for comparing security levels of cloud  providers. 
 Hale and Al.
 in \cite{6655684} extend their first work proposing an ontology representation of security concerns and connect security services expressed in SLA  to documents regulating security controls.
-\cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA Template starting from gathering then categorizing a set of security statements using a semantic tool. 
+\cite{LunaGarcia:2012:BCS:2381913.2381932} focuses on how to build a SEcSLA template starting from gathering then categorizing a set of security statements using a semantic tool. 
 The designed template is then used both to express user security requirements and cloud service provider security provision.
@@
  Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, maybe because measures concern data services and not data itself.
-Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources.
-Whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).
+Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources, whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).
 Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility. 

### 2015-05-06 Workshop2015/camera-ready/introduction.tex
Still some modifications coming

@@
  the \textit{technical and economic} conditions to be fulfilled in order to access potentially unlimited resources.
-Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, and filtering them considering their "structural" characteristics (data variety that implies different formats and data models) and  their quality, e.g., trust, freshness, provenance, partial or total consistency.
+Integrating and processing heterogeneous data collections, calls for efficient methods for correlating, associating, and filtering them considering their variety (i.e., different formats and data models) and   quality, e.g., trust, freshness, provenance, partial or total consistency.
 Existing data integration techniques have to be revisited considering weakly curated and modeled data sets.
-This can be done according to quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services and cloud providers that host  these collections and deliver resources for executing  associated processing and integration processes.
+This can be done according to (i) quality of service (QoS) requirements expressed by their consumers and Service Level Agreement (SLA) contracts exported by data services; (ii)  cloud providers that host  these collections and deliver resources for executing  data processing and integration processes.
 In fact,  the interest of SLA has been demonstrated  in data analysis but has not been yet widely considered for integrating data. 
@@
 To do so, several granularities of SLA must be considered: first, at the cloud level: the SLA ensured by providers regarding data; then at the service level, as unit for accessing and processing data, to be sure to fulfill  specific  needs; and finally at the integration level i.e the possibility to process, correlate and integrate big data collections distributed across different cloud storage supports, providing different quality properties for data (trust, privacy, reliability, etc).
-
-%To better understand our problem, let us consider an example from the domain of energy
-%management.
-We assume we are interested in queries like: \textit{Give a list of energy providers that can provision 1000 KW-h, in the next 10 seconds, that are close to my city, with a cost of 0,50 Euro/KW-h and that are labelled as green?} \\
-% The user demanded to apply a special encryption algorithm to sensitive data if data has to be transferred between providers or between physical sites during the integration process (Constraint1).
-Furthermore, the data providers could wish also that in case of a common use of their data within  an integration process, that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data (Constraint 2).
-We consider a simplified SLA cloud contract inspired in the cheapest contract provided by Azure: \textit{cost of \$0,05 cents per call,  8~GB of I/O volume/month, free data transfer cost within the same region,  1~GB of storage.}
-%The user is ready to pay a maximum of \textit{\$5 as total query cost}; she requests that only  \textit{green} energy providers should be  listed (provenance), with at least  \textit{85$\%$} of precision of provided data, even if they are not fresh; she requires an availability rate of at least 90$\%$ and a response time of  \textit{0,01 s}.
-She demands to contact only data providers with a threshold of trust .
 
@@
 
- %that this should be done assigning the less important privileges to the user w.r.t her credentials to access the different data
-
   From this scenario we identify a set of issues that have to be addressed.
@@
 How can this be done?
+
   The first step is to propose an architecture that integrates all services participating in a data integration process that copes QoS and SLA's of the services that participate in this process for computing a given query.
-
   We have proposed such architecture in~\cite{BennaniGMV14}.
-With this architecture it is necessary to revisit the specification of the integration phases in order to show how to include QoS and SLA and thereby proposing a new way of dealing with a data production and consumption process, taking into account SLA formalism and clauses -especially security concerns-  heterogeneity among clouds.
-Furthermore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing particularly on query rewriting addressing security issues.
+Based on this architecture it is necessary to revisit  the integration phases  specification to include QoS and SLA.
+The objective being to  propose a new way of dealing with a data production and consumption process, considering SLA formalism and clauses -especially security concerns-  and heterogeneity among clouds.
+Therefore, this paper introduces a preliminary solution addressing SLA-guided data integration focusing  on query rewriting addressing security issues.
 We assume that data services publish Agreed-SLA that describe their  static and dynamic QoS measures in specific registries.
 Thanks to an extended query rewriting process, a new kind of SLA is derived to match user preferences with low level agreed SLAs exported by services.
-The derived SLA allows to choose  services (w.r.t user demands) that can contribute for answering a query.
-Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking into account user requirements and inter-cloud contracts.
-%  Particularly, for queries that call several services deployed  on different clouds. 
-%  Among them first,Furthermore, for a non specialist user, she do not realize what is the level of ressources she need to apply the encryption level asked  for. 
-%  As data services are deployed in a multi-cloud context, there is a need to establish the rules on how integration can be made. 
-%  concerns the context in which data will be used among clouds when data services are deployed in a multi-cloud configuration.
-How can the specified services requirements be enforced?
-And finally, data integration in this context faces an heterogeneity problem at different levels but specially in the scenario we are interested in, in data deployment conditions, the SLA expression language, the level security is taken into account in SLA contract.
+The derived SLA allows to choose  services (w.r.t user requirements) that can contribute for answering a query.
+Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking according to user requirements and inter-cloud contracts.
 
@@
 Finally section  \ref{sec:conclusions} concludes the paper and discusses future work.
-%Section \ref{sec:useCase} presents a use case for illustrating the interest and use of our approach.

### 2015-05-06 Workshop2015/camera-ready/conclusions.tex
Final version reviewed to make sentences shorter

@@
 We believe that given the volume and the complexity of query evaluation that includes steps that imply greedy computations, it is important to combine and revisit well-known solutions  adapted to these contexts.
-We are currently developing the strategies and algorithms sketched here applied to energy consumption applications and also to elections and political campaign data integration in order to guide decision making on campaign strategies.
+We are  developing  strategies and algorithms overviewed in this paper and applying them to energy consumption applications and to elections and political campaign data integration to guide decision making on campaign strategies.
 

### 2015-05-06 Workshop2015/camera-ready/incremental.tex
Final version reviewed to make sentences shorter

@@
 In our context, data are provided by services deployed on different clouds. 
-In the example of the MOOC system presented above, several producers will supply equivalent content for a given period of time. 
+In the preivous   MOOC system example, several producers will supply equivalent content for a given period of time. 
 They will be chosen with respect to the  preferences expressed by a consumer.
 
-Consumers will specify queries as Datalog- or SQL-like programs including spatio-temporal attributes and preferences.
+Consumers  specify queries as Datalog- or SQL-like programs including spatio-temporal attributes and preferences.
 For instance, the following query $Q_1$: ``\textit{List of English poetry content providers that can provide commented Emily Dickinson poems that are close to my city and are labeled as experts, where the total cost is less than 1 dollar, using only services that preserve their anonymity}''.
@@
 
-%shows the general architecture of an SLA guided data integration system. 
-%It accesses data services which are data providers deployed in a cloud  that provide agreed SLA's. 
-%The whole process is monitored to determine whether a computed SLA is being honoured while a query is evaluated.
-
-%These descriptions are stored in a directory together with meta-data about the way queries are evaluated for producing results. 
-%The system uses this information  by query processing and monitoring modules for rewriting queries according to given quality of service (QoS) preferences expressed by a data consumer, for example a user.The following lines describe how this query is evaluated according to our approach.
-
 \begin{figure*}
@@
 \end{figure*}
-
-%In order to illustrate our approach, consider a massive open online course system (MOOC) that aims at being privacy respectful of the students participating in courses and produce and consume content according to the geographic area and expertise of participants.
-%Producers are characterized according to their location, the type and topic of the content that they can provide, the access conditions (e.g.
-cost, inscription, or exchange unit), and the time window in which they can produce contents.
-%Consumers are described by their location, their interests requirements during a certain interval of time, the maximum total cost they are ready to pay, or the resources they are ready to provide in order to get the service, and quality of service requirements such as availability and how critical it is to consume a given type of content.
-%An energy exchange market is established in order to continuously trade  content provision/consumption ensuring that all consumers will have the content they require at every moment.
 
@@
 %Given user expressed QoS preferences ({QoS preferences}$_\mathit{user}$) and {agreedSLA}$_i$, 
-The first method allows to obtain for each service $e_i$ the estimation of the budget (in our example, of a given course (content)) and a required minimum size.
-In other words, it  returns the cost of the data, as well as its  size and location.
+For each service $e_i$, the first method returns the cost of the data (in our example, the cost of a given course (content)), as well as its  size and location,  and a required minimum size.  
 The second method is used to engage to a data service (in our example a content data service) and will be used  if the service is retained for a composition to answer the query.
@@
 Besides, she wishes to keep the content exchange private and she wants to order services by reputation.
-The maximum total cost will condition also the kind of privacy preserving algorithms that will be applied.
+The maximum total cost will  also determine the kind of privacy preserving algorithms that will be applied.
 

### 2015-05-06 Workshop2015/camera-ready/queryRewriting.tex
Final version reviewed to make sentences shorter

@@
 
-Query rewriting is a well-known problem for databases.
-It consists in transforming an abstract query into lower-level queries that can be answered by available databases.
+Query rewriting 
+%is a well-known problem for databases. It
+ consists in transforming an abstract query into lower-level queries that can be answered by available databases.
 %Query rewriting is guided by the schema of  abstract and concrete databases.
@@
 The latter case (\textit{i.e}, services that maintain and update information) is a generalization of the data provision case.
-The general case requires considering the functional and non-functional aspects of the query and available services.
+`%The general case requires considering the functional and non-functional aspects of the query and available services.
 %In this context, the \textit{Local as View} (\textit{LAV}) methods of query rewriting~\cite{Levy2000} are suitable.
@@
 The approach consists in generating translations of an abstract query into \textit{several}  compositions over concrete  services. 
-The solutions proposed are ranked and may be coded into concrete workflows.
+The solutions proposed are ranked and may be coded into concrete workflows that will be executed in one or several clouds by a special engine.
 
-The approach proposed in~\cite{CostaAMR13} which may be extended to the case of SLA-guided service-based data integration. 
+The approach proposed in~\cite{CostaAMR13} is being extended to the case of SLA-guided service-based data integration. 
 %

### 2015-05-06 Workshop2015/camera-ready/relwork.tex
Final version reviewed to make sentences shorter

@@
 
-%The agreed conditions should be explicit and quantifiable.
-%They should be part of the contract between the client and the service provider.
-%Their quantifiable nature makes it possible for the conditions to appear as non-functional requirement to be imposed to each individual service.
-%SLA could concern all types of services on the cloud (IaaS, PaaS or SaaS).
-
-%SLA compliance may be ensured by construction or may be monitored during the execution of the service.
-%Monitoring SLAs is normally part of the infrastructure provided by the cloud.
-%Service monitoring may incur in extra processing costs.
-
-%SLA currently exploited in the cloud allows service providers and cloud clients to describe the amount of resources to be simultaneously used and also the conditions to use them.
-%This limit may apply both for the service provider and the client (in the case of service invocation).
-
-%Negotiating a SLA may be a difficult task.
-%Indeed, 
 SLA are normally expressed in terms of \textit{technical}, quantifiable measures, like the storage space size, the degree of virtualization, the number of requests for a given service. 
@@
 
- Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, maybe because measures concern data services and not data itself.
-Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources, whereas data integration in a multi-cloud context implies to express and enforce multiple granularity constraints at different levels of SLA (users, services, clouds and inter-cloud environments).
+ Recent work on SLA modeling in the cloud does not seem to use SLA for data integration, in our opinion because measures concern data services and not data itself.
+Furthermore, SLA are in general exclusively used in a mono-cloud context to express the conditions in which a user can expect the cloud to provide resources.
+In contrast,  data integration in a multi-cloud context implies  expressing and enforcing multiple granularity constraints in different aspects of SLA (users, services, clouds and inter-cloud environments).
 Finally,  an a-priori SLA enforcement mechanism -in opposition to the a-posteriori SLA monitoring to detect violation-  is mandatory to assess data integration feasibility. 

### 2015-05-07 Workshop2015/camera-ready/incremental.tex
Nadia's version

@@
 In our context, data are provided by services deployed on different clouds. 
-In the preivous   MOOC system example, several producers will supply equivalent content for a given period of time. 
+In the previous   MOOC system example, several producers will supply equivalent content for a given period of time. 
 They will be chosen with respect to the  preferences expressed by a consumer.
@@
 
-The Abstract Inter-Cloud Layer (ICL) delivers the results to the  query. 
+The Abstract Inter-Cloud Layer (ICL) (see Figure~\ref{fig:arch} is responsible to deliver the results to the  query. 
 The ICL  first identifies a set of abstract functionalities  and associated services that fit the  query. These descriptions are stored in a service description registry.
@@
 \center{
-\includegraphics[width=0.65\textwidth]{workflow.pdf}
+\includegraphics[width=0.66\textwidth]{workflow.pdf}
 \caption{SLA guided  data integration workflow.\label{fig:arch}}}
@@
 In contrast, the other measures should be computed by monitoring the conversations between the service and the applications that contact it.
-It is the case of service reputation that will determine the way personal user data will be anonymized (Constraint1).
+It is the case of user privacy-preserving service that will determine the way personal user data will be anonymized (Constraint1).
 Some measures will be instantiated depending on the context of  the service invoked within a multi-cloud environment.
@@
 Besides, she wishes to keep the content exchange private and she wants to order services by reputation.
-The maximum total cost will  also determine the kind of privacy preserving algorithms that will be applied.
+The maximum total cost will  also determine the kind of privacy preserving algorithms that should be applied.
 

### 2015-05-07 Workshop2015/camera-ready/introduction.tex
Nadia's version

@@
 Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t.
-to their own, when their data are used  within  an integration process (Constraint 2).
+to their  trust level, when their data are used  within  an integration process (Constraint 2).
 
@@
 The derived SLA allows to choose  services (w.r.t user requirements) that can contribute for answering a query.
-Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated taking according to user requirements and inter-cloud contracts.
+Once data services have been chosen, the integration process will be guided by an integration SLA, negotiated according to user requirements and inter-cloud contracts.
 

### 2015-05-07 Workshop2015/camera-ready/introduction.tex
mostly spell checking

@@
  Providers  and consumers can ask to minimize the transfer of personal data  when they share/consume content.
-According to the level of trust associated to data providers, the MOOC can use privacy preserving technics to let users share content anonymously  (Constraint1).
+According to the level of trust associated to data providers, the MOOC can use privacy preserving techniques to let users share content anonymously  (Constraint1).
 Furthermore,  data providers can  also wish to give restricted data access credentials w.r.t.
@@
 This paper is organized as follows.
-Section \ref{sec:relWork} presents related works that address SLA modelling, integration and SLA guided data management processes in cloud environments.
+Section \ref{sec:relWork} presents related works that address SLA modeling, integration and SLA guided data management processes in cloud environments.
 Section \ref{sec:incremental} gives an overview of our approach and highlights the need of new kind of SLA to conduct the integration process.

### 2015-05-07 SAPSE2015/camera-ready/computingDerivSLA.tex
New Directory: SAPSE2015 contains the camera-ready version (final)

--- 2015-05-05 Workshop2015/camera-ready/computingDerivSLA.tex
@@
 
-%A query has associated preferences  expressed as macroscopic constraints (i.e.
-user preferences statement): execution time, pay / no pay, data reliability, provenance, freshness, privacy-preserving constraints, partial/full results, delivery mode.
-These constraints are coupled with the profile of the user which is in general stated in her cloud subscription (amount of assigned storage space, number of requests, I/O transfered Mega bytes, etc.).
-
-%As said before, we assume that services export their \textit{agreed SLAs} that define measures that can be either expressed as constants,  computed (dynamically) by monitoring the execution and conversations associated to services, and hybrid they can be statically stated  but they change at execution time.
-A service  agreed SLA is expressed through an  XML document using the specification WSLA (Web service level agreement \footnote{\footnotesize http://www.research.ibm.com/people/a/akeller/\-Data/WSLASpecV1-20030128.pdf}).
-The service SLA measures  that we consider in our example are: cost, availability, freshness, provenance, location, duration of the engagement, privacy-preserving status.
-Other measures are associated to the conditions in which the service is called or to the precision and recall of their produced data given a request.
-
-The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures that can come from the evaluation of measures expressed in the cloud subscription of the user.
+The {\em derived SLA} is defined as a set of measures that correspond to the user preferences computed as a function of different static, computed and hybrid measures.
+These measures can come from the evaluation of simpler measures expressed in the cloud subscription of the user.
 The {\em derived SLA}  will guide the way the query will be evaluated, and the way results will be computed and delivered.
 
-In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said in previous section, will guide the evaluation of the query. 
+In the example, some of the user preferences statement measures are used for defining a {\em derived SLA} that, as said before, will guide the evaluation of the query. 
 These measures are defined as a function of the measures used by the agreed SLAs and by the cloud SLA contract. For example: 
@@
 Since some of them can only be determined at execution time, the decision on which services will participate in the evaluation of the query is approximated.
-This later step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}.
-In order to address this problem we introduce the notion of  {\em integration SLA}.
+This latter step may conduct either to the rejection of integration in case of total incompatibility, or to a negotiation step between {\em agreed SLA}s and the {\em derived SLA}.
+In order to address this problem we introduce the notion of  {\em integration SLA} (defined in  Section \ref{sec:queryProcessOpt}).
 %and thus the need for an adaptive setting.

### 2015-05-07 SAPSE2015/old-versions/old-1/useCase.tex
New Directory: SAPSE2015 contains the camera-ready version (final)

--- 2015-02-22 Workshop2015/useCase.tex
@@
 \center{
-\includegraphics[width=0.65\textwidth]{use-case.png}
+\includegraphics[width=0.60\textwidth]{use-case.png}
 \caption{General distributed data storage service.\label{fig:storage}}}
@@
 
-According to our example scenario, we conducted an experimental experience for implementing our data integration approach on a multi-cloud environment.
+According to our example scenario, we conducted an experience for implementing our data integration approach on a multi-cloud environment.
 We focussed on the implementation of a data as a service layer that integrates content from different services related to education but also related on data producers and consumers.
 Figure \ref{fig:storage} shows the general architecture of our scenario, deployed on Window Azure data store services and on Jelastic (https://jelastic.com), an open free cloud provider where we installed NE4J and Mongo NoSQL stores.
-The multi-cloud data as a service layer is a data provision platform storing clean data sets stemming from public data services (Linked in, Tweeter, Facebook) accessible on Internet and also from private ones.
+The multi-cloud data as a service layer is a data provision platform storing clean data sets stemming from public data services (Linked in, Twitter, Facebook) accessible on Internet and also from private ones.
 
@@
 We proposed a global service that gives access to these databases in an integrated way, and can receive queries using a pivot language, UNQL in our case.
-The global service implements a negotiation process for dealing with SLA and  the  query rewriting process.
+The global service implements a  process for dealing with SLA and  the  query rewriting process.
+Global queries are expressed in UNQL and expected SLA in documents containing constraint expression are un-equalities as shown previously.
+For the time being our experiment does not deales with SLA derivation for choosing data services.
+SLA measures concern the delay in which results are delivered, the size of results, and the period in which queries are re-executed in order to get new or fresh data.

### 2015-05-07 SAPSE2015/toSubmit/conclusions.tex
New Directory: SAPSE2015 contains the camera-ready version (final)

--- 2015-05-04 Workshop2015/camera-ready/conclusions.tex
@@
 
-The diversity of mentioned application domains highlights the difficulty regarding SLA manipulation.
-Indeed, cloud, service, and user SLAs could be expressed differently in term of clauses, formalism and content.
-The multi-cloud environment emphasizes these heterogeneities.
-
-The main issue when launching an integration process is to obtain the most accurate answer meeting the best user preferences.
+Furthermore, the integration SLA generation step is outstanding study.
+In fact the integration SLA should indicate the negotiation result with the aim to reuse it in further integration.
 One of the possibilities when studying the integration is to accept the integration process in an incremental  manner so that the query will continue to be evaluated till satisfying the set of QoS and non functional constraints expressed by the user.
 To our knowledge, the incremental production of a solution is beyond  the scope of the current methods for rewriting service compositions and represents a challenge to the area.
-Furthermore, the integration SLA generation step is outstanding study. In fact the integration SLA should indicate the negotiation result with the aim to reuse it in further integration.
 
